%======================================================================%
\section{The Mirror Climb}
\label{sec:climb}
%======================================================================%

\begin{equation}\label{eq:climb:unified}
  \Void\to\R\to\C\to\Quat\to\Oct\to\jalg\to\E{8}\to\E{8}\times\E{8}\to\E{6}\to\cdots\to\Void
\end{equation}

\begin{remark}[Climb sequence forced, not chosen]\label{rem:climb:forced}
The orbit \eqref{eq:climb:unified} is fixed by void, mirror, and capacity---not
by importing string-theory rungs. \emph{Functoriality}
(Definition~\ref{def:mirror}) restricts each step to modes
\textbf{M1}--\textbf{M4} of Definition~\ref{def:mirror:modes}. \emph{Hurwitz
terminal} at $n=4$ (Theorem~\ref{thm:rung-table}) forces the Jordan exit at
$n=5$ and anchors the associative subalgebra $\Quat\subset\Oct$ used below in
soldering (Definition~\ref{def:soldering}). On the stabilized Albert tower,
automorphism mirror closes at $\E{8}$ ($n=6$), product mirror is the unique
\textbf{M4} doubling on a simple Lie rung ($n=7$), and Cartan mirror is the
capacity-balanced collapse back to the $\jalg$ structure group ($n=8$,
Theorem~\ref{thm:e6}). \emph{Observer-slot requirement:} three independent
$\sigma$-anti-invariant classes in $H^1(\hat Q,V_{16})$ arise only after the
heterotic product quotient at $\Mirror^7(\Void)$ (Proposition~\ref{prop:climb:minimal-heterotic},
Section~\ref{sec:observer}); descent to $\E{6}$ supplies dynamics but does not
create the slot space. The above--below correspondence
(Definition~\ref{def:above-below}) ties each rung choice to a localized datum on
$\hat Q$.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Division rungs}
\label{sec:climb:division}
%----------------------------------------------------------------------%

\begin{theorem}[Mirror rung table, $n\leq5$]\label{thm:rung-table}
\begin{center}
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}rcccc@{}}
\toprule
$n$ & $A_n$ & $d_n$ & Mode & \\
\midrule
$0$ & $\{0\}$ & $0$ & void & \\
$1$ & $\R$ & $1$ & discrete & \\
$2$ & $\C$ & $2$ & arithmetic & \\
$3$ & $\Quat$ & $4$ & arithmetic & \\
$4$ & $\Oct$ & $8$ & Hurwitz terminal & \\
$5$ & $\jalg$ & $27$ & Jordan exit & \\
\bottomrule
\end{tabular}
\end{center}
In particular $\Mirror^4(\Void)=\Oct$ and $\Mirror^5(\Void)\cong\jalg$.
\end{theorem}

\begin{proof}
Cayley--Dickson doubling until $\Oct$; Hurwitz uniqueness of normed division
algebras; sedenion zero divisors force Jordan exit to the unique formally real
$H_3(\Oct)$~\cite{Hurwitz1898,SpringerVeldkamp2000}.
\end{proof}

\begin{lemma}[Sedenion failure]\label{lem:sedenion}
$\Mirror_{\mathrm{arith}}(\Oct)$ is $16$-dimensional and not division.
\end{lemma}

%----------------------------------------------------------------------%
\subsection{Exceptional rungs}
\label{sec:climb:exceptional}
%----------------------------------------------------------------------%

On $\jalg$, the stabilizer tower is $G_2\subset F_4\subset\E{6}$. The
Freudenthal diagonal $\mathfrak{M}(\Oct,\Oct)=\mathfrak{e}_8$ yields:

\begin{lemma}[Freudenthal closure]\label{lem:freudenthal}
Let $\mathfrak{M}(\Oct,\Oct)$ be the Freudenthal--Tits magic square entry for
the octonion--octonion pair. Then $\mathfrak{M}(\Oct,\Oct)=\mathfrak{e}_8$,
simply connected, and contains $G_2\times F_4\subset\E{8}$ as the stabilizer of
the diagonal $\jalg$ chart~\cite{Freudenthal1954,Tits1966}.
\end{lemma}

\begin{theorem}[$\Mirror^6(\Void)=\E{8}$]\label{thm:e8}
Automorphism mirror on the octonion--Jordan pair gives $\E{8}$, $d_6=248$.
\end{theorem}

\begin{definition}[Lie product mirror]\label{def:prod-mirror}
On a stabilized exceptional rung with Lie group $G$, the \emph{product mirror}
is $\Mirror_{\mathrm{prod}}(G):=G\times G$ with involution
$\sigma:(g_1,g_2)\mapsto(g_2,g_1)$ exchanging factors---mode~\textbf{M4} at the
Lie level, functorially analogous to Boolean doubling at $n=0\to1$.
\end{definition}

\begin{theorem}[$\Mirror^7(\Void)=\E{8}\times\E{8}$]\label{thm:e8e8}
Product mirror $\Mirror_{\mathrm{prod}}(G)=G\times G$ gives $d_7=496$.
\end{theorem}

\begin{proposition}[Minimal heterotic rung for three observer slots]\label{prop:climb:minimal-heterotic}
$\Mirror^7(\Void)=\E{8}\times\E{8}$ is the \emph{minimal} mirror rung supporting
three observer slots: $\dim H^1(\hat Q,V_{16})^{\sigma=-1}=3$
(Theorem~\ref{thm:observer-fp}). At $n\leq6$ there is no product-mirror
$\mathbb{Z}_2$ quotient on the stabilized datum, hence no
$\Pi_{\sigma=-1}$ observer sector (Section~\ref{sec:observer:definition}). At
$n=8$ the heterotic doubling is already capacity-collapsed to $\E{6}$
(Theorem~\ref{thm:e6}), so the three $1$-classes are fixed on $\hat Q$ at
$n=7$ and only transported below by descent. Thus observer multiplicity is a
\emph{below}-level consequence of the \emph{above} product mirror at the
seventh rung.
\end{proposition}

\begin{proof}
\emph{Minimality at $n\leq6$.}
For $n\leq6$, $\Mirror^n(\Void)$ is a single simple Lie datum or division
algebra. Involution stabilizes within one chart (automorphism mirror at $n=6$),
not across a heterotic pair. The cellular graph has no product-mirror
$\mathbb{Z}_2$ quotient with three independent $\mathbf{16}$-cells
(Definition~\ref{def:tower7} exists only at $n=7$), so
$\dim H^1(\hat Q,V_{16})^{\sigma=-1}$ is undefined and
$\Pi_{\sigma=-1}$ has no observer sector
(Section~\ref{sec:observer:definition}).

\emph{Existence at $n=7$.}
Product mirror gives $\E{8}\times\E{8}$ with involution
$\sigma:(g_1,g_2)\mapsto(g_2,g_1)$. On $\mathcal{T}_7$,
Lemma~\ref{lem:cellular} yields
$\dim H^1(\mathcal{T}_7,\mathcal{F}_{16})^{\sigma=-1}=3$; Proposition~\ref{prop:stone-lift}
and Theorem~\ref{thm:mirror-index} transport this to
$\dim H^1(\hat Q,V_{16})^{\sigma=-1}=3$.

\emph{Descent at $n=8$.}
Cartan mirror $\Pi_{\mathrm{het}}:\E{8}\times\E{8}\to\E{6}$
(Theorem~\ref{thm:e6}) reduces the gauge group but preserves the
$\sigma$-anti-invariant slot basis on $\hat Q$: the three observer indices are
fixed at the heterotic rung and only transported below by descent.
\end{proof}

\begin{theorem}[$\Mirror^8(\Void)=\E{6}$]\label{thm:e6}
Cartan mirror after capacity descent on the Albert graph gives $d_8=78$,
$H=\Spin(10)\times U(1)$, $\mathcal{M}=\E{6}/H$ (EIII), $\dim\mathcal{M}=32$.
\end{theorem}

\begin{proof}
\emph{$E_8$ (Steps 1--3).}
\emph{(i)} On $\jalg$, the stabilizer tower $G_2\subset F_4\subset\E{6}$ is
mirror-refined; the octonion measure before Jordan projection carries an
automorphism mirror $\Mirror_{\mathrm{aut}}$ coupling the two $\Oct$ sectors of
\eqref{eq:matrix} (Appendix~\ref{sec:appendix:albert}).
\emph{(ii)} Among simple Lie algebras containing $G_2\times F_4$ and closed
under octonion--octonion coupling, Lemma~\ref{lem:freudenthal} identifies
$\mathfrak{e}_8$ uniquely; this is classical Freudenthal--Tits data, not an
independent SJET postulate. Mirror functoriality selects
$\Mirror_{\mathrm{aut}}$ as mode~\textbf{M4} on Lie data at the first
exceptional rung.
\emph{(iii)} $d_6=\dim\E{8}=248$; Stone chart dimension $\chi(S_6)=248$
(Definition~\ref{def:chart-dim}).

\emph{$E_8\times E_8$ (Steps 1--3).}
\emph{(i)} Apply $\Mirror_{\mathrm{prod}}$ (Definition~\ref{def:prod-mirror})
to the stabilized datum of Theorem~\ref{thm:e8}; functoriality of $\Mirror$
(Definition~\ref{def:mirror}) gives
$\Mirror^7(\Void)=\Mirror(\Mirror^6(\Void))\cong\E{8}\times\E{8}$.
\emph{(ii)} At a simple exceptional rung, product mirror is the unique
\textbf{M4} doubling compatible with involution
(Proposition~\ref{prop:mirror:involution}); no smaller Lie datum carries a
heterotic $\mathbb{Z}_2$ quotient.
\emph{(iii)} $d_7=2\cdot248=496$; $\sigma:(g_1,g_2)\mapsto(g_2,g_1)$
implements $\Mirror^2\cong\mathrm{id}$ up to diagonal gauge on
$\delta(\E{8})\subset\E{8}\times\E{8}$.

\emph{$E_6$ (Steps 1--4).}
\emph{(i)} On $\E{8}\times\E{8}$, the diagonal embedding
$\delta:\E{8}\hookrightarrow\E{8}\times\E{8}$ is the $\sigma$-stabilized
subgroup. $\mathrm{Bal}_{\mathcal{C}}$ on $\mathcal{G}_{\mathrm{Albert}}$ at
the $\jalg$ rung fixes the $1|10|16$ partition
(Theorem~\ref{thm:partition}).
\emph{(ii)} Among exceptional groups, only $\E{6}$ admits
$H=\Spin(10)\times U(1)$ with branching
$\mathbf{27}=\mathbf{1}\oplus\mathbf{10}\oplus\mathbf{16}$ and coset mirror
$\mathbf{16}\leftrightarrow\overline{\mathbf{16}}$; this branching is
classical~\cite{SpringerVeldkamp2000}. Cartan mirror selects $\E{6}$ as the
capacity-balanced collapse indexed by the rank-$3$ diagonal of $\jalg$, not by
the two $\E{8}$ factors alone (Proposition~\ref{prop:climb:minimal-heterotic}).
\emph{(iii)} $d_8=\dim\E{6}=78$, $\mathcal{M}=\E{6}/H$ (EIII),
$\dim\mathcal{M}=32$.
\emph{(iv)} Descent preserves the three observer slots on $\hat Q$
(Proposition~\ref{prop:stone-lift}); dynamics below $n=7$ does not regenerate
them.
\end{proof}

\begin{proposition}[Exceptional mirror steps]\label{prop:climb:exceptional}
At $n\geq6$ on the stabilized $\jalg$ rung, $\Mirror$ acts as:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item $\E{8}$: automorphism mirror on the octonion--Jordan pair
    (Theorem~\ref{thm:e8});
  \item $\E{8}\times\E{8}$: Lie product mirror $\Mirror_{\mathrm{prod}}$
    (Theorem~\ref{thm:e8e8}, Definition~\ref{def:prod-mirror});
  \item $\E{6}$: Cartan mirror after capacity descent
    (Theorem~\ref{thm:e6});
  \item $\E{6}\to H=\Spin(10)\times U(1)$: coset stabilization on EIII;
  \item $\cdots\to\Void$: collapse after electroweak breaking.
\end{enumerate}
Each step transports the quaternionic soldering block $H_2(\Quat)$ of
Definition~\ref{def:spacetime:H2O} without branching
(Proposition~\ref{prop:soldering-transport}).
\end{proposition}

\begin{definition}[Chart dimension]\label{def:chart-dim}
At $n\geq6$, $\chi(S_n)=\dim A_n\in\{248,496,78\}$; profinite $|S_n|$ is
generally infinite. Stone refinement is chart synchronization, not cardinality
matching~\cite{Stone1936}.
\end{definition}