%======================================================================%
\section{The Mirror Climb: Division and Exceptional Ladders}
\label{sec:ladder}
%======================================================================%

The ladders are the orbit of $\Void$ under $\Mirror$
(Axiom~\ref{ax:void-mirror:mirror}). Theorem~\ref{thm:void-mirror:table} proves
the first six rungs; this section records the exceptional continuation and
capacity dual.

%----------------------------------------------------------------------%
\subsection{Unified climb}
\label{sec:ladder:unified}
%----------------------------------------------------------------------%

\begin{definition}[Unified ladder]\label{def:ladder:unified}
The \emph{unified mirror climb} is
\begin{equation}\label{eq:ladder:unified}
  \Void
  \;\xrightarrow{\Mirror}\;
  \R\;\xrightarrow{\Mirror}\;\C\;\xrightarrow{\Mirror}\;\Quat
  \;\xrightarrow{\Mirror}\;\Oct\;\xrightarrow{\Mirror}\;\jalg
  \;\xrightarrow{\Mirror}\;\E{8}\;\xrightarrow{\Mirror}\;\E{8}\times\E{8}
  \;\xrightarrow{\Mirror}\;\E{6}\;\xrightarrow{\;\cdots\;}\;\Void,
\end{equation}
with $n$-th arrow $\Mirror^n$ as in \eqref{eq:void-mirror:power}. Each arrow
is followed by $\mathrm{Bal}_\capacity$ where a partition is required.
\end{definition}

\begin{remark}[Rung index]
$\Mirror^4(\Void)=\Oct$ and $\Mirror^5(\Void)=\jalg$ are \textbf{theorems}
(Theorem~\ref{thm:void-mirror:table}), not definitions. The exceptional rungs
$n\geq6$ extend the Jordan stabilization.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Hurwitz rung}
\label{sec:ladder:hurwitz}
%----------------------------------------------------------------------%

\begin{theorem}[Hurwitz]\label{thm:ladder:hurwitz}
Mirror arithmetic doubling produces only
\[
  \{0\},\;\R,\;\C,\;\Quat,\;\Oct
\]
of dimensions $0,1,2,4,8$. Equivalently, $\Mirror^4(\Void)=\Oct$ and
$\Mirror^k_{\mathrm{arith}}(\Void)$ is non-division for all $k\geq5$ unless the
Jordan exit to $\jalg$ is taken.
\end{theorem}

\begin{proof}
Cayley--Dickson doubling at each step until $\Oct$; Hurwitz classification of
normed division algebras; sedenion failure
(Lemma~\ref{lem:void-mirror:sedenion}).
\end{proof}

\begin{proposition}[Terminal Jordan rung]\label{prop:ladder:terminal}
The mirror climb stabilizes at
\[
  \Mirror^5(\Void)\;\cong\;\jalg=H_3(\Oct),
  \qquad d_5=27.
\]
The profinite limit $\varprojlim_n\Mirror^n(\Void)$ has $27$ observable
coordinates. No $16$-dimensional division rung appears.
\end{proposition}

\begin{proof}
From Theorem~\ref{thm:void-mirror:table} and uniqueness of $H_3(\Oct)$ as the
formally real Jordan algebra over $\Oct$.
\end{proof}

%----------------------------------------------------------------------%
\subsection{Exceptional rung}
\label{sec:ladder:exceptional}
%----------------------------------------------------------------------%

\begin{proposition}[Exceptional mirror steps]\label{prop:ladder:exceptional}
At $n\geq6$ on the stabilized $\jalg$ rung, $\Mirror$ acts as:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item $\E{8}$: automorphism mirror of the $\Oct$ measure before projection;
  \item $\E{8}\times\E{8}$: heterotic product mirror (left/right sectors);
  \item $\E{6}$: rank-one capacity-balanced cell on $\jalg$;
  \item $\E{6}\to H=\Spin(10)\times U(1)$: Cartan mirror (EIII coset);
  \item $\cdots\to\Void$: collapse after electroweak breaking.
\end{enumerate}
\end{proposition}

\begin{proposition}[Branchings at $\E{6}$]\label{prop:ladder:e6branch}
Under $H=\Spin(10)\times U(1)$,
\begin{equation}\label{eq:foundations:27branch}
  \mathbf{27}=\mathbf{1}_{+4}\oplus\mathbf{10}_{-2}\oplus\mathbf{16}_{+1},
\end{equation}
\begin{equation}\label{eq:foundations:adjoint}
  \mathbf{78}=\mathbf{45}_0\oplus\mathbf{1}_0
  \oplus\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3},
\end{equation}
$\mathcal{M}=\E{6}/H=\mathrm{EIII}$, $\dim_{\R}\mathcal{M}=32$, coset mirror
$\mathbf{16}_{-3}\leftrightarrow\overline{\mathbf{16}}_{+3}$.
\end{proposition}

\begin{conjecture}[Exceptional mirror from Jordan]\label{conj:ladder:e8}
$\Mirror^6(\Void)=\E{8}$ and $\Mirror^7(\Void)=\E{8}\times\E{8}$ are derivable
from the $G_2\subset F_4\subset\E{6}$ stabilizer tower on $\jalg$ without
importing heterotic string theory as primitive data.
\end{conjecture}

\begin{remark}[Heterotic parallel]\label{rem:ladder:heterotic}
$\E{8}\times\E{8}$ matches the heterotic gauge group;
$h^1(\hat Q,V_{16})=3$~\cite{Witten1985} corroborates three generations
(Remark~\ref{rem:sm:heterotic}).
\end{remark}

%----------------------------------------------------------------------%
\subsection{Capacity as dual mirror}
\label{sec:ladder:capacity}
%----------------------------------------------------------------------%

\begin{definition}[Capacity functional]\label{def:ladder:capacity}
On the mirror-refined Albert graph $\mathcal{G}$ with costs $c_i$ and $\mu$,
\begin{equation}\label{eq:ladder:capacity}
  \capacity(\omega)=-\sum_{a\in V}\mu(a)\log\!\Bigl(\sum_{i}
  e^{c_i(a)-\omega_i}\Bigr).
\end{equation}
$\capacity$ is the \emph{dual mirror}: $\Mirror$ doubles sectors;
$\mathrm{Bal}_\capacity$ balances them.
\end{definition}

\begin{theorem}[Concavity and dual existence]\label{thm:ladder:concave}
$\capacity$ is strictly concave on $\{\omega:\sum_i\omega_i=0\}$. For targets
$m_i>0$, $\sum_i m_i=1$, there exists unique $\omega^\star$ with
$\partial\capacity/\partial\omega_i(\omega^\star)=m_i$.
\end{theorem}

\begin{theorem}[Capacity at the Jordan rung]\label{thm:ladder:capacity-jordan}
On $\mathcal{G}_{\mathrm{Albert}}$ at $\Mirror^5(\Void)$, the unique capacity
maximizer yields the $1|10|16$ partition of
Proposition~\ref{prop:foundations:partition}. This is the mirror-dual of the
$\mathbf{27}$ branching \eqref{eq:foundations:27branch}.
\end{theorem}