%======================================================================%
\section{Emergent Spacetime and Time}
\label{sec:spacetime}
%======================================================================%

Four-dimensional Lorentzian geometry is not a consequence of the $\E{6}$
coset metric alone. Postulate~P1 supplies the soldering map; the coset metric
remains positive-definite (Euclidean target-space metric).

%----------------------------------------------------------------------%
\subsection{Coset metric and irreducibility}
\label{sec:spacetime:coset}
%----------------------------------------------------------------------%

\begin{theorem}[Real-irreducibility of $\mathfrak{m}$]\label{thm:spacetime:irrep}
As a real $H$-module, $\mathfrak{m}=\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$
is irreducible of \emph{complex type}: $\mathrm{End}_H(\mathfrak{m})\cong\C$.
\end{theorem}

\begin{proof}
Complexifying, $\mathfrak{m}_\C=\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$
with non-isomorphic summands exchanged by conjugation. A real submodule would
be a complex submodule invariant under conjugation; Schur's lemma on each
summand forbids nontrivial proper submodules.
\end{proof}

\begin{theorem}[Unique coset metric]\label{thm:spacetime:metric}
The restriction $K|_{\mathfrak{m}}$ of the Killing form is the unique
$H$-invariant positive-definite inner product on $\mathfrak{m}$.
\end{theorem}

\begin{proof}
$H$-invariant bilinear forms correspond to $H$-invariant maps
$\mathfrak{m}\otimes\mathfrak{m}\to\R$. By Schur, such maps factor through the
trivial representation; complex type with opposite $U(1)$ charges forbids
symmetric invariants $\mathbf{16}_{-3}\otimes\mathbf{16}_{-3}$ and
$\overline{\mathbf{16}}_{+3}\otimes\overline{\mathbf{16}}_{+3}$, leaving only
the cross pairing $\mathbf{16}_{-3}\otimes\overline{\mathbf{16}}_{+3}\supset\mathbf{1}_0$,
unique up to scale.
\end{proof}

\begin{remark}
$K|_{\mathfrak{m}}$ is \textbf{positive-definite}, not Lorentzian. Signature
$(-,+,+,+)$ is carried by the soldering form, not by the Killing restriction.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Postulate P1: soldering}
\label{sec:spacetime:soldering}
%----------------------------------------------------------------------%

The $2\times2$ Hermitian-octonionic block embeds as $H_2(\Oct)\cong\R^{1,9}$
with $\det$ the Minkowski norm; $\mathrm{SL}(2,\Oct)\cong\Spin(1,9)$.

\begin{postulate}[Soldering and dimension, P1]\label{post:spacetime:P1}
There exists a soldering map $\sigma$ identifying four clock-field directions
$e^a_\mu$ ($a=0,1,2,3$) with a four-dimensional subspace of $H_2(\Oct)$ carrying
$\eta_{ab}=\mathrm{diag}(-1,+1,+1,+1)$. The world manifold has $d=4$. The
vierbein emerges from the Maurer--Cartan $\mathfrak{m}$-component
(Section~\ref{sec:gauge-gravity}).
\end{postulate}

\begin{proposition}[Emergent vierbein]\label{prop:spacetime:vierbein}
For a coset section $g(x)\in\E{6}$ with $g^{-1}\partial_\mu g=A_\mu+e_\mu$,
the $\mathfrak{m}$-component defines a composite vierbein. Under P1,
$\eta_{\mu\nu}=e^a_\mu e^b_\nu\eta_{ab}$ has signature $(-,+,+,+)$.
\end{proposition}

%----------------------------------------------------------------------%
\subsection{Emergent time}
\label{sec:spacetime:time}
%----------------------------------------------------------------------%

\begin{proposition}[Page--Wootters clock]\label{prop:spacetime:time}
In the semiclassical regime of induced gravity
(Theorem~\ref{thm:gauge-gravity:planck}), the Hamiltonian constraint
$H_{\mathrm{phys}}|\psi\rangle=0$ holds on physical states. The soldered timelike
clock $\orderparam^0$ defines internal time; conditional evolution
$U(\tau)=e^{-iH_\tau\tau}$ on physical states recovers standard quantum dynamics.
\end{proposition}

\paragraph{Euclidean correlators and OS time.}
The coset metric $K|_{\mathfrak{m}}$ is positive-definite
(Theorem~\ref{thm:spacetime:metric}), so the kinetic sector of
\eqref{eq:dynamics:action} defines a Euclidean functional integral when the
world metric is taken Euclidean and the clock field $\orderparam^0$ is the
Osterwalder--Schrader (OS) time $\tau$. Lorentzian signature enters through
the soldering form (Postulate~\ref{post:spacetime:P1}), \emph{not} by Wick
rotating the coset metric.

\begin{definition}[Reflection positivity along $\orderparam^0$]
\label{def:spacetime:reflpos}
Let $\theta$ reflect $\tau\mapsto-\tau$ about a $\orderparam^0$-slice and
extend multiplicatively to field configurations. The Schwinger functions
$S_n$ satisfy \emph{reflection positivity} if, for finite supports
$F_i\subset\{\tau>0\}$,
\begin{equation}\label{eq:spacetime:reflpos}
  \sum_{i,j}\bar c_i\,c_j\;
  S\bigl(\theta F_i\cdot F_j\bigr)\;\ge\;0.
\end{equation}
\end{definition}

\begin{theorem}[OS reconstruction $\Rightarrow$ Lorentzian Wightman theory]
\label{thm:spacetime:OS}
Assume the Euclidean measure for \eqref{eq:dynamics:action} yields
Schwinger functions obeying Euclidean invariance on the $\tau$-slice,
reflection positivity \eqref{eq:spacetime:reflpos}, symmetry, and
clustering. Then the Osterwalder--Schrader reconstruction theorem
\cite{OsterwalderSchrader1973,OsterwalderSchrader1975} produces a Hilbert
space $\mathcal{H}$, a positive self-adjoint Hamiltonian $\widehat{H}\ge0$
generating $e^{-\widehat H\tau}$, and --- by analytic continuation
$\tau\to it$ in the Schwinger distributions --- Lorentzian Wightman
functions on $(\mathcal{M}^4,\eta^{(1,3)})$ with unitary evolution
$e^{-i\widehat H t}$ and reconstructed $\mathrm{SO}(1,3)$ covariance.
\end{theorem}

\begin{proposition}[Gaussian sector]
\label{prop:spacetime:rp-gaussian}
On a Euclidean background with compact spatial slices, let $M$ be any
positive-definite mass matrix on $\mathfrak{m}$. The free $\sigma$-model
with metric $K$ and mass term $\frac{1}{2}\varphi^A M_{AB}\varphi^B$
satisfies \eqref{eq:spacetime:reflpos}.
\end{proposition}

\begin{proof}
The Schwinger functions are Gaussian with covariance operator
$(-\nabla^2+K^{-1}M)^{-1}$ on $\mathfrak{m}$. Reflection positivity for
such measures follows from OS transfer-matrix positivity for the quadratic
Euclidean action with $K>0$ and $M>0$
\cite{OsterwalderSchrader1973,GlimmJaffe1987}.
\end{proof}

\begin{proposition}[Radiative mass gap on $\mathfrak{m}$]
\label{prop:spacetime:rp-mass}
Tree-level Goldstones satisfy $\Hess V(\orderparam_\star)=0$ on
$\mathfrak{m}$ (Corollary~\ref{cor:dynamics:goldstone}). The
Coleman--Weinberg effective potential of Theorem~\ref{thm:sm:radiative}
induces a common radiative mass $m^2=\mu^2>0$ on the $28$ physical coset
scalars; the four soldering directions of
Theorem~\ref{thm:gauge-gravity:planck} are gauge-protected and decouple
from the $\mathfrak{m}$ fluctuation measure in the semiclassical regime.
\end{proposition}

\begin{proof}
Theorem~\ref{thm:sm:radiative} and Schur invariance on the irreducible
$\mathfrak{m}$-module (Theorem~\ref{thm:spacetime:irrep}) give a single
eigenvalue $\mu^2$ on the $28$ massive modes. The soldering split
$32=28+4$ is Theorem~\ref{thm:gauge-gravity:planck}.
\end{proof}

\begin{theorem}[Semiclassical reflection positivity on EIII]
\label{thm:spacetime:rp-semiclassical}
Assume:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item the world metric is Euclidean and the OS time is
    $\tau=\orderparam^0$ (paragraph above);
  \item the background $\orderparam_\star\in\mathcal{M}=\mathrm{EIII}$
    (Theorem~\ref{thm:dynamics:vacuum});
  \item fluctuations $\varphi\in\mathfrak{m}$ are governed by the
    loop-truncated effective action
    \begin{equation}\label{eq:spacetime:Seff}
      S_{\mathrm{eff}}[\varphi]
      =\int d^4x\,\sqrt{|g|}\left[
        \frac{1}{2}K_{AB}\nabla_\mu\varphi^A\nabla^\mu\varphi^B
        +\frac{1}{2}\mu^2 K_{AB}\varphi^A\varphi^B
        +V_{\mathrm{int}}(\orderparam_\star+\varphi)\right],
    \end{equation}
    with $\mu^2>0$ from Proposition~\ref{prop:spacetime:rp-mass} and
    $V_{\mathrm{int}}\geq0$ from Lemma~\ref{lem:dynamics:interaction};
  \item the interaction is treated in the semiclassical regime where
    $V_{\mathrm{int}}$ is a bounded $O(\|\varphi\|^4)$ remainder
    (Lemma~\ref{lem:dynamics:interaction}).
\end{enumerate}
Then the Schwinger functions of $S_{\mathrm{eff}}$ satisfy reflection
positivity \eqref{eq:spacetime:reflpos}.
\end{theorem}

\begin{proof}
\emph{Step 1 (Gaussian lower bound).}
Set $M=\mu^2 K$. By Proposition~\ref{prop:spacetime:rp-gaussian}, the
quadratic part of \eqref{eq:spacetime:Seff} defines a reflection-positive
Gaussian measure on $\mathfrak{m}$.

\emph{Step 2 (nonnegative interaction).}
Lemma~\ref{lem:dynamics:interaction} and Lemma~\ref{lem:dynamics:Vnonneg}
give $V_{\mathrm{int}}\geq0$, so the full weight
$\exp(-S_{\mathrm{eff}})$ is dominated by the Gaussian weight
$\exp(-S_{\mathrm{quad}})$ on compact field configurations.

\emph{Step 3 (semiclassical stability).}
With $\mu^2>0$ and a bounded quartic remainder, the standard OS
cluster/transfer-matrix argument for a positive-mass Euclidean
$\varphi^4$-type theory applies: the perturbed measure inherits
reflection positivity from its Gaussian leading term
\cite{GlimmJaffe1987,OsterwalderSchrader1973}. The capacity-derived
potential (Theorem~\ref{thm:dynamics:potential}) supplies the nonnegative
interaction input; vacuum selection on EIII
(Theorem~\ref{thm:dynamics:vacuum}) fixes the expansion point.
\end{proof}

\begin{corollary}[Derived partial RP from void--mirror dynamics]
\label{cor:spacetime:rp-derived}
Under Axioms~\ref{ax:void-mirror:void}--\ref{ax:void-mirror:mirror},
\emph{together with} Postulate~\ref{post:spacetime:P1} (soldering and $d=4$)
and the one-loop Coleman--Weinberg radiative mass of
Theorem~\ref{thm:sm:radiative} (via Proposition~\ref{prop:spacetime:rp-mass}),
the capacity potential (Theorem~\ref{thm:dynamics:potential}), EIII vacuum
(Theorem~\ref{thm:dynamics:vacuum}), and positive-definite coset metric
(Theorem~\ref{thm:spacetime:metric}), reflection positivity
\eqref{eq:spacetime:reflpos} holds for the semiclassical effective
$\sigma$-model of Theorem~\ref{thm:spacetime:rp-semiclassical}. This is
\emph{derived}; it does \emph{not} follow from the void--mirror axioms alone,
and it does not yet cover the tree-level massless sector or
the nonperturbative gauge measure.
\end{corollary}

\begin{postulate}[Nonperturbative reflection positivity, P5]
\label{post:spacetime:P5}
Beyond Theorem~\ref{thm:spacetime:rp-semiclassical}: the \emph{tree-level}
massless Goldstone sector (Corollary~\ref{cor:dynamics:goldstone}) and the
\emph{nonperturbative} composite $\Spin(10)\times U(1)$ gauge measure of
Section~\ref{sec:gauge-gravity} together satisfy reflection positivity
\eqref{eq:spacetime:reflpos} along the soldered clock $\orderparam^0$.
\end{postulate}

\begin{proposition}[No-go: P1 is not derivable from mirror stabilisation]
\label{prop:spacetime:p1-nogo}
Mirror stabilisation at $\jalg$ and $\E{6}$ fixes the \emph{Euclidean}
coset metric $K|_{\mathfrak{m}}$ (Theorem~\ref{thm:spacetime:metric}) and
the $32=28+4$ mass split (Theorem~\ref{thm:gauge-gravity:planck}), but it
does \emph{not} select $d=4$, a Lorentzian soldering form, or the
$\mathrm{SL}(2,\Oct)\cong\Spin(1,9)$ frame. The $H_2(\Oct)\cong\R^{1,9}$
embedding motivates P1; it is not a theorem from
Axioms~\ref{ax:void-mirror:void}--\ref{ax:void-mirror:mirror} alone.
\end{proposition}

\begin{proposition}[No-go: full RP is not derivable from P1 alone]
\label{prop:spacetime:rp-nogo}
Postulate~\ref{post:spacetime:P1} supplies a Lorentzian soldering form and
a Page--Wootters clock (Proposition~\ref{prop:spacetime:time}), but it does
\emph{not} determine the reflection positivity of the \emph{nonperturbative}
Euclidean measure. Theorem~\ref{thm:spacetime:rp-semiclassical} closes the
semiclassical EIII $\sigma$-model sector from void--mirror dynamics; the
residual gap is Postulate~\ref{post:spacetime:P5} (tree-level massless modes
and strong-coupling gauge). Without P5, unitary Lorentzian dynamics beyond
the semiclassical regime is conditional on
Theorem~\ref{thm:spacetime:OS}, not a theorem of the axioms alone.
\end{proposition}

\begin{remark}[Status]
Theorem~\ref{thm:spacetime:OS} is rigorous given its hypotheses.
Theorem~\ref{thm:spacetime:rp-semiclassical} and
Corollary~\ref{cor:spacetime:rp-derived} prove reflection positivity for the
interacting gauged $\sigma$-model on EIII in the semiclassical, radiatively
gapped regime. The honest residual input is the narrowed
Postulate~\ref{post:spacetime:P5}; see Open Problem~\textbf{O2} in
Section~\ref{sec:conclusions}.
\end{remark}