%======================================================================%
\section{Gauge Sector and Induced Gravitation}
\label{sec:gauge-gravity}
%======================================================================%

%----------------------------------------------------------------------%
\subsection{Composite connection}
\label{sec:gauge-gravity:gauge}
%----------------------------------------------------------------------%

The Lie algebra splits $H$-equivariantly as
$\mathfrak{e}_6=\mathfrak{h}\oplus\mathfrak{m}$ with
$\mathfrak{h}=\mathfrak{so}_{10}\oplus\mathfrak{u}_1$ and $\mathfrak{m}$ as in
\eqref{eq:foundations:adjoint}.

\begin{theorem}[Composite gauge connection]\label{thm:gauge-gravity:composite}
For $g(x)\in\E{6}$, write $g^{-1}\partial_\mu g=\mathcal{A}_\mu+e_\mu$ with
$\mathcal{A}_\mu\in\mathfrak{h}$, $e_\mu\in\mathfrak{m}$. Under
$g\mapsto gh^{-1}$, $h\in H$,
\[
  \mathcal{A}_\mu\mapsto h\mathcal{A}_\mu h^{-1}-(\partial_\mu h)h^{-1},
\]
and the curvature $\mathcal{F}_{\mu\nu}=\partial_{[\mu}\mathcal{A}_{\nu]}+
[\mathcal{A}_\mu,\mathcal{A}_\nu]$ transforms as an $H$ field strength. All
$46$ generators of $\mathfrak{h}$ remain massless because $H$ is unbroken.
\end{theorem}

\begin{proof}
Standard transformation of the canonical connection on the reductive homogeneous
bundle $\E{6}\to\mathcal{M}$.
\end{proof}

\begin{proposition}[Induced Yang--Mills]\label{prop:gauge-gravity:ym}
At one loop, integrating out massive coset modes generates
$S_{\mathrm{YM}}=\frac{1}{4\hat g^2}\int\Tr(\mathcal{F}_{\mu\nu}\mathcal{F}^{\mu\nu})$
with $\hat g^{-2}\propto f^2\mu^2/(16\pi^2)$, $[f]=\mathrm{mass}$.
\end{proposition}

%----------------------------------------------------------------------%
\subsection{Anomaly cancellation}
\label{sec:gauge-gravity:anomaly}
%----------------------------------------------------------------------%

Anomalies are computed with Dynkin indices $A_{\mathbf{16}}=A_{\mathbf{10}}=1$,
$A_{\mathbf{1}}=0$ and $U(1)$ charges from \eqref{eq:foundations:27branch}.

\begin{theorem}[Green--Schwarz cancellation]\label{thm:gauge-gravity:gs}
The cubic anomaly $\mathcal{A}_{U(1)^3}$ vanishes:
$16\cdot1^3+10\cdot(-2)^3+1\cdot4^3=0$.
The mixed anomaly $\mathcal{A}_{U(1)\cdot\Spin(10)^2}$ has coefficient $-1$:
$1\cdot1+(-2)\cdot1+4\cdot0=-1$,
and is cancelled by a Green--Schwarz term $\propto\mathrm{tr}(F\wedge F)\,B$
with axion $B$ from the $\mathbf{1}_{+4}$ sector.
\end{theorem}

\begin{proof}
Direct arithmetic on charges and indices; see~\cite{GreenSchwarz1984} for the
mechanism.
\end{proof}

%----------------------------------------------------------------------%
\subsection{Induced gravity}
\label{sec:gauge-gravity:gravity}
%----------------------------------------------------------------------%

\begin{theorem}[Sakharov induced gravity]\label{thm:gauge-gravity:planck}
In a heat-kernel scheme, only massive modes contribute to the $a_2$ coefficient.
With $28$ physical massive coset scalars ($s=+1$, $m^2=\mu^2$ canonically),
\begin{equation}\label{eq:gauge-gravity:planck}
  \MPl^2
  =\frac{1}{16\pi^2}\cdot\frac{1}{6}\sum_{\mathrm{massive}} s_i m_i^2
  \log\frac{\Lambda^2}{m_i^2}
  \approx\frac{28}{6}\cdot\frac{\mu^2}{16\pi^2}
  \log\frac{\Lambda^2}{\mu^2}>0.
\end{equation}
The four soldering directions are protected by diffeomorphism and local Lorentz
Ward identities, not by $\Hess V$.
\end{theorem}

\begin{remark}[Cosmological constant]
The $a_0$ term yields an uncancelled $\Lambda^4$ vacuum energy. SJET does not
solve the cosmological constant problem; $\Lambda_{\mathrm{cc}}$ is a tuned
relevant coupling.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Renormalization group}
\label{sec:gauge-gravity:rg}
%----------------------------------------------------------------------%

\begin{theorem}[Gauge $\beta$-function]\label{thm:gauge-gravity:beta-g}
With canonical dimensionless coupling $\hat g^2$,
\begin{equation}\label{eq:gauge-gravity:beta}
  \beta_{\hat g^2}=2\hat g^2+\frac{b_0}{48\pi^2}\hat g^4,
  \qquad
  b_0=\tfrac{11}{3}C_A-\tfrac{4}{3}T\,n_F-\tfrac{1}{6}T\,n_S.
\end{equation}
For three chiral $\mathbf{16}$s ($n_F=3$) and $n_S=28$ coset scalars:
\begin{equation}\label{eq:gauge-gravity:b0}
  b_0(3\,\mathrm{gen})
  =\tfrac{11}{3}(8)-\tfrac{4}{3}(2)(3)-\tfrac{1}{6}(2)(28)
  =\frac{88-24-28}{3}=12.
\end{equation}
The one-generation anchor ($n_F=1$, $n_S=2$) gives $b_0(1\,\mathrm{gen})=26$.
The gauge sector is asymptotically free ($\hat g^2_\star=0$).
\end{theorem}

\begin{conjecture}[Gravitational UV fixed point]\label{conj:gauge-gravity:kappa}
A truncated RG gives $\beta_\kappa=2\kappa-(5/48\pi^2)\kappa^2$ with
UV-attractive $\kappa_\star=96\pi^2/5$. This one-loop result is indicative,
not rigorous~\cite{Reuter1998}.
\end{conjecture}