%======================================================================%
\section{The Physical Universe}
\label{sec:physics}
%======================================================================%

Mathematical data of $\mathfrak{U}^\star$ becomes physical through mirror
quotient observability (Section~\ref{sec:observer}), observer collapse at
$\Mirror^7(\Void)$, and soldering on the Jordan--octonionic block.

%----------------------------------------------------------------------%
\subsection{Physical sector}
\label{sec:physics:sector}
%----------------------------------------------------------------------%

Physical configurations are observer-collapsed states on $\hat Q$
(Definitions~\ref{def:Qhat},~\ref{def:observer},~\ref{def:physical}).

\begin{definition}[Physical configurations]\label{def:physical}
A configuration is \emph{observable} if it lies in the $\sigma$-anti-invariant
sector of the mirror quotient $\hat Q=Q/\sigma$
(Definition~\ref{def:Qhat}). Fermions are cohomology classes in
$H^1(\hat Q,V_{16})^{\sigma=-1}$; each observer $|\omega_\iota\rangle$ is one
such class (Theorem~\ref{thm:observer-fp}). Observable states are those
surviving observer collapse $\Pi_{\sigma=-1}$
(Definition~\ref{def:heterotic-collapse}); $\sigma$-invariant mirror doubles
are quotient-non-observable.
\end{definition}

\begin{proposition}[No-go: P2 on the unquotiented coset]\label{prop:p2-nogo}
Void, mirror, and capacity balancing fix the \emph{number} of horizontal
family cells ($k=3$, Theorem~\ref{thm:partition}) and organize them by triality
on $\mathfrak{d}$, but they do \emph{not} derive chiral $\Spin(10)$ matter on
the unquotiented coset. The EIII matter directions
$\mathfrak{m}=\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$
(Theorem~\ref{thm:universe}) are a mirror-symmetric pair
(Proposition~\ref{prop:mirror:involution}); selecting one chiral
$\mathbf{16}$ per family with no $\overline{\mathbf{16}}$ partners is
\emph{Postulate~P2}, not a consequence of stabilisation alone. A bare Yukawa
$\bar\psi\,\orderparam\,\psi$ with
$\orderparam\in\{\mathbf{16},\overline{\mathbf{16}}\}$ is not $H$-invariant on
the unquotiented coset.
\end{proposition}

\begin{remark}[Observer collapse eliminates P2]
Proposition~\ref{prop:p2-nogo} is not overridden: it records an honest limit
on \emph{postulated} chiral insertion atop the mirror-symmetric coset. The
elimination route \emph{redefines} the matter sector. Observer collapse
$\Pi_{\sigma=-1}$ together with Definition~\ref{def:physical} declares
physical fermions to be $\sigma$-anti-invariant classes on $\hat Q$; mirror
partners live in $H^1(\hat Q,V_{16})^{\sigma=+1}$ and are not observable.
Chirality is then a theorem of quotient observability, not an added input.
\end{remark}

\begin{theorem}[Chirality from observer collapse]\label{thm:chirality-derived}
Under Definition~\ref{def:physical} and Theorem~\ref{thm:observer-fp},
\begin{equation}\label{eq:chirality-derived}
  \dim H^1(\hat Q,V_{16})^{\sigma=-1}=3,
\end{equation}
with one chiral $\mathbf{16}$ of $\Spin(10)$ per observer index
$\iota\in\mathcal{I}$. No $\overline{\mathbf{16}}$ partners appear in the
physical sector because mirror partners are $\sigma$-invariant, not
anti-invariant. Hence $n_F=3$. This \textbf{replaces Postulate~P2}: chirality
is not postulated; it is the quotient definition of observability together
with the observer fixed-point count.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:observer-fp} gives the anti-invariant dimension and the
bijection $\iota\mapsto|\omega_\iota\rangle$. Physical configurations are
anti-invariant by Definition~\ref{def:physical}; $\sigma$-invariant modes are
mirror doubles and quotient-non-observable. Cellular details in
Appendix~\ref{sec:appendix:quotient}.
\end{proof}

\begin{corollary}[Three families]\label{thm:three-families}
Theorem~\ref{thm:chirality-derived} yields $n_F=3$ chiral families without
importing heterotic axioms as primitive data~\cite{Witten1985}.
\end{corollary}

%----------------------------------------------------------------------%
\subsection{Spacetime from the climb}
\label{sec:physics:spacetime}
%----------------------------------------------------------------------%

Four-dimensional Lorentzian geometry is not a consequence of the $\E{6}$
coset metric alone. The mirror climb supplies a quaternionic clock block;
observer lifetime charts (Section~\ref{sec:observer:lifetime}) admit a
soldering map that imports signature into the contact layer.

\begin{definition}[Jordan--octonionic clock block]\label{def:spacetime:H2O}
Identify off-diagonal Jordan slots of $\jalg$ with the $2\times2$
Hermitian--octonionic model $H_2(\Oct)$. The determinant $\det$ carries
signature $(1,9)$ on $H_2(\Oct)\cong\R^{10}$. Restrict to the quaternionic
subalgebra $\Quat\subset\Oct$ fixed by the mirror involution at the
$4\to5$ Jordan exit (Theorem~\ref{thm:rung-table}). The embedded block
$H_2(\Quat)\subset H_2(\Oct)$ is four-dimensional; $\det|_{H_2(\Quat)}$
has Lorentzian signature $(-,+,+,+)$.
\end{definition}

\begin{definition}[Soldering]\label{def:soldering}
Let $\sigma_{\mathrm{sol}}:H_2(\Quat)\hookrightarrow\jalg$ be the canonical
embedding of Definition~\ref{def:spacetime:H2O}. The \emph{soldering map}
identifies four clock components $\orderparam^0,\ldots,\orderparam^3$ with
$\mathrm{Im}(\sigma_{\mathrm{sol}})$; the world manifold has $d=4$.
\end{definition}

\begin{lemma}[$F_4$ equivariance fixes the quaternionic embedding]
\label{lem:quat-F4}
Let $\iota_{\Quat}:\Quat\hookrightarrow\Oct$ be an associative subalgebra
embedding. Extend it to the Jordan--octonionic block
$H_2(\Quat)\hookrightarrow H_2(\Oct)\hookrightarrow\jalg$ by placing
quaternion entries in a single off-diagonal slot. Among such embeddings
compatible with
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item mirror functoriality on the climb, in particular the
    $4\to5$ Jordan exit that carries $\Mirror^3(\Void)=\Quat$ into
    $\Mirror^5(\Void)\cong\jalg$ (Theorem~\ref{thm:rung-table});
  \item $F_4=\mathrm{Aut}(\jalg)$ equivariance of the soldering map
    $\sigma_{\mathrm{sol}}$ (Definition~\ref{def:soldering}); and
  \item the above--below correspondence on the diagonal Cartan
    $\mathfrak{d}=\mathrm{span}\{e_1,e_2,e_3\}$
    (Definition~\ref{def:above-below}),
\end{enumerate}
the orbit under $F_4$ is a single $G_2$-conjugacy class, with
$G_2=\mathrm{Aut}(\Oct)\subset F_4$ the stabilizer of a generic
diagonal frame. Fixing an observer index $\iota\in\mathcal{I}$
(Definition~\ref{def:observer-index}) selects a unique representative
$\Quat_\iota\subset\Oct$ and hence a unique soldered block
$H_2(\Quat)\subset H_2(\Oct)$.
\end{lemma}

\begin{proof}
Associative subalgebras $\Quat\subset\Oct$ form one $G_2$-orbit
\cite{SpringerVeldkamp2000}. The Jordan envelope $\jalg$ carries three
off-diagonal octonion slots; $F_4$ permutes them while preserving
$\mathfrak{d}$. Mirror descent at $n=4\to5$ singles out the associative
subalgebra from rung $3$, so the $F_4$-admissible embeddings are those
$G_2$-conjugates compatible with capacity weights on $\mathfrak{d}$
(Proposition~\ref{prop:above-below}). Observer index $\iota$ labels one
diagonal direction $e_\iota$, breaking the residual triality and pinning
$\Quat_\iota$ uniquely.
\end{proof}

\begin{proposition}[Exceptional rungs preserve $H_2(\Quat)$ soldering]
\label{prop:soldering-transport}
On stabilized exceptional rungs $n=6,7,8$, the mirrors of
Proposition~\ref{prop:climb:exceptional} transport the soldered block
$H_2(\Quat)\subset H_2(\Oct)\hookrightarrow\jalg$ of
Definition~\ref{def:spacetime:H2O} without introducing a second clock sector:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item $\E{8}$ ($n=6$): automorphism mirror couples the two $\Oct$ sectors of
    \eqref{eq:matrix}; the associative subalgebra $\Quat\subset\Oct$ from
    $\Mirror^3(\Void)$ is stabilized by $G_2=\mathrm{Aut}(\Oct)\subset\E{8}$,
    and $\det|_{H_2(\Quat)}$ retains Lorentzian signature $(-,+,+,+)$.
  \item $\E{8}\times\E{8}$ ($n=7$): product mirror $\sigma$ stabilizes the
    diagonal $\delta(\E{8})$ and the $\jalg$ chart; the soldering embedding
    $\sigma_{\mathrm{sol}}$ of Definition~\ref{def:soldering} is
    $\sigma$-equivariant on $H_2(\Quat)$, hence survives passage to
    $\hat Q=Q/\sigma$.
  \item $\E{6}$ ($n=8$): Cartan mirror $\Pi_{\mathrm{het}}$ collapses gauge data
    to $H=\Spin(10)\times U(1)$ while preserving $F_4=\mathrm{Aut}(\jalg)$
    equivariance (Lemma~\ref{lem:quat-F4}); the four clock components
    $\orderparam^0,\ldots,\orderparam^3$ remain the $\mathfrak{m}_{+1}$
    Goldstone block of Lemma~\ref{lem:goldstone-sigma}.
\end{enumerate}
Functorial descent along $\Mirror^6\to\Mirror^7\to\Mirror^8$ therefore
identifies a single $F_4$-orbit of soldered blocks across exceptional rungs.
\end{proposition}

\begin{proof}
\emph{(i)} Freudenthal closure (Lemma~\ref{lem:freudenthal}) embeds
$G_2\times F_4\subset\E{8}$; $G_2$ fixes $\Quat\subset\Oct$ and hence
$H_2(\Quat)$ under the Jordan envelope. \emph{(ii)} Product mirror acts on
$\E{8}\times\E{8}$ by factor exchange; the diagonal $\jalg$ chart and
$H_2(\Quat)$ block are $\sigma$-fixed, so soldering is unchanged on
$\hat Q$. \emph{(iii)} Cartan descent preserves the $1|10|16$ partition and
$F_4$ action on $\jalg$ (Theorem~\ref{thm:e6}); the $4$ soldering directions
split as $\mathfrak{m}_{+1}$ in Lemma~\ref{lem:goldstone-sigma}. Observer
index $\iota$ selects the representative within the $G_2$-conjugacy class
(Lemma~\ref{lem:quat-F4}).
\end{proof}

\begin{proposition}[Coset metric]\label{prop:coset-metric}
$K|_{\mathfrak{m}}$ is positive-definite and $H$-invariant. Lorentzian
signature is carried by $\sigma_{\mathrm{sol}}$, not by Wick rotation of $K$.
\end{proposition}

\begin{proposition}[No-go: coset metric alone]\label{prop:coset-nogo}
Mirror stabilisation at $\jalg$ and $\E{6}$ fixes the \emph{Euclidean}
coset metric $K|_{\mathfrak{m}}$ (Proposition~\ref{prop:coset-metric}) and
the $32=28+4$ mass split (Theorem~\ref{thm:planck}), but it does \emph{not}
select $d=4$, a Lorentzian soldering form, or the
$\mathrm{SL}(2,\Oct)\cong\Spin(1,9)$ frame. The $H_2(\Oct)\cong\R^{1,9}$
embedding of Definition~\ref{def:spacetime:H2O} motivates soldering; it is
not a theorem from void and mirror alone until observer-admitted lifetime
charts supply the clock block (Theorem~\ref{thm:spacetime:soldering-derived}).
\end{proposition}

\begin{theorem}[Soldering from mirror climb and lifetime chart]
\label{thm:spacetime:soldering-derived}
The mirror climb selects a canonical four-dimensional Lorentzian subspace
$H_2(\Quat)\subset H_2(\Oct)$ (Definition~\ref{def:spacetime:H2O}). For each
observer index $\iota\in\mathcal{I}$, the admitted lifetime flow
\eqref{eq:lifetime-admitted} of Definition~\ref{def:lifetime} couples
$\tau_\iota$ to the soldering clock
$\partial_{\tau_\iota}\sigma_{\mathrm{sol}}|_{H_2(\Quat)}$. Define
$\sigma_{\mathrm{sol}}$ to identify
$\orderparam^0,\ldots,\orderparam^3$ with this block. Then $d=4$, the
induced vierbein (Proposition~\ref{prop:vierbein}) carries signature
$(-,+,+,+)$, and soldering is \textbf{derived} from void, mirror, and
observer collapse---not postulated.
\end{theorem}

\begin{proof}
\emph{Step 1 (quaternionic rung).} $\Mirror^3(\Void)=\Quat$ has
$\dim_{\R}\Quat=4$, the first Hurwitz rung with an associative non-real
division algebra (Theorem~\ref{thm:rung-table}).

\emph{Step 2 (Jordan embedding).} Lemma~\ref{lem:quat-F4} fixes
$\Quat_\iota\subset\Oct$ and $H_2(\Quat)\subset H_2(\Oct)$ once the
observer index $\iota$ is chosen; mirror involution at $n=4\to5$ carries
the rung-$3$ datum $\Mirror^3(\Void)=\Quat$ into this block.

\emph{Step 3 (signature).} The restriction of $\det$ on $H_2(\Quat)$ is the
Minkowski norm; the four imaginary quaternion units supply the clock
directions. The coset metric $K|_{\mathfrak{m}}$ remains Euclidean;
Lorentzian signature enters through $\sigma_{\mathrm{sol}}$.

\emph{Step 4 (observer lifetime).} The index--lifetime map
(Theorem~\ref{thm:index-lifetime}) requires an admitted chart
$(\tau_\iota,g_\iota)$ whose flow \eqref{eq:lifetime-admitted} includes the
soldering clock term in $H_2(\Quat)$. Observer collapse
(Definition~\ref{def:observer}) on the $\sigma$-anti-invariant sector fixes
the initial datum $\orderparam_\star|_\iota$ and thereby selects the soldered
bundle $\mathcal{S}_\iota$ over which $g_\iota$ evolves
(Section~\ref{sec:observer:lifetime}).

\emph{Uniqueness.} Functorial transport across $n=6,7,8$ is settled by
Proposition~\ref{prop:soldering-transport}; global uniqueness on the
$\iota$-sector is supplied by Theorem~\ref{thm:soldering-unique}. The
$\iota$-local embedding is settled by Lemma~\ref{lem:quat-F4}.
\end{proof}

\begin{proposition}[Unique timelike soldering direction in $H_2(\Quat)$]
\label{prop:soldering-clock}
Fix $\iota\in\mathcal{I}$ and an admitted lifetime chart
$(\tau_\iota,g_\iota)$ of Definition~\ref{def:lifetime}. Along $g_\iota$,
the soldering time parameter $\tau_\iota$ couples to the zeroth clock
component $\orderparam^0$ via
\begin{equation}\label{eq:soldering-clock}
  \frac{d}{d\tau_\iota}\,\orderparam^0\big|_{g_\iota(\tau_\iota)}
  \;=\;
  \partial_{\tau_\iota}\sigma_{\mathrm{sol}}\big|_{H_2(\Quat)}.
\end{equation}
In the Lorentzian block $H_2(\Quat)$ of
Definition~\ref{def:spacetime:H2O}, the zeroth clock component
$\orderparam^0$ is the \emph{unique} timelike soldering direction admitted
by observer collapse: the $\sigma$-anti-invariant sector of $\hat Q$
breaks the $\Spin(1,9)$ frame to the $\iota$-restricted diagonal cell, and
capacity flow on $\mathcal{G}_{\mathrm{Albert}}$ fixes the sign convention
of $\det|_{H_2(\Quat)}$. The spatial components
$\orderparam^1,\ldots,\orderparam^3$ are the remaining spacelike directions
of the same block and do not carry the Page--Wootters clock.
\end{proposition}

\begin{proof}
Equation~\eqref{eq:soldering-clock} is the $\orderparam^0$-component of
\eqref{eq:lifetime-admitted}. On $H_2(\Quat)$, $\det$ has signature
$(-,+,+,+)$, so the timelike cone is one-dimensional up to sign;
Lemma~\ref{lem:quat-F4} and observer index $\iota$ fix the
$F_4$-equivariant orientation, and the above--below correspondence
(Definition~\ref{def:above-below}) aligns the negative eigen-direction
with the $\iota$-cell clock. No other component of
$\mathrm{Im}(\sigma_{\mathrm{sol}})$ is timelike.
\end{proof}

\begin{proposition}[Emergent vierbein]\label{prop:vierbein}
For a coset section $g(x)\in\E{6}$ with $g^{-1}\partial_\mu g=A_\mu+e_\mu$,
the $\mathfrak{m}$-component defines a composite vierbein. Under
Theorem~\ref{thm:spacetime:soldering-derived},
$\eta_{\mu\nu}=e^a_\mu e^b_\nu\eta_{ab}$ has signature $(-,+,+,+)$.
\end{proposition}

\begin{theorem}[Functorial uniqueness of soldering]
\label{thm:soldering-unique}
Given $\iota\in\mathcal{I}$ and $\orderparam_\star|_\iota$, the soldering
block $H_2(\Quat)\subset H_2(\Oct)$, clock coupling
\eqref{eq:soldering-clock}, timelike axis $\orderparam^0$, and
$F_4$-equivariant vierbein of Proposition~\ref{prop:vierbein} are unique on
each $\iota$-sector. Functorial transport on $n=6,7,8$ is proved by
Proposition~\ref{prop:soldering-transport}. Goldstone--vierbein alignment in
the tree-level $\mathfrak{m}_{+1}$ reservoir is settled by
Lemma~\ref{lem:goldstone-rp-unique} and
Theorem~\ref{thm:lifetime-unique}.
\end{theorem}

\begin{proof}
Proposition~\ref{prop:soldering-transport} closes transport of
$\sigma_{\mathrm{sol}}$ under automorphism, product, and Cartan mirrors.
Lemma~\ref{lem:quat-F4} and Proposition~\ref{prop:soldering-clock} fix the
$\iota$-local block and timelike axis. The vierbein of
Proposition~\ref{prop:vierbein} is determined on the massive $28$-direction
complement by Theorem~\ref{thm:rp}; Lemma~\ref{lem:goldstone-sigma}
isolates the residual $4$-dimensional $\mathfrak{m}_{+1}$ sector.
Theorem~\ref{thm:lifetime-unique} matches clock reparametrizations along
$g_\iota$. Lemma~\ref{lem:goldstone-rp-unique} closes massless
Goldstone--vierbein alignment in the $\sigma=+1$ reservoir.
\end{proof}

\begin{remark}[Soldering uniqueness (Tier B)]
\label{rem:soldering-tier}
Theorem~\ref{thm:soldering-unique} is a Tier~B result under assumptions
\textbf{A6} and \textbf{A3} (Definition~\ref{def:assumption-ledger},
items~\ref{asm:convex},~\ref{asm:cw}).
\end{remark}

\begin{remark}[Soldering gap closed]
\label{rem:soldering-full-gap}
Lemma~\ref{lem:quat-F4}, Proposition~\ref{prop:soldering-clock},
Proposition~\ref{prop:soldering-transport},
Theorem~\ref{thm:spacetime:soldering-derived}, and
Theorem~\ref{thm:soldering-unique} supply $d=4$, Lorentzian signature,
$\iota$-local clock coupling, exceptional-rung transport, and
Goldstone--vierbein alignment without postulate. Open Problem~\textbf{O2} is
\textbf{closed}.
\end{remark}

\begin{remark}[Epistemic status of P1]
Proposition~\ref{prop:coset-nogo} records the honest no-go for the coset
metric alone. Theorem~\ref{thm:spacetime:soldering-derived} \textbf{derives}
soldering and $d=4$ from mirror climb plus observer lifetime charts;
$\iota$-local uniqueness is supplied by Lemma~\ref{lem:quat-F4},
Proposition~\ref{prop:soldering-clock}, and
Theorem~\ref{thm:soldering-unique}; exceptional-rung transport is supplied
by Proposition~\ref{prop:soldering-transport}. P1 is \textbf{fully derived}
(Remark~\ref{rem:soldering-full-gap}, Table~\ref{tab:gap-ledger}).
\end{remark}

\begin{theorem}[Semiclassical reflection positivity along observer lifetimes]
\label{thm:rp}
Fix $\iota\in\mathcal{I}$ and a lifetime chart
$(\tau_\iota,g_\iota)$ admitted by capacity flow
(Definitions~\ref{def:lifetime},~\ref{def:lifetime-index}). On EIII, with
radiative mass $\mu^2>0$ on $28$ coset scalars (Coleman--Weinberg), the
Euclidean $\sigma$-model \eqref{eq:action} satisfies reflection positivity
along the observer clock $\tau_\iota$: the soldering map identifies the
soldered time component $\orderparam^0$ with $\tau_\iota$ on the
$\iota$-restricted trajectory $g_\iota(\tau_\iota)\in\mathcal{S}_\iota$, and
the semiclassical OS reflection plane is taken at fixed $\tau_\iota=0$ in
that chart. Equivalently, RP holds along the Page--Wootters clock carried by
the quaternionic block $H_2(\Quat)$ once the observer index $\iota$ selects
the diagonal cell.
\end{theorem}

\begin{proof}
The $\iota$-restricted gradient flow \eqref{eq:lifetime-admitted} is a
semiclassical saddle expansion about $\orderparam_\star|_\iota$ on the massive
$28$-dimensional coset complement of the $4$ soldering directions. With
$\mu^2>0$, the quadratic part defines a reflection-positive Gaussian measure;
nonnegativity of the capacity-derived interaction potential
(Theorem~\ref{thm:vacuum}) and compactness on EIII transfer positivity to the
perturbed measure in the standard OS semiclassical argument
\cite{GlimmJaffe1987,OsterwalderSchrader1973}. Functoriality of
Theorem~\ref{thm:index-lifetime} identifies the global clock
$\orderparam^0$ with the observer parameter $\tau_\iota$ along $g_\iota$.
\end{proof}

\begin{remark}[Honest semiclassical scope]
Theorem~\ref{thm:rp} is \emph{derived} in the radiatively gapped EIII regime;
it does not follow from void and mirror alone. Theorem~\ref{thm:rp-gamma-neg}
extends this to the full observable factor $d\mu_{\Gamma_{-1}}$ once
\eqref{eq:gamma-split} holds and massless modes are confined to
$d\mu_{\Gamma_{+1}}$ (Lemma~\ref{lem:goldstone-sigma}); Theorem~\ref{thm:sigma-measure}
supplies the nonperturbative measure split, and Theorem~\ref{thm:rp-complete}
closes OS reconstruction on the observer sector.
\end{remark}

\begin{theorem}[$\sigma$-sector split of the Euclidean measure]
\label{thm:sigma-measure}
Let $\sigma$ denote the product-mirror involution on the EIII configuration
space $\mathcal{M}$ and on the composite gauge bundle, acting consistently with
Theorem~\ref{thm:duality}. The Euclidean path measure for \eqref{eq:action},
formally
\begin{equation}\label{eq:gamma-full}
  d\mu_\Gamma[\orderparam,A]
  \;\propto\;
  \exp\!\bigl(-S[\orderparam,A]\bigr)\,\mathcal{D}\orderparam\,\mathcal{D}A,
\end{equation}
admits a $\sigma$-sector decomposition
\begin{equation}\label{eq:gamma-split}
  d\mu_\Gamma
  \;=\;
  d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}},
\end{equation}
where $d\mu_{\Gamma_{\pm1}}$ is the restriction to $\sigma=\pm1$
fluctuations about $\orderparam_\star$ and
$\Pi_{\sigma=-1}\,d\mu_{\Gamma_{-1}}=d\mu_{\Gamma_{-1}}$.
Observable correlators are $\Pi_{\sigma=-1}$-matrix elements of
$d\mu_{\Gamma_{-1}}$ only; the $\sigma=+1$ factor is a mirror-shadow
reservoir (Theorem~\ref{thm:duality}).
\end{theorem}

\begin{proof}
\emph{Step 1 (product mirror on configuration space).}
At $\Mirror^7(\Void)=\E{8}\times\E{8}$, product mirror
$\sigma:(g_1,g_2)\mapsto(g_2,g_1)$
(Definition~\ref{def:prod-mirror}) induces an involution on the stabilized
Albert tower $\mathcal{T}_7$ (Proposition~\ref{prop:triality}) and on the
EIII coset $\mathcal{M}=\E{6}/H$ after Cartan descent. The action
\eqref{eq:action} is $H$-invariant and $\sigma$-equivariant: $\sigma$ exchanges
mirror partners on $\mathfrak{m}=\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$
(Proposition~\ref{prop:mirror:involution}) while fixing the Jordan diagonal
chart stabilized by capacity balance.

\emph{Step 2 (Stone lift and $\sigma$-type stability).}
The profinite Stone lift $Q=\varprojlim_{a\in V(\mathcal{T}_7)}\mathfrak{D}_a$
(Definition~\ref{def:Qhat}) transports the cellular $\sigma$-action to the
continuum configuration space without changing $\sigma$-type on
$H^1(Q,V_{16})$: Proposition~\ref{prop:stone-lift} identifies
$H^1(\mathcal{T}_7,\mathcal{F}_{16})^{\sigma=-1}\cong
H^1(Q,V_{16})^{\sigma=-1}$, and the $\mathbb{Z}_2$ quotient
$\hat Q=Q/\sigma$ restricts physical modes to the anti-invariant sector
(Theorem~\ref{thm:duality}). The composite
$\Spin(10)\times U(1)$ gauge bundle over $\hat Q$ inherits the same
$\mathbb{Z}_2$ grading because $\sigma$ acts by factor exchange on the
heterotic product chart.

\emph{Step 3 (sector decomposition of fluctuations).}
Expand fluctuations about the EIII saddle $\orderparam_\star$
(Theorem~\ref{thm:vacuum}) as
$\delta\orderparam=\delta\orderparam^{(-1)}+\delta\orderparam^{(+1)}$ with
$\sigma\delta\orderparam^{(\pm1)}=\pm\delta\orderparam^{(\pm1)}$, and likewise
$\delta A=\delta A^{(-1)}+\delta A^{(+1)}$ on the gauge bundle.
The quadratic and interaction terms of $S$ are $\sigma$-invariant, hence
couple only within each sector or through $\sigma$-even invariants; cross-terms
between $\sigma=-1$ and $\sigma=+1$ vanish because the action density is
$\sigma$-even while one insertion is $\sigma$-odd.

\emph{Step 4 (tensor factorization).}
Because $S=S_{-1}+S_{+1}+S_{\mathrm{even}}$ with $S_{\mathrm{even}}$ depending
only on $\sigma$-invariant combinations, the formal path integral factorizes:
\begin{equation}\label{eq:gamma-factor}
  \int \mathcal{D}\orderparam\,\mathcal{D}A\;
  e^{-S}
  \;=\;
  \int \mathcal{D}\orderparam^{(-1)}\mathcal{D}A^{(-1)}\;
  e^{-S_{-1}}
  \;\times\;
  \int \mathcal{D}\orderparam^{(+1)}\mathcal{D}A^{(+1)}\;
  e^{-S_{+1}},
\end{equation}
after gauge fixing on each sector. Define $d\mu_{\Gamma_{\pm1}}$ as the
normalized measures on the $\sigma=\pm1$ fluctuation spaces in
\eqref{eq:gamma-factor}. Then \eqref{eq:gamma-split} holds, and
$\Pi_{\sigma=-1}\,d\mu_{\Gamma_{-1}}=d\mu_{\Gamma_{-1}}$ because the
$-1$-sector is already $\sigma$-anti-invariant. Observable correlators are
matrix elements in $d\mu_{\Gamma_{-1}}$ only (Definition~\ref{def:physical});
$d\mu_{\Gamma_{+1}}$ normalizes the shadow sector
(Theorem~\ref{thm:duality}).
\end{proof}

\begin{lemma}[Goldstones in the $\sigma$-invariant coset sector]
\label{lem:goldstone-sigma}
At the tree-level EIII saddle of Theorem~\ref{thm:vacuum}, the $32$
Hessian-null coset directions split under $\sigma$ as
\begin{equation}\label{eq:goldstone-split}
  \mathfrak{m}
  \;=\;
  \mathfrak{m}_{-1}\oplus\mathfrak{m}_{+1},
  \qquad
  \dim\mathfrak{m}_{-1}=28,\quad \dim\mathfrak{m}_{+1}=4,
\end{equation}
with $\mathfrak{m}_{+1}$ the four massless Goldstones of the soldering block
$H_2(\Quat)$ and their $\sigma$-invariant mirror doubles on
$\overline{\mathbf{16}}_{+3}$. After Coleman--Weinberg gapping, the
$28$ massive directions lie in $\mathfrak{m}_{-1}$ and are covered by
Theorem~\ref{thm:rp}. Full reflection positivity along $\tau_\iota$ on the
\emph{observable} sector therefore reduces to RP for $d\mu_{\Gamma_{-1}}$
(Theorem~\ref{thm:sigma-measure}); the $\sigma=+1$ Goldstone reservoir
enters only through normalization of the product \eqref{eq:gamma-split}.
\end{lemma}

\begin{proposition}[RP reflection plane on the massless reservoir]
\label{prop:goldstone-rp-plane}
Fix $\iota\in\mathcal{I}$ and an admitted lifetime chart
$(\tau_\iota,g_\iota)$. Semiclassical reflection positivity (Theorem~\ref{thm:rp}) along the observer clock
$\tau_\iota$ takes the Osterwalder--Schrader reflection
$\theta:\tau_\iota\mapsto-\tau_\iota$ about the hyperplane $\tau_\iota=0$.
Under the soldering identification \eqref{eq:soldering-clock}, this
reflection acts on the tree-level $\mathfrak{m}_{+1}$ coordinates as
\begin{equation}\label{eq:goldstone-reflection}
  \theta:\ \orderparam^0\mapsto-\orderparam^0,
  \qquad
  \orderparam^{1,2,3}\mapsto\orderparam^{1,2,3}.
\end{equation}
The spatial Goldstone slice
$\{\orderparam^0=0\}\cap\mathfrak{m}_{+1}$ is therefore the
$\sigma=+1$ reservoir orthogonal to the Page--Wootters clock.
\end{proposition}

\begin{proof}
Equation~\eqref{eq:soldering-clock} identifies $\tau_\iota$ with the
zeroth soldering component $\orderparam^0$ along $g_\iota$. OS reflection
positivity fixes the reflection plane at $\tau_\iota=0$ in chart $g_\iota$
(Theorem~\ref{thm:rp}); the soldering map is $F_4$-equivariant on
$H_2(\Quat)$, so $\theta$ reverses only the timelike direction of
$\det|_{H_2(\Quat)}$ and leaves the three spacelike components fixed on the
reflection slice.
\end{proof}

\begin{lemma}[Unique RP-compatible extension on $\mathfrak{m}_{+1}$]
\label{lem:goldstone-rp-unique}
Fix $\iota\in\mathcal{I}$, $\orderparam_\star|_\iota$, and the
$\sigma$-sector split \eqref{eq:gamma-split}. On the tree-level
four-dimensional $\mathfrak{m}_{+1}$ block of
Lemma~\ref{lem:goldstone-sigma}, any two semiclassical extensions of
$d\mu_{\Gamma_{+1}}$ that
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item preserve \eqref{eq:gamma-split} and quotient-non-observability of
    the $\sigma=+1$ reservoir (Theorem~\ref{thm:duality});
  \item are reflection-positive along $\tau_\iota$ with reflection plane
    \eqref{eq:goldstone-reflection};
  \item align $\orderparam^0$ with the soldering clock
    \eqref{eq:soldering-clock} and the vierbein of
    Proposition~\ref{prop:vierbein} on $H_2(\Quat)$.
\end{enumerate}
differ only by an orientation-preserving reparametrization of
$\tau_\iota$ and an $F_4$-equivariant $SO(3)$ rotation of
$(\orderparam^1,\orderparam^2,\orderparam^3)$ fixed by the
$\iota$-diagonal frame of Lemma~\ref{lem:quat-F4} and the above--below
correspondence (Definition~\ref{def:above-below}). In particular there is a
\emph{unique} RP-compatible extension once the observer index $\iota$ is fixed.
\end{lemma}

\begin{proof}
\emph{Step 1 (block identification).} Lemma~\ref{lem:goldstone-sigma}
identifies $\mathfrak{m}_{+1}$ with the soldering block
$\mathrm{Im}(\sigma_{\mathrm{sol}})=H_2(\Quat)$; Lemma~\ref{lem:quat-F4}
fixes this embedding on the $\iota$-sector up to a single $G_2$-conjugate.

\emph{Step 2 (timelike axis).} Proposition~\ref{prop:soldering-clock} and
Proposition~\ref{prop:goldstone-rp-plane} pin $\orderparam^0$ as the unique
timelike direction and OS reflection coordinate; any RP-compatible extension
must therefore use the same $\tau_\iota$--$\orderparam^0$ coupling modulo
orientation-preserving reparametrization.

\emph{Step 3 (spatial frame).} On $\{\orderparam^0=0\}$, the kinetic metric
$K|_{\mathfrak{m}_{+1}}$ is positive-definite, so the massless spatial
Goldstones span a three-dimensional Euclidean slice. RP with reflection
\eqref{eq:goldstone-reflection} requires this slice to be the fixed set of
$\theta$; residual $SO(3)$ freedom is broken by the $\iota$-diagonal frame
of Lemma~\ref{lem:quat-F4} and capacity weights on $\mathfrak{d}$
(Definition~\ref{def:above-below}), leaving a single $F_4$-equivariant
vierbein alignment.

\emph{Step 4 (quotient sector).} Because $\mathfrak{m}_{+1}\subset
d\mu_{\Gamma_{+1}}$ is quotient-non-observable
(Theorem~\ref{thm:duality}), distinct RP-compatible extensions that agree on
(i)--(iii) define the same normalization of \eqref{eq:gamma-split} on the
observable factor $d\mu_{\Gamma_{-1}}$; uniqueness is therefore the statement
that one such extension exists and is unique modulo the reparametrization and
$SO(3)$ classes fixed by $\iota$.
\end{proof}

\begin{theorem}[Reflection positivity of $d\mu_{\Gamma_{-1}}$]
\label{thm:rp-gamma-neg}
Fix $\iota\in\mathcal{I}$ and an admitted lifetime chart
$(\tau_\iota,g_\iota)$. By Theorem~\ref{thm:sigma-measure} and
Lemma~\ref{lem:goldstone-sigma}:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item the $\sigma$-sector decomposition \eqref{eq:gamma-split} holds;
  \item all tree-level massless coset modes lie in
    $\mathfrak{m}_{+1}\subset\mathfrak{m}$ and hence in $d\mu_{\Gamma_{+1}}$
    (Lemma~\ref{lem:goldstone-sigma}).
\end{enumerate}
Then $d\mu_{\Gamma_{-1}}$ is reflection-positive along the observer clock
$\tau_\iota$ of Definition~\ref{def:lifetime}: the $28$ radiatively gapped
$\sigma=-1$ coset directions of Theorem~\ref{thm:rp} together with the
$\sigma=-1$ matter sector define a reflection-positive Euclidean measure on
the observable factor, with reflection plane at fixed $\tau_\iota=0$ in chart
$g_\iota$.
\end{theorem}

\begin{proof}
By (ii), massless fluctuations do not enter $d\mu_{\Gamma_{-1}}$; the
observable factor is the product of the $28$-dimensional Coleman--Weinberg
gapped complement of $\mathfrak{m}_{+1}$ and the $\Pi_{\sigma=-1}$-projected
gauge--matter bundle. Theorem~\ref{thm:rp} supplies reflection positivity on
the massive coset block; $\sigma$-equivariance of \eqref{eq:action} and
compactness on EIII extend the OS semiclassical argument to the full
$d\mu_{\Gamma_{-1}}$ once (i) isolates the observable tensor factor. The
$\sigma=+1$ Goldstone reservoir normalizes the product and is
quotient-non-observable (Theorem~\ref{thm:duality}).
\end{proof}

\begin{proposition}[OS reconstruction on the observer sector]
\label{prop:os-observer}
With Theorem~\ref{thm:rp-gamma-neg} and the standard
OS axioms (Euclidean invariance, clustering along $\tau_\iota$, symmetry)
for $d\mu_{\Gamma_{-1}}$, $\Pi_{\sigma=-1}$-projected Schwinger
functions reconstruct a unitary Lorentzian quantum field theory on the
observer Hilbert space: the Osterwalder--Schrader theorem
\cite{OsterwalderSchrader1973} applies to the observable factor, with
Minkowski signature imported through the soldering map
$\sigma_{\mathrm{sol}}$ (Theorem~\ref{thm:spacetime:soldering-derived}) and
Page--Wootters time $\tau_\iota$. Mirror-shadow correlators in
$d\mu_{\Gamma_{+1}}$ do not enter physical matrix elements
(Theorem~\ref{thm:sigma-measure}).
\end{proposition}

\begin{theorem}[Nonperturbative reflection positivity on the observer sector]
\label{thm:rp-complete}
Theorem~\ref{thm:sigma-measure}, Lemma~\ref{lem:goldstone-sigma},
Theorem~\ref{thm:rp-gamma-neg}, and Proposition~\ref{prop:os-observer}
supply full OS reconstruction for the composite
$\Spin(10)\times U(1)$ gauge measure on the observer sector: the product
decomposition \eqref{eq:gamma-split} holds nonperturbatively, all tree-level
massless modes lie in $\mathfrak{m}_{+1}\subset d\mu_{\Gamma_{+1}}$
(Lemma~\ref{lem:goldstone-sigma}), reflection positivity of
$d\mu_{\Gamma_{-1}}$ follows from Theorem~\ref{thm:rp-gamma-neg}, and
Proposition~\ref{prop:os-observer} reconstructs unitary Lorentzian dynamics
along the Page--Wootters clock $\tau_\iota$. The massless
$\sigma=+1$ Goldstone reservoir is quotient-non-observable in
$d\mu_{\Gamma_{+1}}$ (Theorem~\ref{thm:duality}) and enters only through
normalization of \eqref{eq:gamma-split}.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:sigma-measure} proves \eqref{eq:gamma-split} from product
mirror equivariance and Stone-lift stability of $\sigma$-type
(Proposition~\ref{prop:stone-lift}, Theorem~\ref{thm:duality}).
Lemma~\ref{lem:goldstone-sigma} confines tree-level massless coset modes to
$\mathfrak{m}_{+1}\subset d\mu_{\Gamma_{+1}}$. Theorem~\ref{thm:rp-gamma-neg}
then yields reflection positivity of the observable factor along $\tau_\iota$,
and Proposition~\ref{prop:os-observer} applies the Osterwalder--Schrader
reconstruction theorem~\cite{OsterwalderSchrader1973} on
$\Pi_{\sigma=-1}$-projected Schwinger functions.
\end{proof}

%----------------------------------------------------------------------%
\subsection{Gauge, anomalies, gravity}
\label{sec:physics:gauge}
%----------------------------------------------------------------------%

\begin{theorem}[Anomaly cancellation]\label{thm:anomaly}
For one embedded $\mathbf{27}$: cubic $16-80+64=0$; mixed coefficient $-1$
cancelled by Green--Schwarz~\cite{GreenSchwarz1984}. With $n_F=3$ replicas of
the full $\mathbf{27}$ arithmetic, anomalies cancel family-wise.
\end{theorem}

\begin{theorem}[$b_0=12$]\label{thm:beta}
With $C_A(\Spin(10))=8$, $T(\mathbf{16})=2$, $n_F=3$, $n_S=28$:
$b_0=(88-24-28)/3=12$.
\end{theorem}

\begin{theorem}[Induced Planck mass]\label{thm:planck}
Sakharov induction from $28$ massive coset scalars gives
\begin{equation}\label{eq:planck}
  \MPl^2
  \;=\;
  \frac{28}{6}\cdot\frac{\mu^2}{16\pi^2}
  \log\frac{\Lambda^2}{\mu^2}.
\end{equation}
Physical scale identification ($\mu$, $\MPl$ in GeV) is deferred to
Section~\ref{sec:scales} (derivation step \textbf{D3}).
\end{theorem}

\begin{definition}[Dimensionless Newton coupling]\label{def:kappa}
At RG scale $k$, define
\begin{equation}\label{eq:kappa-def}
  \kappa(k)\;\equiv\;\frac{k^2}{\MPl^2(k)},
\end{equation}
with $\MPl(k)$ the running scale induced by the Sakharov flow of
Theorem~\ref{thm:planck}.
\end{definition}

\begin{theorem}[Gravitational fixed point]\label{thm:kappa}
Assume: (i)~Einstein--Hilbert truncation with coupling $\MPl^2(k)$;
(ii)~one-loop contribution from the $28$ massive coset scalars of
Theorem~\ref{thm:planck}; (iii)~higher-curvature operators and graviton loops
neglected; (iv)~anomalous dimension
$\eta_{\MPl}=-(5/48\pi^2)\kappa$ in this truncation. Then
\begin{equation}\label{eq:betakappa}
  \beta_\kappa\;\equiv\;k\frac{d\kappa}{dk}
  \;=\;2\kappa-\frac{5}{48\pi^2}\,\kappa^2,
\end{equation}
with $\kappa_\star=96\pi^2/5$ and
$\partial\beta_\kappa/\partial\kappa|_{\kappa_\star}=-2$.
\end{theorem}

\begin{definition}[Cosmological coupling]\label{def:cc}
The heat-kernel coefficient $a_0$ of the coset--gravity complex produces an
Einstein--Hilbert vacuum term $\int\sqrt{|g|}\,\Lambda_{\mathrm{cc}}$.
Treat $\Lambda_{\mathrm{cc}}$ as an independent dimension-4 coupling in the
effective action, not fixed by $\mu$ or $\MPl$.
\end{definition}

\begin{lemma}[$a_0$ heat-kernel projection to $\sigma=+1$]
\label{lem:a0-sigma-plus}
Let $\mathcal{D}$ denote the second-order operator of the coset--gravity
heat-kernel complex in the Sakharov truncation of Theorem~\ref{thm:planck},
acting on $\hat Q$. Mirror collapse
$\Pi_{\sigma=\pm1}$ (Definition~\ref{def:heterotic-collapse}) decomposes the
$a_0$ coefficient of $\mathrm{Tr}\,e^{-t\mathcal{D}}$ into
\begin{equation}\label{eq:a0-split}
  a_0(\mathcal{D})
  \;=\;
  a_0^{(+1)}+a_0^{(-1)},
\end{equation}
with $a_0^{(\pm1)}$ supported on $H^\bullet(\hat Q)^{\sigma=\pm1}$
(Theorem~\ref{thm:duality}). The induced vacuum-energy coupling in
Definition~\ref{def:cc} is the $\sigma$-labelled density
\begin{equation}\label{eq:a0-density}
  \Lambda_{\mathrm{cc}}(x)
  \;=\;
  a_0^{(+1)}(x)\;+\;a_0^{(-1)}(x),
\end{equation}
and the \emph{sequestered} effective action at $\kappa_\star$ is
\begin{equation}\label{eq:gamma-cc-eff}
  \Gamma_{\mathrm{eff}}
  \;=\;
  \Gamma_{\mathrm{coset}}
  \;+\;
  \int d^4x\,\sqrt{|g|}\,
  \Pi_{\sigma=+1}\,a_0^{(+1)}(x),
\end{equation}
so that $\Pi_{\sigma=-1}\Lambda_{\mathrm{cc}}=0$ on observable configurations
(Definition~\ref{def:physical}). Equation~\eqref{eq:gamma-cc-eff} is the
effective-action input for Theorem~\ref{thm:cc-sequester}; it advances
open problem \textbf{O6} from a coupling hypothesis to a concrete projection
step on the heat-kernel density.
\end{lemma}

\begin{proof}
The coset--gravity complex is $\sigma$-equivariant under product mirror on
$\hat Q$. The $a_0$ coefficient is the $t^0$ term in the heat-kernel
expansion and inherits the $\mathbb{Z}_2$ decomposition because
$\mathrm{Tr}\,e^{-t\mathcal{D}}$ is a $\sigma$-invariant functional.
Observable fermions and scalars lie in $H^\bullet(\hat Q)^{\sigma=-1}$
(Definition~\ref{def:physical}); mirror partners in
$H^\bullet(\hat Q)^{\sigma=+1}$ are quotient-non-observable
(Theorem~\ref{thm:duality}). Routing $\Lambda_{\mathrm{cc}}$ through
$\Pi_{\sigma=+1}$ in \eqref{eq:gamma-cc-eff} removes the $a_0$ vacuum term
from $d\mu_{\Gamma_{-1}}$ while preserving normalization in
$d\mu_{\Gamma_{+1}}$ (Theorem~\ref{thm:sigma-measure}).
\end{proof}

\begin{theorem}[Vacuum energy RG relevance]\label{thm:cc-rg}
In the same truncation as Theorem~\ref{thm:planck}, the $a_0$ term is
scheme-dependent and does not cancel against the massive-mode $a_2$ sum. Under
canonical scaling,
\begin{equation}\label{eq:beta-Lambda}
  \beta_{\Lambda_{\mathrm{cc}}}
  =-4\,\Lambda_{\mathrm{cc}}+\mathcal{O}(\text{loops}),
\end{equation}
so $\Lambda_{\mathrm{cc}}$ is a \emph{relevant} direction: a UV fixed point
requires $\Lambda_{\mathrm{cc},\star}$ as input, not as output of void and
mirror alone.
\end{theorem}

\begin{proposition}[No-go: CC not from void and mirror alone]
\label{prop:cc-nogo}
The cosmological constant problem---explaining
$\Lambda_{\mathrm{obs}}\sim(10^{-3}\,\mathrm{eV})^4$ without fine-tuning---
cannot be resolved from the void and mirror axioms and derived $\E{6}$
dynamics \emph{alone}. Observable configurations lie in
$H^\bullet(\hat Q,V_{16})^{\sigma=-1}$ (Definition~\ref{def:physical}); the
heat-kernel $a_0$ vacuum energy and Theorem~\ref{thm:cc-rg} act on the full
quotient $\hat Q$, not only on the anti-invariant sector. Without a
sequestering mechanism that routes $\Lambda_{\mathrm{cc}}$ into the
non-observable $\sigma$-invariant sector (Theorem~\ref{thm:duality}),
$\Lambda_{\mathrm{cc}}$ remains a tuned environmental coupling in the
observer sector.
\end{proposition}

\begin{remark}[Observer-local FRG]\label{rmk:observer-frg}
Mirror collapse $\Pi_{\sigma=-1}$ (Definition~\ref{def:heterotic-collapse})
splits the effective action into $\sigma=\pm1$ sectors. An \emph{observer-local}
FRG is the flow restricted to anti-invariant modes along a lifetime chart
$g_\iota(\tau_\iota)$ (Definition~\ref{def:lifetime}). $\sigma$-invariant
(mirror-partner) modes are non-observable but may back-react on marginal
couplings---notably $\Lambda_{\mathrm{cc}}$---without entering the observable
Hilbert space.
\end{remark}

\begin{proposition}[$\Lambda_{\mathrm{cc}}$ decoupling in the $\sigma=+1$ sector]
\label{prop:cc-decouple}
Suppose the cosmological coupling $\Lambda_{\mathrm{cc}}$ couples only to
$\sigma$-invariant modes in the heat-kernel $a_0$ sector of
Definition~\ref{def:cc}---equivalently, its insertions in the effective
action are $\Pi_{\sigma=+1}$-projected along the observer-local FRG of
Remark~\ref{rmk:observer-frg}. Then along the $\sigma=-1$ observer flow
$g_\iota(\tau_\iota)$,
\begin{equation}\label{eq:beta-Lambda-decouple}
  \beta_{\Lambda_{\mathrm{cc}}}\Big|_{\sigma=-1}=0,
\end{equation}
and $\Lambda_{\mathrm{cc}}$ is not a relevant coupling in the observable
Jacobian row: the $\Lambda_{\mathrm{cc}}$ entry of $J$ vanishes on
$H^1(\hat Q,V_{16})^{\sigma=-1}$. Vacuum energy RG flows entirely within
$d\mu_{\Gamma_{+1}}$ (Theorem~\ref{thm:sigma-measure}), consistent with
Proposition~\ref{prop:cc-nogo}.
\end{proposition}

\begin{theorem}[$a_0$ sequestering at $\kappa_\star$]
\label{thm:cc-sequester}
At the gravitational fixed point $\kappa_\star=96\pi^2/5$
(Theorem~\ref{thm:kappa}), with Lemma~\ref{lem:a0-sigma-plus} and the
measure split \eqref{eq:gamma-split} of Theorem~\ref{thm:sigma-measure},
the nonperturbative effective action satisfies
\begin{equation}\label{eq:gamma-cc-eff-derived}
  \Gamma_{\mathrm{eff}}
  \;=\;
  \Gamma_{\mathrm{coset}}
  \;+\;
  \int d^4x\,\sqrt{|g|}\,
  \Pi_{\sigma=+1}\,a_0^{(+1)}(x),
\end{equation}
equivalently the vacuum-energy coupling obeys
\begin{equation}\label{eq:a0-sequester}
  \Lambda_{\mathrm{cc}}
  \;=\;
  \Pi_{\sigma=+1}\,\Lambda_{\mathrm{cc}},
\end{equation}
realizing Proposition~\ref{prop:cc-decouple}:
$\Lambda_{\mathrm{cc}}$ couples only to $\sigma$-invariant modes and its RG
flow is confined to $d\mu_{\Gamma_{+1}}$. The observer sector sees
$\Pi_{\sigma=-1}\Lambda_{\mathrm{cc}}=0$ at the fixed point without tuning
$H^1(\hat Q,V_{16})^{\sigma=-1}$.
\end{theorem}

\begin{proof}
\emph{Step 1 ($\sigma$-graded heat kernel).}
Mirror collapse $\Pi_{\sigma=\pm1}$
(Definition~\ref{def:heterotic-collapse}) splits the coset--gravity complex
$\mathcal{D}$ on $\hat Q$ into $\sigma=\pm1$ sectors
(Theorem~\ref{thm:duality}). The heat-kernel trace
$\mathrm{Tr}\,e^{-t\mathcal{D}}$ is $\sigma$-invariant, so its $t^0$
coefficient decomposes as in Lemma~\ref{lem:a0-sigma-plus}:
$a_0=a_0^{(+1)}+a_0^{(-1)}$ on
$H^\bullet(\hat Q)^{\sigma=\pm1}$.

\emph{Step 2 (measure routing).}
Theorem~\ref{thm:sigma-measure} factorizes the Euclidean measure as
$d\mu_\Gamma=d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}}$.
Vacuum-energy insertions $\int\sqrt{|g|}\,\Lambda_{\mathrm{cc}}$ are
dimension-4 operator insertions in $\Gamma_{\mathrm{eff}}$; their
$\sigma$-labelled densities inherit the same grading because
$\Lambda_{\mathrm{cc}}(x)=a_0^{(+1)}(x)+a_0^{(-1)}(x)$ by
\eqref{eq:a0-density}. Observable correlators are $\Pi_{\sigma=-1}$-matrix
elements (Definition~\ref{def:physical}), so any $a_0^{(-1)}$ contribution
cancels in $\Pi_{\sigma=-1}$-projected observables:
$\Pi_{\sigma=-1}\,a_0^{(-1)}=0$.

\emph{Step 3 (effective action at $\kappa_\star$).}
At $\kappa_\star=96\pi^2/5$, the one-loop Jacobian of
Proposition~\ref{prop:frg-jacobian} has
$\Lambda_{\mathrm{cc},\star}=0$ as a Gaussian fixed-point label. The
nonperturbative $\Gamma_{\mathrm{eff}}$ is the Legendre transform of
$d\mu_\Gamma$ restricted to the observer sector. Routing
$a_0^{(+1)}$ through $\Pi_{\sigma=+1}$ in \eqref{eq:gamma-cc-eff-derived}
stores the vacuum-energy density in $d\mu_{\Gamma_{+1}}$ while removing it
from $d\mu_{\Gamma_{-1}}$; this is exactly \eqref{eq:gamma-cc-eff} and
yields \eqref{eq:a0-sequester}.

\emph{Step 4 (decoupling).}
Proposition~\ref{prop:cc-decouple} then gives
$\beta_{\Lambda_{\mathrm{cc}}}|_{\sigma=-1}=0$ along observer flow
$g_\iota(\tau_\iota)$; Corollary~\ref{cor:beta-Lambda-fp} records the
vanishing $\Lambda_{\mathrm{cc}}$ row in the observable Jacobian at the
fixed point.
\end{proof}

\begin{corollary}[Vanishing $\Lambda_{\mathrm{cc}}$ $\beta$-function on observable flow at FP]
\label{cor:beta-Lambda-fp}
At the extended fixed point $(\xi_\star,0,0,\kappa_\star,0)$ of
\eqref{eq:frg-fp}, under the $\Pi_{\sigma=+1}$ coupling hypothesis of
Proposition~\ref{prop:cc-decouple}---equivalently, under the $a_0$
sequestering route of Theorem~\ref{thm:cc-sequester}---the
observer-local FRG along $g_\iota(\tau_\iota)$ satisfies
\begin{equation}\label{eq:beta-Lambda-obs-fp}
  \beta_{\Lambda_{\mathrm{cc}}}\Big|_{\sigma=-1,\,\mathrm{FP}}
  \;=\;
  0,
\end{equation}
and $\Lambda_{\mathrm{cc}}$ is \emph{not} a UV-relevant direction in the
observable stability matrix: the $J$-row on
$H^1(\hat Q,V_{16})^{\sigma=-1}$ has no $\Lambda_{\mathrm{cc}}$ entry. The
global $\beta_{\Lambda_{\mathrm{cc}}}=-4\Lambda_{\mathrm{cc}}$ of
Theorem~\ref{thm:cc-rg} flows entirely in $d\mu_{\Gamma_{+1}}$.
\end{corollary}

\begin{proof}
Immediate from Proposition~\ref{prop:cc-decouple} at
$\Lambda_{\mathrm{cc},\star}=0$ and from the diagonal Jacobian
\eqref{eq:jacobian-diag} once the $\Lambda_{\mathrm{cc}}$ coupling is
$\sigma=+1$-projected along the observer flow
(Appendix~\ref{sec:appendix:frg}).
\end{proof}

Collect dimensionless couplings
$(\xi,\hat g^2,\hat y^2,\kappa,\Lambda_{\mathrm{cc}})$ with
$\xi=k^2/f^2$, $\hat g^2=k^2 g^2/f^2$, $\hat y^2=k^2 y^2/f^2$,
$\kappa$ as in \eqref{eq:kappa-def}, and $\Lambda_{\mathrm{cc}}$ as in
Definition~\ref{def:cc}. In the extended one-loop coset--gauge--gravity
truncation (still neglecting $R^2$, graviton loops, and higher curvature),
\begin{equation}\label{eq:frg-system}
\begin{aligned}
  \beta_{\xi}&=2\xi,
  &\quad
  \beta_{\hat g^2}&=2\hat g^2+\frac{b_0}{48\pi^2}\hat g^4,
  &\quad
  \beta_{\hat y^2}&=2\hat y^2+\mathcal{O}(\hat y^4,\hat g^2\hat y^2),
  \\[4pt]
  \beta_{\kappa}&=2\kappa-\frac{5}{48\pi^2}\kappa^2,
  &\quad
  \beta_{\Lambda_{\mathrm{cc}}}&=-4\,\Lambda_{\mathrm{cc}}+\mathcal{O}(\text{loops}).
\end{aligned}
\end{equation}

\begin{proposition}[Jacobian in extended one-loop truncation]
\label{prop:frg-jacobian}
At the fixed point
$(\xi_\star,\hat g^2_\star,\hat y^2_\star,\kappa_\star,\Lambda_{\mathrm{cc},\star})
=(\xi_\star,0,0,96\pi^2/5,0)$, the stability matrix
$J=\partial\beta_i/\partial g_j$ has diagonal spectrum
$\mathrm{eig}(J)=\{+2,+2,+2,-2,-4\}$. With
$\theta_i=-\mathrm{eig}(\partial\beta_i/\partial g_i)$, exactly two directions
are UV-relevant: $\kappa$ ($\theta_\kappa=+2$) and
$\Lambda_{\mathrm{cc}}$ ($\theta_{\Lambda}=+4$). Details in
Appendix~\ref{sec:appendix:frg}.
\end{proposition}

\begin{theorem}[Graviton/$R^2$ persistence of $\kappa_\star$]
\label{thm:kappa-persistence}
Extend the truncation of Theorem~\ref{thm:kappa} by a curvature-squared
coupling $\alpha R^2$ and graviton loops. With
$\sigma$-invariant graviton and $R^2$ modes decoupled from the observer-local
flow on $H^1(\hat Q,V_{16})^{\sigma=-1}$
(Remark~\ref{rmk:observer-frg}), Proposition~\ref{prop:kappa-R2} and
Theorem~\ref{thm:cc-sequester} imply
\begin{equation}\label{eq:kappa-persist}
  \beta_\kappa\Big|_{\kappa_\star,\,\sigma=-1}=0,
  \qquad
  \left.\frac{\partial\beta_\kappa}{\partial\kappa}\right|_{\kappa_\star}=-2,
\end{equation}
so $\kappa_\star=96\pi^2/5$ is a UV-attractive fixed point on the observable
row: subleading vacuum-energy and graviton/$R^2$ back-reaction are routed to
$d\mu_{\Gamma_{+1}}$ (Theorem~\ref{thm:sigma-measure},
Theorem~\ref{thm:cc-sequester}) without modifying
$\beta_\kappa|_{\sigma=-1}$ at the fixed point.
\end{theorem}

\begin{proof}
Graviton and $R^2$ operators are $\sigma$-invariant on $\hat Q$; observer
collapse $\Pi_{\sigma=-1}$ removes their contributions from the anti-invariant
Jacobian row (Remark~\ref{rmk:observer-frg}). Proposition~\ref{prop:kappa-R2}
gives the leading-order flow
$\beta_\kappa=2\kappa-(5/48\pi^2)\kappa^2+\mathcal{O}(\alpha,\text{graviton})$
with unchanged $\kappa_\star$ and stability eigenvalue $-2$. Mixed
$\kappa$--$\alpha$ and graviton-loop corrections enter only through
$\beta_{\Lambda_{\mathrm{cc}}}$ in the sequestered $\sigma=+1$ sector
(Proposition~\ref{prop:cc-decouple}, Theorem~\ref{thm:cc-sequester}), so
$\beta_\kappa|_{\sigma=-1}$ is unchanged at $\kappa_\star$. Evaluating at the
extended fixed point \eqref{eq:frg-fp} yields \eqref{eq:kappa-persist}.
\end{proof}

%----------------------------------------------------------------------%
\subsection{GUT breaking from observer collapse}
\label{sec:physics:breaking}
%----------------------------------------------------------------------%

The heterotic product mirror supplies exact
$\mathbf{16}/\overline{\mathbf{16}}$ duality at $\Mirror^7(\Void)$; observer
collapse $\Pi_{\sigma=-1}$ (Definition~\ref{def:heterotic-collapse}) breaks
this pairing and selects chiral descent directions. Symmetry breaking below is
gradient flow of $V$ on $\iota$-restricted coset directions, functorially
descended from the global EIII minimum above
(Definition~\ref{def:above-below}).

\begin{lemma}[Hessian sector decomposition]\label{lem:breaking-hess}
Let $\orderparam_\star\in\mathcal{M}$ be the rank-one EIII vacuum
(Theorem~\ref{thm:vacuum}) and write fluctuations
$\delta\orderparam=\delta\orderparam_{\mathbf{1}}+\delta\orderparam_{\mathbf{10}}+\delta\orderparam_{\mathbf{16}}$
under the capacity partition
$\mathbf{27}=\mathbf{1}\oplus\mathbf{10}\oplus\mathbf{16}$
(Theorem~\ref{thm:partition}). On the coset
$\mathfrak{m}=\mathbf{16}_{-3}\oplus\overline{\mathbf{16}}_{+3}$, the Hessian
$\Hess V(\orderparam_\star)$ decomposes $H$-equivariantly into $\mathbf{1}$,
$\mathbf{10}$, and $\mathbf{16}\oplus\overline{\mathbf{16}}$ blocks. Restricting
to the observer diagonal $\mathfrak{d}=\mathrm{span}\{e_1,e_2,e_3\}$
(Definition~\ref{def:observer-index}), one obtains a further $\iota$-sector
split
\begin{equation}\label{eq:breaking-hess-iota}
  \Hess V(\orderparam_\star)\big|_{\mathfrak{d}}
  \;=\;
  \bigoplus_{\iota=1}^3 \Hess_\iota V(\orderparam_\star),
\end{equation}
with $\Hess_\iota$ acting on the $\iota$-cell of
$H^1(\hat Q,V_{16})^{\sigma=-1,\,\iota}$. At tree level
$\Hess V(\orderparam_\star)=0$ on $\mathfrak{m}$: the $32$ coset directions are
exact Goldstones; unstable modes enter only after Coleman--Weinberg radiative
correction~\cite{ColemanWeinberg1973}.
\end{lemma}

\begin{proposition}[Chiral breaking directions]\label{prop:breaking-chiral}
The observer projector $\Pi_{\sigma=-1}$ selects breaking along
$\sigma$-anti-invariant coset directions in
$H^1(\hat Q,V_{16})^{\sigma=-1}$ and suppresses the mirror-symmetric
$\overline{\mathbf{16}}$ partner. A vacuum-expectation trajectory $g_\iota(\tau)$
solving \eqref{eq:lifetime-admitted} therefore breaks
$H=\Spin(10)\times U(1)$ along chiral $\mathbf{16}$-type fluctuations tied to
slot $\iota$, not along a simultaneous
$\mathbf{16}\oplus\overline{\mathbf{16}}$ pairing. Duality is exact at the
heterotic rung (Theorem~\ref{thm:duality}); physical breaking is the localized
violation induced by collapse.
\end{proposition}

\begin{proof}
$\Pi_{\sigma=-1}=\tfrac12(\mathrm{id}-\sigma)$ annihilates $\sigma$-invariant
modes. On $\mathfrak{m}$ the mirror involution exchanges
$\mathbf{16}_{-3}$ and $\overline{\mathbf{16}}_{+3}$
(Proposition~\ref{prop:mirror:involution}); anti-invariant fluctuations lie in
$\mathbf{16}_{-3}$ modulo the $\iota$-diagonal restriction. The lifetime flow
\eqref{eq:lifetime-admitted} restricts $\nabla V$ to the $\iota$-sector,
breaking product mirror symmetry while preserving capacity balance on the global
datum $\mathfrak{U}^\star$.
\end{proof}

\begin{lemma}[Coleman--Weinberg instability from coercive $V$]
\label{lem:breaking-cw}
Let $V$ be the coercive EIII potential of Theorem~\ref{thm:vacuum}
and Definition~\ref{def:potential}, and let $V_{\mathrm{eff}}$ denote its Coleman--Weinberg
one-loop lift about $\orderparam_\star\in\mathcal{M}$ as in
Theorem~\ref{thm:rp}. Then on the $28$ radiatively massive coset directions of
Lemma~\ref{lem:breaking-hess}, each $\Hess_\iota V_{\mathrm{eff}}(\orderparam_\star)$
has exactly one negative eigenvalue in the
$\Pi_{\sigma=-1}$-projected $\iota$-cell, with all other massive directions
positive. The unstable mode lies in the $\mathbf{27}$ block of
Lemma~\ref{lem:breaking-hess-spin10} and is labelled by
\eqref{eq:breaking-higgs-map}.
\end{lemma}

\begin{proof}
Coercivity of $V$ on compact $\E{6}$ (Theorem~\ref{thm:vacuum}) fixes a unique
global minimum on $\mathcal{M}=\E{6}/H$ with $32$ tree-level Goldstones on
$\mathfrak{m}$ (Lemma~\ref{lem:breaking-hess}). Coleman--Weinberg resummation
about $\orderparam_\star$ gaps the $28$ coset scalars with $\mu^2>0$
(Theorem~\ref{thm:rp}), leaving one tachyonic direction per $\iota$-cell because
capacity balance on $\mathfrak{d}$ breaks the residual $H$-degeneracy through
the weights $w_\iota\in\{1/27,10/27,16/27\}$ of Theorem~\ref{thm:partition}.
$H$-equivariance and Proposition~\ref{prop:breaking-chiral} restrict the
negative mode to $\sigma$-anti-invariant data; the tensor-product labels follow
from Lemma~\ref{lem:breaking-hess-spin10}.
\end{proof}

\begin{lemma}[Capacity-ordered instability thresholds]
\label{lem:breaking-capacity-order}
Let $w_1=1/27$, $w_2=10/27$, $w_3=16/27$ be the sector masses of
Theorem~\ref{thm:partition}, descended to observer slot $\iota$ by
Proposition~\ref{prop:above-below}. Along an admitted lifetime chart
$g_\iota(\tau_\iota)$ of Definition~\ref{def:lifetime}, the Coleman--Weinberg
instability threshold for the $\iota$-cell unstable mode scales as
\begin{equation}\label{eq:breaking-threshold}
  \tau_\iota^\star \;\propto\; \frac{1}{w_\iota}.
\end{equation}
Hence the $\iota=3$ mode ($w_3=16/27$) triggers before the $\iota=2$ and
$\iota=1$ staged breaks; the electroweak $\iota=1$ mode ($w_1=1/27$) is last.
\end{lemma}

\begin{proof}
On $\mathcal{G}_{\mathrm{Albert}}$, $\mathrm{Bal}_{\mathcal{C}}$ fixes the
relative sector masses $(w_1,w_2,w_3)$ globally (Theorem~\ref{thm:partition});
Proposition~\ref{prop:above-below} identifies these with the $\iota$-diagonal
cells of $\mathfrak{d}$. The $\iota$-restricted gradient flow
\eqref{eq:lifetime-admitted} couples $\nabla V|_\iota$ to the cell weight
$\omega^\star_\iota\propto w_\iota$ (Definition~\ref{def:lifetime-index}), so
the quadratic coefficient of $V_{\mathrm{eff}}$ along the unstable direction
of Lemma~\ref{lem:breaking-cw} is proportional to $w_\iota$. A mode becomes
tachyonic when $\tau_\iota$ exceeds $\tau_\iota^\star\propto 1/w_\iota$; larger
$w_\iota$ implies an earlier threshold.
\end{proof}

\begin{theorem}[First breaking]\label{thm:breaking-e6so10}
Let $V$ be coercive on EIII (Theorem~\ref{thm:vacuum}) with Coleman--Weinberg
lift $V_{\mathrm{eff}}$ (Lemma~\ref{lem:breaking-cw}). With observer collapse on
$\hat Q$ and a fixed observer index $\iota\in\mathcal{I}$, gradient flow of
$V_{\mathrm{eff}}$ on the $\iota$-restricted coset triggers the first step
\begin{equation}\label{eq:breaking-e6so10}
  \E{6}\;\longrightarrow\; \Spin(10)\times U(1)
\end{equation}
along the rank-one orbit of $\mathcal{M}$, with $U(1)$ charge aligned to the
$\iota$-diagonal of $\mathfrak{d}$. The residual stabilizer
$\mathfrak{h}=\mathfrak{so}_{10}\oplus\mathfrak{u}_1$ is the symmetry group of
Theorem~\ref{thm:universe}(iii).
\end{theorem}

\begin{proof}
Rank-one EIII fixes $\mathcal{M}=\E{6}/(\Spin(10)\times U(1))$ globally
(Theorem~\ref{thm:vacuum}). An $\iota$-localized unstable fluctuation in
$\mathbf{16}_{-3}$ is an adjoint-direction Goldstone of $\E{6}/H$; flow along
that mode restores a $\Spin(10)$-invariant submanifold while breaking the
remaining $U(1)_\iota\subset U(1)$ tied to the chosen diagonal. The branching
matches the standard
$\mathbf{78}=\mathbf{45}\oplus\mathbf{1}\oplus\mathbf{16}\oplus\overline{\mathbf{16}}$
pattern at the $\Spin(10)$-invariant vacuum~\cite{Witten1985,GeorgiGlashow1974}.
\end{proof}

\begin{lemma}[Unstable Hessian directions under $\Spin(10)$ branching]
\label{lem:breaking-hess-spin10}
Let $V_{\mathrm{eff}}$ denote the Coleman--Weinberg effective potential about
$\orderparam_\star$ (Theorem~\ref{thm:rp}). Write Jordan fluctuations
$\delta\orderparam\in\mathbf{27}=\mathbf{1}\oplus\mathbf{10}\oplus\mathbf{16}$
(Theorem~\ref{thm:partition}) and restrict to the observer diagonal
$\mathfrak{d}$ as in \eqref{eq:breaking-hess-iota}. After radiative lifting,
each $\Hess_\iota V_{\mathrm{eff}}(\orderparam_\star)$ is
$H$-equivariant on its $\iota$-cell. Under the standard $\Spin(10)$ branching
\begin{equation}\label{eq:breaking-adjoint-branch}
  \mathbf{78}
  \;=\;
  \mathbf{45}\oplus\mathbf{1}\oplus\mathbf{16}\oplus\overline{\mathbf{16}},
  \qquad
  \mathbf{27}=\mathbf{1}\oplus\mathbf{10}\oplus\mathbf{16},
\end{equation}
and the observer projector $\Pi_{\sigma=-1}$, unstable directions classify as
follows:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item $\iota=3$ ($\mathbf{16}$-sector, capacity weight $16/27$): unstable
    modes lie in $\mathbf{16}_{-3}$ and embed in the adjoint
    $\mathbf{16}\subset\mathbf{78}$; they couple to the $\mathbf{45}$ adjoint
    orbit of $\Spin(10)$.
  \item $\iota=2$ ($\mathbf{10}$-sector, weight $10/27$): unstable modes lie in
    $\mathbf{10}_{-2}\subset\mathbf{27}$ and embed in the antisymmetric
    $\mathbf{126}$ via $\mathbf{16}\times\mathbf{16}\supset\mathbf{126}$
    (with $\overline{\mathbf{16}}$ suppressed by $\Pi_{\sigma=-1}$).
  \item $\iota=1$ ($\mathbf{1}$-sector, weight $1/27$): unstable trace modes
    couple to the $\mathbf{10}$ fundamental through the Yukawa portal
    $\mathbf{16}\times\mathbf{16}\times\mathbf{10}$ and the residual
    $\mathbf{10}\subset\mathbf{27}$ block.
\end{enumerate}
Mirror partners $\overline{\mathbf{16}}_{+3}$ do not appear in the unstable
spectrum of the observable sector.
\end{lemma}

\begin{proof}
$V_{\mathrm{eff}}$ is $H$-invariant, so each $\Hess_\iota V_{\mathrm{eff}}$ is
an $H$-intertwiner on the $\iota$-cell. The capacity partition aligns
$\iota=1,2,3$ with the $\mathbf{1}$, $\mathbf{10}$, $\mathbf{16}$ blocks of
$\mathbf{27}$ (Proposition~\ref{prop:above-below}). Items (i)--(iii) follow
from \eqref{eq:breaking-adjoint-branch}, the standard $\Spin(10)$ tensor
products $\mathbf{16}\times\mathbf{16}=\mathbf{1}\oplus\mathbf{45}\oplus
\mathbf{126}$ and $\mathbf{16}\times\mathbf{10}=\mathbf{16}\oplus\mathbf{144}$,
and Proposition~\ref{prop:breaking-chiral}.
\end{proof}

\begin{proposition}[Higgs labels from $\mathbf{27}$-sector Hessians]
\label{prop:breaking-higgs-labels}
Under Lemma~\ref{lem:breaking-hess-spin10}, radiatively unstable
$\Hess_\iota V_{\mathrm{eff}}$ directions map to observable Higgs multiplets
of the $\Spin(10)$ chain:
\begin{equation}\label{eq:breaking-higgs-map}
  \Hess_3 V_{\mathrm{eff}}\;\longmapsto\;\Phi_{\mathbf{45}}\in\mathbf{45}_H,
  \qquad
  \Hess_2 V_{\mathrm{eff}}\;\longmapsto\;\Phi_{\mathbf{126}}\in\mathbf{126}_H,
  \qquad
  \Hess_1 V_{\mathrm{eff}}\;\longmapsto\;\Phi_{\mathbf{10}}\in\mathbf{10}_H.
\end{equation}
Each label is the $\Pi_{\sigma=-1}$-projected unstable mode of the
corresponding $\mathbf{27}$ block, with capacity weight
$w_\iota\in\{1/27,10/27,16/27\}$ fixing the relative scale of the induced
VEV along $g_\iota$.
\end{proposition}

\begin{proof}
The $\mathbf{45}_H$ identification uses the adjoint embedding
$\mathbf{16}\subset\mathbf{78}$: an $\iota=3$ fluctuation is a
$\Spin(10)$-breaking direction in $\mathfrak{so}_{10}$. The $\mathbf{126}_H$
identification uses $\mathbf{16}\times\mathbf{16}\supset\mathbf{126}$ on the
$\iota=2$ cell. The $\mathbf{10}_H$ identification follows from the residual
$\mathbf{10}$ block at $\iota=1$ and the cubic portal
$\mathbf{16}\times\mathbf{16}\times\mathbf{10}$. Capacity weights set the
ordering of instability thresholds along the lifetime chart.
\end{proof}

\begin{theorem}[Second breaking]\label{thm:breaking-so10su5}
Assume Theorem~\ref{thm:breaking-e6so10} and a $\Spin(10)\times U(1)$
intermediate vacuum. With $V_{\mathrm{eff}}$ as in Lemma~\ref{lem:breaking-cw},
the unstable $\Hess_3 V_{\mathrm{eff}}$ mode on the $\iota=3$ cell---the
$\mathbf{16}$-sector with largest capacity weight $w_3=16/27$
(Lemma~\ref{lem:breaking-capacity-order})---triggers gradient flow of
$V_{\mathrm{eff}}$ along $g_3$ at the earliest staged threshold, producing
\begin{equation}\label{eq:breaking-so10su5}
  \Spin(10)\times U(1)\;\longrightarrow\;\mathrm{SU}(5)\times U(1)_X,
\end{equation}
with Higgs fluctuation $\Phi_{\mathbf{45}}\in\mathbf{45}_H$ of
Proposition~\ref{prop:breaking-higgs-labels}. The residual gauge algebra is
$\mathfrak{su}_5\oplus\mathfrak{u}_1$.
\end{theorem}

\begin{proof}
The $\iota=3$ unstable mode lies in $\mathbf{16}_{-3}$ and embeds in
$\mathbf{45}\subset\mathbf{78}$ (Lemma~\ref{lem:breaking-hess-spin10}(i)).
Flow along $\Phi_{\mathbf{45}}$ aligns the vacuum with a $\mathrm{SU}(5)$
subalgebra of $\mathfrak{so}_{10}$; the standard branching
$\mathbf{45}\to\mathbf{24}\oplus\mathbf{1}\oplus\cdots$ under
$\mathrm{SU}(5)\times U(1)_X$ matches Georgi--Glashow
$\Spin(10)\to\mathrm{SU}(5)\times U(1)_X$~\cite{GeorgiGlashow1974}. The
$16/27$ weight dominates the $\iota=2$ and $\iota=1$ thresholds, so this is
the second step after \eqref{eq:breaking-e6so10}.
\end{proof}

\begin{lemma}[$\mathbf{126}_H$ decomposition under $\Pi_{\sigma=-1}$]
\label{lem:breaking-126-sigma}
Let $\Phi_{\mathbf{126}}\in\mathbf{126}_H$ be the antisymmetric Higgs direction
of Proposition~\ref{prop:breaking-higgs-labels}, realized as the unstable
$\Hess_2 V_{\mathrm{eff}}$ mode on the $\iota=2$ cell. The $\Spin(10)$ tensor
product $\mathbf{16}\times\mathbf{16}=\mathbf{1}\oplus\mathbf{45}\oplus
\mathbf{126}$ supplies $\mathbf{126}_H$ as the antisymmetric wedge of chiral
spinors. Under the standard $\mathrm{SU}(5)\times U(1)_X$ branching,
\begin{equation}\label{eq:breaking-126-branch}
  \mathbf{126}
  \;\longrightarrow\;
  \mathbf{10}_{-4}\oplus\overline{\mathbf{10}}_{4}
  \oplus\mathbf{15}_{-6}\oplus\overline{\mathbf{15}}_{6}
  \oplus\mathbf{1}_{10},
\end{equation}
with $\mathbf{1}_{10}$ the $B\!-\!L=2$ singlet that lowers rank. The observer
projector $\Pi_{\sigma=-1}$ acts on \eqref{eq:breaking-126-branch} as follows:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item Bilinear fluctuations $\omega_i\wedge\omega_j$ with
    $|\omega_i\rangle,|\omega_j\rangle\in H^1(\hat Q,V_{16})^{\sigma=-1}$
    are $\sigma$-invariant, so the $\mathbf{126}$ portal is built entirely from
    anti-invariant observer modes; mirror partners in
    $H^1(\hat Q,V_{16})^{\sigma=+1}$ do not enter.
  \item Conjugate multiplets paired by $\sigma$ on $\mathfrak{m}$ are suppressed:
    $\Pi_{\sigma=-1}$ annihilates the $\overline{\mathbf{10}}_{4}$ and
    $\overline{\mathbf{15}}_{6}$ mirror channels, retaining the chiral
    $\mathbf{10}_{-4}\oplus\mathbf{15}_{-6}\oplus\mathbf{1}_{10}$ sector.
  \item The $\mathrm{SU}(5)\to$SM breaking direction is the
    $\Pi_{\sigma=-1}$-projected component of $\mathbf{1}_{10}$ together with
    the $(1,1)$ singlet inside $\mathbf{15}_{-6}$; the residual
    $\mathrm{SU}(3)_c\times\mathrm{SU}(2)_L\times U(1)_Y$ algebra is the
    stabilizer after its VEV.
\end{enumerate}
Capacity weight $w_2=10/27$ fixes the scale ordering of this mode relative to
the $\iota=3$ and $\iota=1$ thresholds.
\end{lemma}

\begin{proof}
Item~(i) uses $\sigma(\omega_i\wedge\omega_j)=\sigma(\omega_i)\sigma(\omega_j)
\omega_i\wedge\omega_j$ with $\sigma(\omega_i)=-1$ on physical fermions.
Item~(ii) follows from Proposition~\ref{prop:breaking-chiral} and the mirror
exchange on $\overline{\mathbf{16}}_{+3}$. Item~(iii) is the standard
$\mathrm{SU}(5)$ rank-breaking pattern: $\langle\mathbf{1}_{10}\rangle$ removes
$U(1)_X$ and the $(1,1)\subset\mathbf{15}$ direction completes
$\mathrm{SU}(5)\to\mathrm{SU}(3)_c\times\mathrm{SU}(2)_L\times U(1)_Y$
\cite{GeorgiGlashow1974,Witten1985}. The $10/27$ weight is the $\mathbf{10}$
block capacity datum of Theorem~\ref{thm:partition}.
\end{proof}

\begin{theorem}[Third breaking]\label{thm:breaking-su5sm}
Assume Theorem~\ref{thm:breaking-so10su5} and a
$\mathrm{SU}(5)\times U(1)_X$ intermediate vacuum. With $V_{\mathrm{eff}}$ as
in Lemma~\ref{lem:breaking-cw}, the unstable $\Hess_2 V_{\mathrm{eff}}$ mode on
the $\iota=2$ cell---capacity weight $w_2=10/27$
(Lemma~\ref{lem:breaking-capacity-order})---triggers gradient flow of
$V_{\mathrm{eff}}$ along $g_2$ after the $\iota=3$ stage, producing
\begin{equation}\label{eq:breaking-su5sm}
  \mathrm{SU}(5)\times U(1)_X
  \;\longrightarrow\;
  \mathrm{SU}(3)_c\times\mathrm{SU}(2)_L\times U(1)_Y,
\end{equation}
with Higgs fluctuation $\Phi_{\mathbf{126}}\in\mathbf{126}_H$ of
Proposition~\ref{prop:breaking-higgs-labels} and observable content given by
Lemma~\ref{lem:breaking-126-sigma}. The residual gauge algebra is
$\mathfrak{su}_3\oplus\mathfrak{su}_2\oplus\mathfrak{u}_1$.
\end{theorem}

\begin{proof}
The $\iota=2$ unstable mode lies in $\mathbf{10}_{-2}\subset\mathbf{27}$ and
embeds in $\mathbf{126}$ via $\mathbf{16}\times\mathbf{16}$
(Lemma~\ref{lem:breaking-hess-spin10}(ii)). Flow along
$\Pi_{\sigma=-1}\Phi_{\mathbf{126}}$ aligns the vacuum with the
$\mathbf{1}_{10}\oplus(1,1)\subset\mathbf{15}$ direction of
\eqref{eq:breaking-126-branch}; the standard branching
$\mathbf{15}\to(3,1)_{-1/3}\oplus(1,3)_{1/3}\oplus(1,1)_{-4/3}$ and
$\mathbf{10}\to(3,1)_{1/3}\oplus(1,2)_{-1/2}\oplus(1,1)_{2/3}$ under
$\mathrm{SU}(3)_c\times\mathrm{SU}(2)_L\times U(1)_Y$ matches Georgi--Glashow
$\mathrm{SU}(5)\to$SM~\cite{GeorgiGlashow1974}. The $10/27$ weight places this
step after \eqref{eq:breaking-so10su5} and before the $\iota=1$
electroweak stage.
\end{proof}

\begin{proposition}[Weinberg angle at $M_{\mathrm{GUT}}$]
\label{prop:weinberg-gut}
Assume Theorems~\ref{thm:breaking-e6so10} and~\ref{thm:breaking-so10su5}, with
$\Spin(10)$ gauge coupling normalization surviving to the GUT scale
(Theorem~\ref{thm:beta}, $b_0=12$). At $M_{\mathrm{GUT}}$,
\begin{equation}\label{eq:weinberg-gut}
  \sin^2\theta_W(M_{\mathrm{GUT}})=\tfrac38,
\end{equation}
where $\theta_W$ is the electroweak mixing angle in the canonical
$\mathrm{SU}(5)\subset\Spin(10)$ embedding. This is the group-theoretic anchor
for Prediction~\ref{pred:gut}.
\end{proposition}

\begin{proof}
In the $\Spin(10)$ adjoint, embed
$\mathrm{SU}(5)\times U(1)_X\subset\Spin(10)$ with generators normalized by
$\mathrm{Tr}(T_aT_b)=\delta_{ab}$ on the spinor $\mathbf{16}$. Hypercharge
$Y$ is the standard $\mathrm{SU}(5)$ combination; electric charge
$Q=T_3+Y$. Then
$\sin^2\theta_W=\mathrm{Tr}(T_3^2)/\mathrm{Tr}(Q^2)=3/8$ at unification,
independent of the intermediate $\mathbf{126}_H$ VEV scale
\cite{GeorgiGlashow1974,Witten1985}.
\end{proof}

\begin{theorem}[Electroweak breaking]\label{thm:breaking-ew}
Assume Theorems~\ref{thm:breaking-so10su5} and~\ref{thm:breaking-su5sm}.
With $V_{\mathrm{eff}}$ as in Lemma~\ref{lem:breaking-cw}, the unstable
$\Hess_1 V_{\mathrm{eff}}$ mode on the $\iota=1$ cell---capacity weight
$w_1=1/27$ (Lemma~\ref{lem:breaking-capacity-order})---triggers gradient flow
along $g_1$ with $\Phi_{\mathbf{10}}\in\mathbf{10}_H$, producing
\begin{equation}\label{eq:breaking-ew}
  \mathrm{SU}(2)_L\times U(1)_Y
  \;\longrightarrow\;
  U(1)_{\mathrm{em}},
\end{equation}
with $\mathrm{SU}(3)_c$ unbroken. The electroweak scale is set by the
$1/27$ capacity weight on the final $\iota=1$ breaking stage.
\end{theorem}

\begin{proof}
$\mathbf{10}_H$ contains the $\mathrm{SU}(5)$ Higgs doublet
$\mathbf{5}\oplus\overline{\mathbf{5}}$; an $\iota=1$ fluctuation in
$\Phi_{\mathbf{10}}$ breaks the electroweak subgroup while leaving
$\mathrm{SU}(3)_c$ intact. The ordering $\iota=3\to2\to1$ follows capacity
weights $(16/27,10/27,1/27)$; the electroweak step is last because the
$\mathbf{1}$-sector carries the smallest weight.
\end{proof}

\begin{proposition}[Sequential $\iota$-ordered gradient flow]
\label{prop:breaking-sequential}
Let $V_{\mathrm{eff}}$ be the Coleman--Weinberg lift of coercive $V$
(Lemma~\ref{lem:breaking-cw}) and let $(g_1,g_2,g_3)$ be admitted lifetime
charts on $\mathcal{S}_\iota$ (Definition~\ref{def:lifetime}) with common
initial datum $\orderparam_\star|_\iota$. Along the composite observer trajectory
that concatenates $g_3$, then $g_2$, then $g_1$ after each intermediate vacuum is
reached, $\iota$-restricted gradient flow of $V_{\mathrm{eff}}$ visits the
breaking stages in capacity order $3\to2\to1$ because instability thresholds
satisfy \eqref{eq:breaking-threshold} (Lemma~\ref{lem:breaking-capacity-order})
and $\nabla V_{\mathrm{eff}}|_\iota$ is dominated by the unresolved cell of
largest $w_\iota$. Uniqueness up to reparametrization of $\tau_\iota$ on each
sector follows from Proposition~\ref{prop:lifetime-flow-unique}.
\end{proposition}

\begin{proof}
At $\orderparam_\star$, Lemma~\ref{lem:breaking-cw} supplies one tachyonic
direction per $\iota$-cell with threshold $\tau_\iota^\star\propto 1/w_\iota$.
Since $w_3>w_2>w_1$, the $\iota=3$ mode becomes unstable first among the staged
$\Spin(10)$, $\mathrm{SU}(5)$, and electroweak steps; flow along $g_3$ reaches
the $\mathrm{SU}(5)\times U(1)_X$ vacuum of Theorem~\ref{thm:breaking-so10su5}.
Re-expanding $V_{\mathrm{eff}}$ about that vacuum, the $\iota=2$ mode is next
(Theorem~\ref{thm:breaking-su5sm}), then the $\iota=1$ mode
(Theorem~\ref{thm:breaking-ew}). The first $\E{6}\to\Spin(10)\times U(1)$ step
is triggered by any $\iota$-cell unstable $\mathbf{16}$ mode
(Theorem~\ref{thm:breaking-e6so10}) and precedes the capacity-ordered cascade.
\end{proof}

\begin{theorem}[Complete GUT--Higgs chain]\label{thm:breaking-complete}
Let $V$ be the coercive EIII potential (Theorem~\ref{thm:vacuum}) with
Coleman--Weinberg lift $V_{\mathrm{eff}}$ (Lemma~\ref{lem:breaking-cw}).
Sequential $\iota$-restricted gradient flow of $V_{\mathrm{eff}}$ on the $28$
radiatively massive coset directions (Theorem~\ref{thm:rp}), with capacity
ordering $w_3>w_2>w_1$ from Theorem~\ref{thm:partition}, realizes the staged
chain
\begin{equation}\label{eq:breaking-chain}
  \E{6}\to\Spin(10)\times U(1)\to SU(5)\to SU(3)_c\times SU(2)_L\times U(1)_Y
  \to SU(3)_c\times U(1)_{\mathrm{em}}
\end{equation}
as follows:
\begin{enumerate}[label=\textbf{(\arabic*)},leftmargin=*]
  \item \textbf{$\E{6}\to\Spin(10)\times U(1)$} --- any $\iota$-cell unstable
    $\mathbf{16}$ mode (Theorem~\ref{thm:breaking-e6so10}).
  \item \textbf{$\Spin(10)\to\mathrm{SU}(5)\times U(1)_X$} --- $\iota=3$
    $\mathbf{45}_H$ direction, largest weight $w_3=16/27$
    (Theorem~\ref{thm:breaking-so10su5},
    Lemma~\ref{lem:breaking-capacity-order}).
  \item \textbf{$\mathrm{SU}(5)\to\mathrm{SU}(3)_c\times\mathrm{SU}(2)_L
    \times U(1)_Y$} --- $\iota=2$ $\mathbf{126}_H$ direction, weight
    $w_2=10/27$ (Theorem~\ref{thm:breaking-su5sm},
    Lemma~\ref{lem:breaking-126-sigma}).
  \item \textbf{Electroweak} --- $\iota=1$ $\mathbf{10}_H$ direction, weight
    $w_1=1/27$ (Theorem~\ref{thm:breaking-ew},
    Lemma~\ref{lem:breaking-capacity-order}).
\end{enumerate}
Observable Higgs content $\mathbf{45}_H$, $\mathbf{126}_H$, $\mathbf{10}_H$ is
the $\Pi_{\sigma=-1}$-projected unstable spectrum of
\eqref{eq:breaking-higgs-map} (Proposition~\ref{prop:breaking-higgs-labels}).
Yukawa matrices $y_{ij}$ arise from cubic overlap integrals
\begin{equation}\label{eq:breaking-yukawa}
  y_{ij}\;\propto\;\int_{\hat Q}\omega_\iota\wedge\omega_j\wedge\Phi_{\mathrm{Higgs}},
\end{equation}
of observer modes $|\omega_\iota\rangle$ on $\hat Q$
(Definition~\ref{def:observer}) against $\Phi_{\mathrm{Higgs}}\in\{\Phi_{\mathbf{45}},
\Phi_{\mathbf{126}},\Phi_{\mathbf{10}}\}$. Section~\ref{sec:yukawa} develops
the leading-order evaluation of \eqref{eq:breaking-yukawa}.
Proposition~\ref{prop:weinberg-gut} fixes $\sin^2\theta_W=3/8$ at
$M_{\mathrm{GUT}}$ once $\Spin(10)$ survives. The sequential realization of all
four steps is supplied by Proposition~\ref{prop:breaking-sequential}.
\end{theorem}

\begin{proof}
\emph{Step 1 (instability).} Coercivity of $V$ (Theorem~\ref{thm:vacuum})
and Theorem~\ref{thm:rp} yield $V_{\mathrm{eff}}$ with one unstable mode per
$\iota$-cell (Lemma~\ref{lem:breaking-cw}), labelled by
\eqref{eq:breaking-higgs-map} (Lemma~\ref{lem:breaking-hess-spin10},
Proposition~\ref{prop:breaking-higgs-labels}).

\emph{Step 2 (individual breaks).} Theorem~\ref{thm:breaking-e6so10} gives
the $\E{6}\to\Spin(10)\times U(1)$ step from any $\iota$-localized $\mathbf{16}$
fluctuation. Theorems~\ref{thm:breaking-so10su5},~\ref{thm:breaking-su5sm},
and~\ref{thm:breaking-ew} give the $\Spin(10)\to\mathrm{SU}(5)$,
$\mathrm{SU}(5)\to$SM, and electroweak stages from the $\iota=3,2,1$ unstable
modes respectively.

\emph{Step 3 (ordering).} Lemma~\ref{lem:breaking-capacity-order} orders
instability thresholds as $\tau_3^\star<\tau_2^\star<\tau_1^\star$ because
$w_3>w_2>w_1$. Proposition~\ref{prop:breaking-sequential} shows that admitted
gradient flow visits stages \textbf{(2)--(4)} in that order; stage~\textbf{(1)}
precedes them by Theorem~\ref{thm:breaking-e6so10}.

\emph{Step 4 (Higgs and Yukawa).} Higgs quantum numbers follow from
\eqref{eq:breaking-higgs-map} and Lemma~\ref{lem:breaking-126-sigma}; Yukawa
couplings are defined by \eqref{eq:breaking-yukawa} on $\hat Q$.
\end{proof}

\begin{corollary}[GUT breaking from $V$]\label{cor:breaking}
Gradient flow of $V_{\mathrm{eff}}$ on $\iota$-restricted coset directions
triggers \eqref{eq:breaking-chain} with Higgs content $\mathbf{45}_H$,
$\mathbf{126}_H$, $\mathbf{10}_H$. The observer-derived mechanism is
Theorem~\ref{thm:breaking-complete} (Lemmas~\ref{lem:breaking-hess},
~\ref{lem:breaking-hess-spin10},~\ref{lem:breaking-cw},
~\ref{lem:breaking-capacity-order};
Propositions~\ref{prop:breaking-chiral},~\ref{prop:breaking-higgs-labels},
~\ref{prop:breaking-sequential};
Theorems~\ref{thm:breaking-e6so10},~\ref{thm:breaking-so10su5},
~\ref{thm:breaking-su5sm},~\ref{thm:breaking-ew},
Proposition~\ref{prop:weinberg-gut}).
\end{corollary}

\begin{remark}[As above, so below]\label{rem:breaking-above-below}
Global capacity balance fixes the EIII minimum $\orderparam_\star\in\mathcal{M}$
\emph{above} (Theorem~\ref{thm:vacuum}); observer collapse localizes breaking
\emph{below} to the $\iota$-sector lifetime chart
(Definition~\ref{def:lifetime}). The correspondence \eqref{eq:above-below}
identifies the profinite universe datum $\mathfrak{U}^\star$ with fixed-point
collapse on $\hat Q$: the same potential $V$ governs the global vacuum and the
slot-resolved descent trajectories $g_\iota$. What is proved globally on
$\mathfrak{U}^\star$---the $1|10|16$ split, rank-one EIII, three observer
slots---appears locally as chiral gauge breaking in slot $\iota$, without
importing mirror-symmetric partners.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Flavon hierarchy from observer capacity flow}
\label{sec:physics:flavon}
%----------------------------------------------------------------------%

Assume Corollary~\ref{cor:breaking}. The flavour group
$SU(3)_F\subset\Spin(10)$ acts on the three chiral $\mathbf{16}$s; each
observer index $\iota\in\mathcal{I}$ labels one diagonal direction of
$\mathfrak{d}\subset\jalg$ and hence one $SU(3)_F$ flavour axis.

\begin{proposition}[Flavon sector from observer indices]\label{prop:flavon-sector}
The three observer slots of Theorem~\ref{thm:chirality-derived} index three
$SU(3)_F$ breaking stages. Along the lifetime chart $g_\iota(\tau_\iota)$
(Definition~\ref{def:lifetime}), the capacity flow
$\omega^\star_\iota(\tau)=\capacity_\iota(\tau)$ of
Definition~\ref{def:lifetime-index} records which flavon direction is active at
time $\tau$ within slot $\iota$. Mirror stabilisation fixes $n_F=3$ but not,
by itself, Yukawa eigenvalues or mixing matrices.
\end{proposition}

\begin{theorem}[Flavon hierarchy, P3$'$]\label{thm:flavon-hierarchy}
Assume Theorem~\ref{thm:breaking-complete} and the capacity-weighted flavon
potential $V_F$ of Definition~\ref{def:flavon-potential}. Sequential
$SU(3)_F\to SU(2)_F\to U(1)_F$ breaking is driven by the observer-indexed
capacity RG flow $\omega^\star_\iota(\tau)$ of
Proposition~\ref{prop:flavon-beta}, with $\phi_\iota$ the flavon along
diagonal $e_\iota$. Minimization of $V_F$ along $\mathfrak{d}$
(Theorem~\ref{thm:flavon-vev}) yields
\begin{equation}\label{eq:flavon-hierarchy-vev}
  \langle\phi_3\rangle^2 : \langle\phi_2\rangle^2 : \langle\phi_1\rangle^2
  \;=\;
  w_3 : w_2 : w_1
  \;=\;
  16 : 10 : 1,
\end{equation}
and off-diagonal overlap coefficients $\mathcal{H}_{ij}$ of
Theorem~\ref{thm:Hij-derived} supply CKM/PMNS mixing without an independent
flavon postulate.
\end{theorem}

\begin{proof}
Theorem~\ref{thm:flavon-vev} proves the VEV ordering from $V_F$ minimization
subject to the hub constraint $\phi_1+\phi_2+\phi_3=0$.
Proposition~\ref{prop:flavon-beta} and Theorems~\ref{thm:nu-ratio-rg},
\ref{thm:nu-ratio-2loop} realize the capacity RG flow on $SU(3)_F$.
Theorem~\ref{thm:Hij-derived} transports the flavon bilinear data to Yukawa
off-diagonals via Lemma~\ref{lem:Pij-hub}.
\end{proof}