%======================================================================%
\section{Conclusions}
\label{sec:conclusions}
%======================================================================%

SJET builds the universe from the mirror:
\begin{equation}
  \Void\xrightarrow{\;\Mirror\;}\cdots\xrightarrow{\;\Mirror\;}\mathfrak{U}^\star,
  \qquad
  \mathfrak{U}^\star=\Climb^\infty(\Void).
\end{equation}
Observers arise at the heterotic rung as collapsed fixed-point states:
\begin{equation}
  \iota \;\longmapsto\; |\omega_\iota\rangle \in H^1(\hat Q,V_{16})^{\sigma=-1},
  \qquad
  g_\iota:\mathbb{R}\to\mathcal{S}_\iota.
\end{equation}
Only two axioms are primitive. Duality, observer multiplicity, and the
index--lifetime map are \textbf{derived} from $E_8\times E_8$ collapse and the
Lefschetz fixed-point theorem.

\subsection{Epistemic summary}

\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Status} & \textbf{Content} \\
\midrule
Axioms & void, mirror \\
Theorems & rung table, $E_8$, $E_8\times E_8$, $E_6$, partition, vacuum, \\
 & duality, observer fixed points, chirality derived, index--lifetime map, \\
 & soldering derived, lifetime/soldering uniqueness reductions, \\
 & anomalies, $b_0=12$, \\
 & $\kappa_\star$ (one-loop trunc.), CC RG relevance, semiclassical RP, \\
 & conditional RP for $d\mu_{\Gamma_{-1}}$ (Thm.~\ref{thm:rp-gamma-neg}), \\
 & $a_0$ sequestering sketch at $\kappa_\star$, extended FRG Jacobian \\
Lemmas & $F_4$ fixes $\Quat\subset\Oct$ (Lemma~\ref{lem:quat-F4}), \\
 & Goldstones in $\sigma=+1$ coset sector \\
Definitions & above--below, observer, lifetime chart, $H_2(\Quat)$ block, \\
 & physical sector, $\kappa$, $\Lambda_{\mathrm{cc}}$ \\
Propositions & CC no-go (void+mirror alone), flavon sector from $\iota$, \\
 & mirror descent preserves lifetime chart class, exceptional rungs preserve \\
 & $H_2(\Quat)$ soldering, gradient-flow uniqueness on $\iota$-sector, \\
 & unique timelike $\orderparam^0$, \\
 & $\sigma$-sector measure split, OS reconstruction on observer sector, \\
 & CC $\Lambda_{\mathrm{cc}}$ decoupling, leading-order $\kappa_\star$/$R^2$ stability \\
Corollaries & $\beta_{\Lambda_{\mathrm{cc}}}=0$ on observable flow at FP \\
Conjectures & lifetime/soldering massless-sector closure, \\
 & nonperturbative $\sigma$-measure split (Conj.~\ref{conj:rp}), GUT \\
 & breaking, CC sequestering (Conj.~\ref{conj:cc-sequester}), \\
 & $\kappa_\star$ graviton/$R^2$ persistence (Conj.~\ref{conj:kappa}), \\
 & flavon hierarchy P3$'$ (Conj.~\ref{conj:flavon}) \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Prediction development}

Section~\ref{sec:predictions} maps SJET to 2025--2030 experiments.
Table~\ref{tab:predictions-comparison} and Appendix~\ref{sec:appendix:numerical}
(Table~\ref{tab:numerical-workbook}) record the numerical scorecard:
\textbf{T1 matches} on $n_F=3$ and $b_0=12$; \textbf{match (leading)} on
$\Delta m^2_{31}/\Delta m^2_{21}\approx 33$ (D2 flavon RG); \textbf{pending}
on neutrino ordering, $m_\mu/m_e$, muon $a_\mu$, and $\Lambda_{\mathrm{obs}}$;
\textbf{match (conditional)} on $\sin^2\theta_W(M_Z)$ from GUT anchor $3/8$ and
on $\tau(p\to e^+\pi^0)\gtrsim 10^{34}$\,yr under the $\E{6}$ chain.
\textbf{Immediate falsifiers (T1):} no fourth generation (structurally
excluded). \textbf{Near-term targets (T2):} JUNO normal ordering (2027--2028)
and sub-percent $\Delta m^2$ ratio.
\textbf{Conditional (T3):} $\Lambda_{\mathrm{obs}}\approx 0$,
$\sin^2\theta_W(M_{\mathrm{GUT}})=3/8$, DESI $w(z)\approx -1$.
\textbf{D1} (Yukawa overlaps), \textbf{D2} (flavon RG), and \textbf{D3}
(scale identification, $\mu\equiv v$) are \textbf{partially closed}
(Sections~\ref{sec:yukawa}, \ref{sec:physics:flavon-rg}, \ref{sec:scales};
Table~\ref{tab:derivation-status}).
Table~\ref{tab:falsification-timeline} orders the 2026--2030 experimental
contacts. The enumerated proof targets in Section~\ref{sec:predictions:program}
(D1.\textit{a--c}, D2.\textit{a--c}, D3.\textit{a--c}) are required for
sub-percent agreement with JUNO and Muon $g$-2.

\subsection{Open problems}

\begin{enumerate}[label=\textbf{O\arabic*.},leftmargin=*]
  \item \textbf{Partially addressed (O1):}
    Proposition~\ref{prop:lifetime-flow-unique} proves $\iota$-sector
    uniqueness under convex $V$;
    Proposition~\ref{prop:lifetime-descent} proves mirror descent
    $n=7\to8$ preserves lifetime chart class;
    Theorem~\ref{thm:lifetime-unique-reduced} reduces
    Conjecture~\ref{conj:lifetime-unique} to the tree-level massless
    $\mathfrak{m}_{+1}$ sector (Remark~\ref{rem:lifetime-full-gap}).
  \item \textbf{Partially addressed (O2):}
    Lemma~\ref{lem:quat-F4} and Proposition~\ref{prop:soldering-clock} fix the
    $\iota$-local soldered block and timelike clock;
    Proposition~\ref{prop:soldering-transport} proves exceptional-rung
    transport on $n=6,7,8$;
    Theorem~\ref{thm:soldering-unique-reduced} reduces
    Conjecture~\ref{conj:soldering-unique} to the massless Goldstone sector
    (Theorem~\ref{thm:spacetime:soldering-derived} derives $d=4$
    conditionally; Remark~\ref{rem:soldering-full-gap}).
  \item Prove Conjecture~\ref{conj:breaking} from $V$.
  \item \textbf{Partially addressed (O4):} Theorem~\ref{thm:rp-gamma-neg} and
    Proposition~\ref{prop:os-observer} supply conditional RP and OS
    reconstruction on the observer sector once massless modes lie in
    $d\mu_{\Gamma_{+1}}$ only (Lemma~\ref{lem:goldstone-sigma});
    Conjecture~\ref{conj:rp} is reduced to nonperturbative proof of
    \eqref{eq:gamma-split} with the composite gauge measure.
  \item \textbf{Partially addressed (O5):} Proposition~\ref{prop:kappa-R2},
    Corollary~\ref{cor:beta-Lambda-fp}, and Theorem~\ref{thm:cc-sequester-sketch}
    give leading-order persistence of $\kappa_\star$ with vacuum-energy
    back-reaction routed to $d\mu_{\Gamma_{+1}}$; \emph{still open:}
    nonperturbative curved-background FRG confirmation
    (Conjecture~\ref{conj:kappa}).
  \item \textbf{Partially addressed (O6):} Lemma~\ref{lem:a0-sigma-plus},
    Theorem~\ref{thm:cc-sequester-sketch}, and
    Corollary~\ref{cor:beta-Lambda-fp} show
    $\beta_{\Lambda_{\mathrm{cc}}}|_{\sigma=-1,\,\mathrm{FP}}=0$ under
    $\Pi_{\sigma=+1}$ projection of the $a_0$ heat-kernel density
    \eqref{eq:gamma-cc-eff}; Conjecture~\ref{conj:cc-sequester} is reduced to
    deriving that split from $\Gamma_{\mathrm{eff}}$ at $\kappa_\star$.
  \item \textbf{Partially addressed (P3$'$):} Proposition~\ref{prop:flavon-sector}
    and Conjecture~\ref{conj:flavon} reduce flavon hierarchy to capacity flow
    $\omega^\star_\iota(\tau)$ on $SU(3)_F$; \emph{still open:} prove ordering
    and mixing matrices from $V_F$.
\end{enumerate}

\subsection{Archive}

The prior modular manuscript (39 pages, verification ledger, axiomatic
elimination program) is preserved in \texttt{old/sjet-stack/}.