%======================================================================%
\section{Predictions and Experimental Contact}
\label{sec:predictions}
%======================================================================%

SJET is not complete until its outputs confront measurement. This section
records \textbf{what is already fixed} by void, mirror, and observer collapse,
\textbf{what follows conditionally} from capacity descent and flavon flow, and
\textbf{which near-term experiments} (2025--2030) can falsify or corroborate
each tier. All comparisons use public results as of mid-2026; cited values are
experimental central values unless noted.

%----------------------------------------------------------------------%
\subsection{Prediction protocol}
\label{sec:predictions:protocol}
%----------------------------------------------------------------------%

\begin{definition}[Prediction tiers]\label{def:prediction-tiers}
\begin{enumerate}[label=\textbf{T\arabic*.},leftmargin=*]
  \item \textbf{Exact} --- integer or rational consequence of proved theorems
    (no free parameters).
  \item \textbf{Leading} --- order-of-magnitude from capacity weights
    $(1/27,10/27,16/27)$ and observer index $\iota$.
  \item \textbf{Conditional} --- follows if Conjectures~\ref{conj:breaking-derived},
    \ref{conj:flavon}, \ref{conj:cc-sequester} hold; falsifiable but not yet
    proved from axioms alone.
\end{enumerate}
\end{definition}

\begin{definition}[Contact map]\label{def:contact-map}
A \emph{contact map} assigns each prediction $P$ to an observable $\mathcal{O}$
and experiment $E$ with tolerance $\delta$:
\begin{equation}\label{eq:contact}
  \mathcal{C}(P)=(\mathcal{O},E,\delta),
  \qquad
  \text{falsified if }|\mathcal{O}_{\mathrm{exp}}-\mathcal{O}_{\mathrm{SJET}}|>\delta.
\end{equation}
\end{definition}

%----------------------------------------------------------------------%
\subsection{Tier T1: exact predictions}
\label{sec:predictions:T1}
%----------------------------------------------------------------------%

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Quantity} & \textbf{SJET value} & \textbf{Source} & \textbf{Experiment (2026)} \\
\midrule
Family count $n_F$ & $3$ & Thm.~\ref{thm:chirality-derived} & No 4th gen (LHC) \\
$\beta$-function $b_0$ & $12$ & Thm.~\ref{thm:beta} & SM 1-loop $\beta_\lambda$ \\
Coset scalars $n_S$ & $28$ & Thm.~\ref{thm:planck} & EWSB scalar count \\
Mixed GS coeff.\ (1 fam.) & $-1$ & Thm.~\ref{thm:anomaly} & String/GS sign \\
$\kappa_\star$ & $96\pi^2/5$ & Thm.~\ref{thm:kappa} & FRG benchmark \\
Observer slots $|\mathcal{I}|$ & $3$ & Thm.~\ref{thm:observer-fp} & --- \\
\bottomrule
\end{tabular}
\caption{Exact (T1) predictions. $\kappa_\star\approx189.6$ is dimensionless in
the stated truncation; $\MPl$ and $v$ in GeV are conditional
(Section~\ref{sec:scales}, Table~\ref{tab:scale-map}).}
\label{tab:predictions-T1}
\end{table}

\begin{proposition}[No fourth generation]\label{prop:no-fourth}
The Lefschetz index $\mathrm{ind}_\sigma(\bar\partial_{V_{16}})=-3$ fixes
$|\mathcal{I}|=3$ exactly. A fourth chiral family requires a fourth
$\sigma$-anti-invariant $1$-class on $\hat Q$, contradicting
Theorem~\ref{thm:observer-fp}. SJET predicts \textbf{no} sequential fourth
generation at any energy reachable without changing the heterotic quotient
structure.
\end{proposition}

\begin{remark}[Muon $g-2$ contact, T1]
Fermilab Muon $g$-2 (June 2025 final run) reports
$a_\mu=0.001\,165\,920\,705(205)$~\cite{MuonG2FNAL2025}.
The T1 prediction is \textbf{structural}: new physics from a fourth family or
extra mirror-observable chiral families is excluded; any residual anomaly must
arise from the $\mathbf{27}$ sector with $n_F=3$, $n_S=28$, and $b_0=12$.
\textbf{D1 (partial):} Theorem~\ref{thm:g2-oneloop} and
Proposition~\ref{prop:g2-estimate} (Section~\ref{sec:g2},
Table~\ref{tab:g2-estimate}) give a one-loop estimate
$\Delta a_\mu^{\mathrm{SJET}}\approx1.1\times10^{-8}$, $\sim4\times$ the
SM--experiment anomaly $\delta a_\mu\approx2.6\times10^{-9}$ at full portal
coupling $y_\mu=m_\mu/v$ from Theorem~\ref{thm:yukawa-mass}. This is
\textbf{order-of-magnitude}, not a precision fit; two-loop flavon RG (D2) and
derived $v$ (D3) compress the estimate.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Tier T2: leading-order spectrum}
\label{sec:predictions:T2}
%----------------------------------------------------------------------%

Capacity weights $(m_1,m_{10},m_{16})=(1/27,10/27,16/27)$ descend to observer
indices $\iota=1,2,3$ on $\mathfrak{d}$.

\begin{proposition}[Generation ordering]\label{prop:gen-ordering}
Under the flavon sector map of Proposition~\ref{prop:flavon-sector}, observer
index $\iota$ carries capacity weight $\omega^\star_\iota\propto w_\iota$ with
\begin{equation}\label{eq:capacity-weights}
  w_1:w_2:w_3 = 1:10:16.
\end{equation}
Leading-order Yukawa hierarchies satisfy $y_\iota\propto\sqrt{w_\iota}$ and
$m_\iota\propto w_\iota$ at fixed Higgs VEV.
\end{proposition}

\begin{prediction}[Normal neutrino mass ordering]\label{pred:nu-ordering}
\textbf{T2.} The heaviest neutrino mass eigenstate is $m_3$ (normal ordering):
$w_3>w_2>w_1$ implies $m_3>m_2>m_1$ before RG corrections.
\textbf{Contact:} JUNO mass-ordering determination (2026--2028);
$\mathcal{C}(\text{NO})=(\text{sign}(\Delta m^2_{31}-\Delta m^2_{21}),
\mathrm{JUNO},\text{sign test})$.
\end{prediction}

\begin{prediction}[Mass-squared ratio target]\label{pred:nu-ratio}
\textbf{T2 (leading, refined).} Capacity descent gives the tree-level ratio
$w_3/w_1=16$ (Proposition~\ref{prop:gen-ordering}). One-loop capacity RG on
$V_F$ (Definition~\ref{def:flavon-potential},
Proposition~\ref{prop:flavon-beta}, Theorem~\ref{thm:nu-ratio-rg}) yields
\begin{equation}\label{eq:nu-ratio}
  \frac{\Delta m^2_{31}}{\Delta m^2_{21}}
  \;=\;
  \frac{w_3}{w_1}\,R_{\mathrm{RG}}
  \;=\;
  16\,R_{\mathrm{RG}},
\end{equation}
with
\begin{equation}\label{eq:nu-ratio-RG}
  R_{\mathrm{RG}}
  \;=\;
  1 + \frac{(w_3-w_1)\,b_0}{24\pi^2}\,
  \ln\!\frac{M_{\mathrm{GUT}}}{\mu_{\mathrm{osc}}}.
\end{equation}
Proposition~\ref{prop:R-RG-numeric} evaluates $R_{\mathrm{RG}}^{(1)}\approx 1.91$
at one loop, giving $\Delta m^2_{31}/\Delta m^2_{21}\approx 30.6$; two-loop
thresholds (Theorem~\ref{thm:nu-ratio-2loop},
Proposition~\ref{prop:nu-ratio-pdg}) raise this to
$16\,R_{\mathrm{RG}}^{(1)}R_{\mathrm{RG}}^{(2)}\approx 33.3$, matching
PDG~2025~\cite{PDG2025} central value $\approx 33.8$ with
$\delta R_{\mathrm{RG}}\approx 0.18$. The RG factor $R_{\mathrm{RG}}\sim 2$
is the capacity enhancement that moves the tree-level $16$ into the measured
decade.
\textbf{Falsifier:} inverted ordering; ratio $\ll 3$ or $\gg 10^3$ after
sub-percent JUNO oscillation fits.
\end{prediction}

\begin{prediction}[Sector mass ratios]\label{pred:sector-ratios}
\textbf{T2.} Quark/lepton mass ratios at a common GUT scale obey
$m_3:m_2:m_1\sim 16:10:1$ (capacity weights). In particular
$m_\mu/m_e\sim 10$ at leading order if $\iota=2$ labels the muon sector.
\textbf{Contact:} PDG mass ratios; $\mu$ $g$-2 via Theorem~\ref{thm:g2-oneloop}
and Table~\ref{tab:g2-estimate} ($\Delta a_\mu^{\mathrm{SJET}}/\delta a_\mu\sim4$
at leading order).
\end{prediction}

%----------------------------------------------------------------------%
\subsection{Tier T3: conditional predictions}
\label{sec:predictions:T3}
%----------------------------------------------------------------------%

\begin{prediction}[Observable cosmological constant]\label{pred:cc}
\textbf{T3.} If Conjecture~\ref{conj:cc-sequester} holds at $\kappa_\star$,
\begin{equation}\label{eq:Lambda-obs}
  \Lambda_{\mathrm{obs}}\approx 0
\end{equation}
in the $\sigma=-1$ observer sector, with environmental vacuum energy stored in
$H^\bullet(\hat Q)^{\sigma=+1}$.
\textbf{Contact:} DESI/JWST dark-energy equation of state
$w\to -1$ with no fine-tuned drift; $\mathcal{C}=(w,\mathrm{DESI},|w+1|<0.05)$.
Does \emph{not} by itself resolve the Hubble tension; a non-zero
$\Lambda_{\mathrm{obs}}$ in the sequestered framework would falsify T3.
\end{prediction}

\begin{prediction}[GUT-scale unification]\label{pred:gut}
\textbf{T3.} Under Conjecture~\ref{conj:breaking-derived} with $\Spin(10)$ survival
to $M_{\mathrm{GUT}}$,
\begin{equation}\label{eq:sin2w}
  \sin^2\theta_W(M_{\mathrm{GUT}})=\tfrac38,
  \qquad
  \alpha_{\mathrm{em}}^{-1}(M_{\mathrm{GUT}})\approx 24,
\end{equation}
with $b_0=12$ fixing the $\Spin(10)$ normalization of Thm.~\ref{thm:beta}.
\textbf{Contact:} high-scale coupling unification fits (SUSY or non-SUSY);
deviation of $b_0$ from $12$ shifts unification scale.
\end{prediction}

\begin{prediction}[Weinberg angle at $M_Z$ from GUT anchor]\label{pred:sin2w-mz}
\textbf{T3.} If Prediction~\ref{pred:gut} holds with
$M_{\mathrm{GUT}}\sim 2\times 10^{16}\,\mathrm{GeV}$ and $b_0=12$, one-loop
$\Spin(10)$--$\mathrm{SU}(5)$ running gives
\begin{equation}\label{eq:sin2w-mz}
  \sin^2\theta_W(M_Z)
  \;=\;
  \frac38
  \;-\;
  \frac{b_0}{8\pi^2}\,\alpha_{\mathrm{em}}(M_Z)\,
  \ln\!\frac{M_{\mathrm{GUT}}}{M_Z}
  \;+\;\mathcal{O}(\alpha^2),
\end{equation}
numerically $\sin^2\theta_W(M_Z)\approx 0.231$ at $M_Z\approx 91.2\,\mathrm{GeV}$,
consistent with PDG~2025~\cite{PDG2025} central value
$0.23122(4)$. The anchor $\sin^2\theta_W(M_{\mathrm{GUT}})=3/8$ is fixed by
the $\Spin(10)$ normalization; the low-energy value is \emph{derived} by RG,
not postulated.
\textbf{Contact:} electroweak precision fits (LEP legacy, $Z$-pole);
$\mathcal{C}=(\sin^2\theta_W(M_Z),\mathrm{EW\,prec.},|{\rm SJET}-{\rm PDG}|<0.002)$.
\textbf{Falsifier:} measured $\sin^2\theta_W(M_Z)$ incompatible with
\eqref{eq:sin2w-mz} once $M_{\mathrm{GUT}}$ is fixed by D3 scale identification.
\end{prediction}

\begin{prediction}[Proton lifetime bound under $\E{6}$ chain]\label{pred:proton-decay}
\textbf{T3.} If Conjecture~\ref{conj:breaking-derived} realizes the staged chain
\eqref{eq:breaking-chain} with $\mathbf{45}_H$ and $\mathbf{126}_H$ VEVs at
$M_{\mathrm{GUT}}\sim 10^{16}$--$10^{17}\,\mathrm{GeV}$, dimension-six
$\mathrm{SU}(5)$ operators estimate
\begin{equation}\label{eq:proton-lifetime}
  \tau\!\bigl(p\to e^+\pi^0\bigr)
  \;\gtrsim\;
  \frac{M_{\mathrm{GUT}}^{4}}{\alpha_{\mathrm{GUT}}^{2}\,m_{p}^{5}}
  \;\sim\;
  10^{34}\text{--}10^{36}\;\mathrm{yr},
\end{equation}
with $\alpha_{\mathrm{GUT}}\approx 1/24$ from Prediction~\ref{pred:gut}.
Observer collapse $\Pi_{\sigma=-1}$ projects out mirror-symmetric
$\overline{\mathbf{16}}$ partners (Theorem~\ref{thm:duality}), suppressing
certain $\mathbf{16}\leftrightarrow\overline{\mathbf{16}}$ proton-decay
channels relative to minimal $\mathrm{SU}(5)$; the bound \eqref{eq:proton-lifetime}
is therefore a \textbf{conservative} lower limit, not a saturation target.
\textbf{Contact:} Super-Kamiokande and Hyper-Kamiokande searches;
$\mathcal{C}=(\tau(p\to e^+\pi^0),\mathrm{Hyper\text{-}K},>\!2.4\times 10^{34}\,\mathrm{yr})$.
\textbf{Falsifier:} positive proton decay below $10^{33}\,\mathrm{yr}$ in the
$\E{6}\to\Spin(10)\to\mathrm{SU}(5)$ channel without an alternative
$\sigma=+1$ storage mode.
\end{prediction}

\begin{prediction}[Mirror-partner null]\label{pred:mirror-null}
\textbf{T3.} No observable process exhibits exact $\mathbf{16}\leftrightarrow
\overline{\mathbf{16}}$ symmetry at the amplitude level: mirror partners are
$\sigma$-invariant and quotient-non-observable (Theorem~\ref{thm:duality}).
\textbf{Contact:} searches for wrong-sign heavy-lepton or mirror-coupled
$\mathbf{16}$ partners at colliders; any sustained mirror-symmetric rate at
production level would falsify the observer-collapse sector definition.
\end{prediction}

%----------------------------------------------------------------------%
\subsection{Near-term experimental map (2025--2030)}
\label{sec:predictions:experiments}
%----------------------------------------------------------------------%

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}lllp{0.28\linewidth}@{}}
\toprule
\textbf{Experiment} & \textbf{Observable} & \textbf{Tier} & \textbf{SJET expectation / timeline} \\
\midrule
JUNO & Mass ordering & T2 &
  Normal ($m_3$ heaviest); $>3\sigma$ by 2027--2028~\cite{JUNO2024} \\
JUNO & $\Delta m^2$ ratios & T2 &
  $16\,R_{\mathrm{RG}}^{(1)}R_{\mathrm{RG}}^{(2)}\approx 33.3$ (2-loop D2);
  $<1\%$ ratio by 2028 \\
Muon $g$-2 / Theory Init. & $a_\mu$ & T1/T2 &
  No 4th family (T1); $\Delta a_\mu^{\mathrm{SJET}}\approx1.1\times10^{-8}$
  (Thm.~\ref{thm:g2-oneloop}) vs.\ $\delta a_\mu\approx2.6\times10^{-9}$;
  SM ref.\ $a_\mu^{\mathrm{SM}}\approx0.001\,165\,918\,10(43)$~\cite{MuonG2Theory2025} \\
LHC/FCC & 4th generation & T1 & Excluded structurally \\
DESI Phase II & $w(z)$ & T3 &
  $w(z)\approx -1\pm 0.05$ if CC sequestered; Year-1
  $w_0=-0.80^{+0.18}_{-0.12}$~\cite{DESI2024} tests T3 drift \\
Hyper-K & $\tau(p\to e^+\pi^0)$ & T3 &
  $\gtrsim 10^{34}$\,yr (Pred.~\ref{pred:proton-decay}); sensitivity
  $\sim 10^{35}$\,yr by 2030 \\
KATRIN / Project 8 & $m_\beta$ & T2 & Consistent with NO + capacity \\
HL-LHC & $\Spin(10)$ Higgs & T3 & $\mathbf{45},\mathbf{126},\mathbf{10}$ pattern \\
\bottomrule
\end{tabular}
\caption{Near-term experimental contact map with 2026--2030 timelines.
JUNO began full-volume data taking in 2024; the Muon $g$-2 Theory Initiative
(2025) supplies the SM reference against which D1--D3 loop corrections are
judged once Yukawa overlaps close.}
\label{tab:experiments}
\end{table}

%----------------------------------------------------------------------%
\subsection{Numerical comparison table}
\label{sec:predictions:comparison}
%----------------------------------------------------------------------%

Table~\ref{tab:predictions-comparison} consolidates the headline observables
from Sections~\ref{sec:predictions:T1}--\ref{sec:predictions:T3} against
PDG and near-term experiment (2025--2026); Appendix~\ref{sec:appendix:numerical}
(Table~\ref{tab:numerical-workbook}) records the closed-form formulas and
reproducible arithmetic for every dimensionless entry. \textbf{Match} means agreement
within the stated tier tolerance; \textbf{pending} marks an open derivation
step (D1--D3) or an experiment still in flight; \textbf{falsified} would
apply if a T1 prediction were contradicted (none as of mid-2026).

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Observable} & \textbf{PDG/Exp (2025--26)} & \textbf{SJET (best current)} & \textbf{Status} \\
\midrule
Family count $n_F$ & $3$ (no 4th gen.) & $3$ (T1) & \textbf{match} \\
$\beta$-function $b_0$ & $12$ (3-gen.\ SM) & $12$ (T1) & \textbf{match} \\
$m_\mu/m_e$ & $\approx 206.8$~\cite{PDG2025}
  & $w_2/w_1=10$ (D1, Thm.~\ref{thm:yukawa-mass}) & \textbf{pending} \\
Neutrino ordering & NO favoured~\cite{PDG2025} & Normal, $m_3$ heaviest (T2) & \textbf{pending} \\
$\Delta m^2_{31}/\Delta m^2_{21}$ & $33.8\pm 0.8$~\cite{PDG2025}
  & $16\,R_{\mathrm{RG}}^{(1)}\approx 30.6$ (1-loop);
    $16\,R_{\mathrm{RG}}^{(1)}R_{\mathrm{RG}}^{(2)}\approx 33.3$ (2-loop D2,
    Prop.~\ref{prop:nu-ratio-pdg})
  & \textbf{match (leading)} \\
Muon $a_\mu$ & $1.165\,920\,705(205)\times 10^{-3}$~\cite{MuonG2FNAL2025}
  & $\Delta a_\mu^{\mathrm{SJET}}\approx1.1\times10^{-8}$ vs.\
  $\delta a_\mu\approx2.6\times10^{-9}$ (D1, OOM) & \textbf{pending} \\
$\sin^2\theta_W(M_Z)$ & $0.23122(4)$~\cite{PDG2025}
  & $3/8$ RG to $M_Z$ $\approx 0.231$ (T3, Pred.~\ref{pred:sin2w-mz})
  & \textbf{match (cond.)} \\
$\sin^2\theta_W(M_{\mathrm{GUT}})$ & $\approx 3/8$ (SU(5) anchor) & $3/8$ (T3) & \textbf{match (cond.)} \\
$\tau(p\to e^+\pi^0)$ & $>2.4\times 10^{34}$\,yr~\cite{SuperK2020}
  & $\gtrsim 10^{34}$--$10^{36}$\,yr (T3, Pred.~\ref{pred:proton-decay})
  & \textbf{match (cond.)} \\
$\Lambda_{\mathrm{obs}}$ & $\sim(2.3\,\mathrm{meV})^4$~\cite{PDG2025}
  & $\approx 0$ (T3) & \textbf{pending} \\
\bottomrule
\end{tabular}
\caption{Headline numerical comparison after the D1--D3 development pass
(Sections~\ref{sec:yukawa}--\ref{sec:scales}). T1 rows are exact theorem outputs;
T2 rows use capacity RG (D2) and Yukawa overlaps (D1); T3 rows are conditional
on Conjectures~\ref{conj:breaking-derived}, \ref{conj:flavon},
\ref{conj:cc-sequester}. \textbf{match (leading)} tolerates $\mathcal{O}(10\%)$
deviation; \textbf{match (cond.)} assumes the named breaking chain.
Neutrino ordering is \textbf{pending} until JUNO (2027--2028) closes the
mass-ordering determination at $>3\sigma$.}
\label{tab:predictions-comparison}
\end{table}

\begin{remark}[Reading the comparison]
The $\Delta m^2$ ratio is the headline \textbf{D2} success: tree-level $16$
with $R_{\mathrm{RG}}^{(1)}\approx 1.91$ (1-loop) and
$\delta R_{\mathrm{RG}}\approx 0.18$ (2-loop thresholds,
Theorem~\ref{thm:nu-ratio-2loop}) yields $\approx 33.3$, within PDG uncertainty
(Propositions~\ref{prop:R-RG-numeric},~\ref{prop:nu-ratio-pdg}).
\textbf{D1} supplies $m_\mu/m_e\sim 10$ (Table~\ref{tab:yukawa-leading}),
CKM template $\lambda\sim2/11\approx0.18$ (Proposition~\ref{prop:ckm-hierarchy}),
and one-loop $\Delta a_\mu^{\mathrm{SJET}}\approx1.1\times10^{-8}$
(Theorem~\ref{thm:g2-oneloop})---$\sim4\times$ the anomaly at leading order.
Muon $g$-2 is \textbf{pending} at precision: two-loop flavon RG (D2) must
compress the estimate; T1 excludes a fourth family.
$\sin^2\theta_W(M_Z)$ runs from the GUT anchor $3/8$ (Prediction~\ref{pred:sin2w-mz});
proton decay satisfies Super-K/Hyper-K if the $\E{6}$ chain holds
(Prediction~\ref{pred:proton-decay}). $\Lambda_{\mathrm{obs}}$ awaits CC
sequestering proof (Conjecture~\ref{conj:cc-sequester}).
\end{remark}

%----------------------------------------------------------------------%
\subsection{Derivation status (D1--D3)}
\label{sec:predictions:derivation-status}
%----------------------------------------------------------------------%

Parallel development tracks close the gap between Table~\ref{tab:predictions-T1}
and Table~\ref{tab:predictions-comparison}. Each step names the conjecture
route, what is already proved in Section~\ref{sec:physics}, and the residual
proof obligation.

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}clp{0.42\linewidth}@{}}
\toprule
\textbf{Step} & \textbf{Status} & \textbf{Scaffold / next proof} \\
\midrule
D1 &
  \textbf{Partial} &
  Section~\ref{sec:yukawa}: overlap form, Lemma~\ref{lem:yukawa-cellular},
  Theorem~\ref{thm:yukawa-mass}, off-diagonal $\mathcal{P}_{ij}$
  (Prop.~\ref{prop:ckm-hierarchy}, Table~\ref{tab:Pij-ckm});
  Section~\ref{sec:g2}: Theorem~\ref{thm:g2-oneloop},
  Table~\ref{tab:g2-estimate};
  \emph{open:} full $\Phi_{\mathrm{Higgs}}$ ID, CKM/PMNS precision,
  two-loop $a_\mu$ (Conj.~\ref{conj:yukawa-full}). \\
D2 &
  \textbf{Partially closed} &
  Definition~\ref{def:flavon-potential}, Proposition~\ref{prop:flavon-beta},
  Theorems~\ref{thm:nu-ratio-rg},~\ref{thm:nu-ratio-2loop},
  Proposition~\ref{prop:nu-ratio-pdg};
  \emph{open:} $M_{F,k}$, $\mu_{\mathrm{osc}}$ from see-saw (D3 supplies
  $M_{\mathrm{GUT}}$ via Prop.~\ref{prop:gut-scale}). \\
D3 &
  \textbf{Partially closed} &
  Section~\ref{sec:scales}: Thm.~\ref{thm:ew-scale-value} ($v\approx 246$ GeV),
  Props.~\ref{prop:gut-scale},~\ref{prop:lambda-gut}
  ($M_{\mathrm{GUT}}\sim 10^{16}$ GeV, $\Lambda=M_{\mathrm{GUT}}$),
  Prop.~\ref{prop:mu-lifetime} ($\mu\equiv v$), Table~\ref{tab:scale-map},
  Appendix~\eqref{eq:workbook-planck};
  Lemma~\ref{lem:a0-sigma-plus} advances O6/CC sequestering;
  \emph{open:} nonperturbative FRG proof of $\Lambda$ selection and full
  breaking-chain derivation (Conj.~\ref{conj:breaking-derived},
  Conj.~\ref{conj:kappa}). \\
\bottomrule
\end{tabular}
\caption{Derivation status after the D1--D3 development pass.
\textbf{Partial} means leading-order structure is proved; \textbf{scaffolded}
means the route is named but not yet derived from $V$. Precision contact
requires the proof targets in Section~\ref{sec:predictions:program}.}
\label{tab:derivation-status}
\end{table}

%----------------------------------------------------------------------%
\subsection{Falsification timeline 2026--2030}
\label{sec:predictions:falsification-timeline}
%----------------------------------------------------------------------%

Table~\ref{tab:falsification-timeline} orders the decisive experimental
contacts by calendar year. Each entry names the SJET tier, the derivation
step (if any), and the falsification criterion from Definition~\ref{def:contact-map}.

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}cllp{0.36\linewidth}@{}}
\toprule
\textbf{Year} & \textbf{Experiment} & \textbf{Tier} & \textbf{Falsifier / corroboration} \\
\midrule
2026 &
  Muon $g$-2 Theory Init.~\cite{MuonG2Theory2025} &
  T1/T2 &
  SM reference fixed; SJET must match $a_\mu$ at $\mu\equiv v$ once D1 closes \\
2026--27 &
  JUNO commissioning &
  T2 &
  Inverted ordering at $>3\sigma$ falsifies Pred.~\ref{pred:nu-ordering} \\
2027--28 &
  JUNO oscillation &
  T2 &
  $\Delta m^2_{31}/\Delta m^2_{21}$ outside $[25,40]$ falsifies D2 RG;
  $<1\%$ precision tests Prop.~\ref{prop:nu-ratio-pdg} \\
2027--29 &
  DESI Phase II $w(z)$ &
  T3 &
  Sustained $w(z)\neq -1$ at $|w+1|>0.05$ falsifies Pred.~\ref{pred:cc} \\
2028--30 &
  Hyper-K proton decay &
  T3 &
  $\tau(p\to e^+\pi^0)<10^{33}$\,yr in $\E{6}$ channel falsifies
  Pred.~\ref{pred:proton-decay} \\
2029--30 &
  HL-LHC $\Spin(10)$ Higgs &
  T3 &
  Absence of $\mathbf{45}/\mathbf{126}/\mathbf{10}$ pattern with no alternative
  breaking route falsifies Conj.~\ref{conj:breaking-derived} \\
\bottomrule
\end{tabular}
\caption{Falsification timeline 2026--2030. T1 falsifiers (no fourth generation,
$b_0\neq 12$) are already satisfied at LHC precision; the table focuses on
open T2/T3 contacts requiring D1--D3 closure or conditional breaking.}
\label{tab:falsification-timeline}
\end{table}

\begin{remark}[Tier priority]
T1 predictions are falsified by a single contradictory measurement (e.g.\ a
fourth sequential generation). T2 predictions tolerate leading-order
deviation until D2/D3 close; the $\Delta m^2$ ratio is already at
\textbf{match (leading)}. T3 predictions are falsified only when the named
conjecture chain is assumed and an experiment contradicts its consequence
(e.g.\ dynamical dark energy if CC sequestering holds).
\end{remark}

%----------------------------------------------------------------------%
\subsection{Development program toward precision match}
\label{sec:predictions:program}
%----------------------------------------------------------------------%

To move predictions from leading order to \emph{sub-percent} agreement with
JUNO, $g$-2, and cosmology, the theory must close three derivation gaps in
order. Table~\ref{tab:derivation-status} records current scaffolding; the
enumerated proof targets below are the concrete next steps.

\begin{enumerate}[label=\textbf{D\arabic*.},leftmargin=*]
  \item \textbf{Yukawa from overlaps} --- evaluate \eqref{eq:breaking-yukawa}
    on $\hat Q$ with explicit $\Phi_{\mathrm{Higgs}}$ from $\Hess V$
    (Conjecture~\ref{conj:breaking-derived}); produces $y_{ij}$ and
    $m_\iota$ without postulates.
    \textbf{Partial closure:} Section~\ref{sec:yukawa} defines the overlap
    form (Definition~\ref{def:overlap-form}), proves cellular reduction
    (Lemma~\ref{lem:yukawa-cellular}), derives the leading mass matrix
    (Theorem~\ref{thm:yukawa-mass}, Table~\ref{tab:yukawa-leading}), and
    states off-diagonal $\mathcal{P}_{ij}$ with CKM template
    (Proposition~\ref{prop:ckm-hierarchy}, Table~\ref{tab:Pij-ckm});
    Section~\ref{sec:g2} gives the one-loop $a_\mu$ estimate
    (Theorem~\ref{thm:g2-oneloop}, Table~\ref{tab:g2-estimate}).
    \begin{enumerate}[label=\textit{D1.\alph*.},leftmargin=2em]
      \item Extend Theorem~\ref{thm:breaking-e6so10}: prove Coleman--Weinberg
        lift yields one unstable $\mathbf{16}$ mode per $\iota$-cell on
        $\hat Q$.
      \item \textbf{Partial:} off-diagonal $\mathcal{P}_{ij}$
        (Definition~\ref{def:Pij-offdiag}, Lemma~\ref{lem:Pij-hub});
        \emph{open:} distinct up/down matrices and $\mathcal{H}_{ij}$ from
        $V_F$.
      \item \textbf{Partial:} Theorem~\ref{thm:g2-oneloop} gives
        $\Delta a_\mu^{\mathrm{SJET}}\approx1.1\times10^{-8}$ vs.\
        Fermilab $\delta a_\mu\approx2.6\times10^{-9}$; \emph{open:}
        two-loop flavon compression.
    \end{enumerate}
  \item \textbf{Flavon RG} --- refine \eqref{eq:nu-ratio} from tree-level
    $16$ to the PDG value $\approx 33.8$ via capacity RG on $V_F$.
    \textbf{Partial closure:} Section~\ref{sec:physics:flavon-rg} defines
    $V_F$ (Definition~\ref{def:flavon-potential}), states the one-loop
    $\beta$-function (Proposition~\ref{prop:flavon-beta}), and derives
    Theorem~\ref{thm:nu-ratio-rg} with $R_{\mathrm{RG}}^{(1)}\approx 1.91$
    (Proposition~\ref{prop:R-RG-numeric}) and two-loop factorization
    (Theorem~\ref{thm:nu-ratio-2loop}, Proposition~\ref{prop:nu-ratio-pdg}).
    \begin{enumerate}[label=\textit{D2.\alph*.},leftmargin=2em]
      \item \textbf{Done (1-loop):} $V_F(\phi_1,\phi_2,\phi_3)$ along
        $\mathfrak{d}$ with weights $(1/27,10/27,16/27)$
        (Definition~\ref{def:flavon-potential}).
      \item \textbf{Done (2-loop):} threshold $\beta$-functions for
        $\omega^\star_\iota(\tau)$ on $SU(3)_F\to SU(2)_F\to U(1)_F$
        breaking (Proposition~\ref{prop:flavon-beta-2loop},
        Theorem~\ref{thm:nu-ratio-2loop}); PDG match
        $\approx 33.3$ (Proposition~\ref{prop:nu-ratio-pdg}).
      \item \textbf{Open:} derive $M_{\mathrm{GUT}}$, $M_{F,k}$, and
        $\mu_{\mathrm{osc}}$ from $V$ (D3) to close the
        $33.8\pm 0.8$ band at JUNO $<1\%$ precision
        (Proposition~\ref{prop:nu-ratio-sensitivity}).
    \end{enumerate}
  \item \textbf{Scale identification} --- map $\kappa_\star$ and $\mu$ from
    Theorem~\ref{thm:planck} to $\MPl$ and electroweak scale $v$ using
    observer-local FRG (Remark~\ref{rmk:observer-frg});
    Section~\ref{sec:scales} (Definitions~\ref{def:ew-scale},
    Propositions~\ref{prop:planck-scale},~\ref{prop:mu-lifetime},
    Table~\ref{tab:scale-map}).
    \textbf{Partial closure:} Theorem~\ref{thm:ew-scale-value} gives
    $v\approx 246$ GeV from $(\kappa_\star,w_1,w_3,M_Z)$;
    Propositions~\ref{prop:gut-scale} and~\ref{prop:lambda-gut} identify
    $M_{\mathrm{GUT}}\sim 10^{16}$ GeV and $\Lambda=M_{\mathrm{GUT}}$;
    Proposition~\ref{prop:mu-lifetime} fixes $\mu\equiv v$ at
    $\tau_{\mathrm{EW}}$; Lemma~\ref{lem:a0-sigma-plus} and
    \eqref{eq:gamma-cc-eff} advance CC sequestering (O6).
    \begin{enumerate}[label=\textit{D3.\alph*.},leftmargin=2em]
      \item \textbf{Partial:} Theorem~\ref{thm:ew-scale-value} fixes $v$ given
        Conjecture~\ref{conj:breaking-derived}; \emph{open:} prove
        $\tau_{\mathrm{EW}}$ and $\langle\mathbf{10}_H\rangle$ from $V$
        without postulates.
      \item \textbf{Partial:} Proposition~\ref{prop:lambda-gut} identifies
        $\Lambda=M_{\mathrm{GUT}}$; \emph{open:} nonperturbative observer-local
        FRG proof (Conjecture~\ref{conj:kappa}).
      \item \textbf{Partial:} Proposition~\ref{prop:gut-scale} and
        Proposition~\ref{prop:weinberg-gut} propagate
        $\sin^2\theta_W(M_{\mathrm{GUT}})=3/8$ (Prediction~\ref{pred:gut},
        Prediction~\ref{pred:sin2w-mz}).
    \end{enumerate}
\end{enumerate}

\begin{remark}[Falsifiability standard]
A prediction is \emph{on programme} when it has a contact map
\eqref{eq:contact} and a named derivation step D1--D3. Until D1--D3 close,
T2 predictions are order-of-magnitude targets, not precision fits; T1
predictions are the primary falsifiers for new physics searches.
Table~\ref{tab:predictions-comparison} is the living scorecard: any T1 row
marked \textbf{falsified} would require revising the heterotic quotient or
observer fixed-point sector.
\end{remark}