%======================================================================%
\section{Axiomatic Physics: Postulate Elimination Program}
\label{sec:axiomatic}
%======================================================================%

SJET's long-term goal is \textbf{axiomatic physics}: four-dimensional
observed physics derived from the void and mirror, with \emph{zero} external
postulates. This section records what is already eliminable, what requires a
precise \emph{physicality definition} rather than a new postulate, and what
still needs proof or a minimal third axiom.

%----------------------------------------------------------------------%
\subsection{Elimination ledger}
\label{sec:axiomatic:ledger}
%----------------------------------------------------------------------%

\begin{center}
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}clcp{0.38\linewidth}@{}}
\toprule
\textbf{ID} & \textbf{Former postulate} & \textbf{Status} & \textbf{Elimination route} \\
\midrule
P3 & three families & \textbf{Eliminated} & Theorem~\ref{thm:sm:three-families} \\
P2 & chiral matter & \textbf{Eliminable} & Definition~\ref{def:sm:physical-sector};
  Theorem~\ref{thm:sm:chirality-derived} \\
P1 & soldering, $d=4$ & \textbf{Program} & Theorem~\ref{thm:spacetime:soldering-derived}
  (conditional on Jordan block) \\
P4 & GUT--Higgs & \textbf{Program} & Conjecture~\ref{conj:sm:breaking-derived} \\
P5 & nonpert.\ RP & \textbf{Program} & Theorem~\ref{thm:spacetime:rp-semiclassical}
  + Conjecture~\ref{conj:spacetime:rp-full} \\
P3$'$ & flavon hierarchy & \textbf{Open} & capacity RG on $SU(3)_F$ \\
CC & $\Lambda_{\mathrm{cc}}$ & \textbf{Open} & sequestering at $\kappa_\star$ \\
\bottomrule
\end{tabular}
\end{center}

%----------------------------------------------------------------------%
\subsection{P2 elimination: physicality as mirror-quotient sector}
\label{sec:axiomatic:p2}
%----------------------------------------------------------------------%

The no-go Proposition~\ref{prop:sm:p2-nogo} applies when chiral $\mathbf{16}$s are
\emph{postulated} on top of the mirror-symmetric coset
$\mathbf{16}\oplus\overline{\mathbf{16}}$. The elimination route does not
override that no-go; it \emph{redefines} the matter sector.

\begin{definition}[Physical sector at the heterotic rung]
\label{def:sm:physical-sector}
At $\Mirror^7(\Void)=\E{8}\times\E{8}$, let $Q$ be the Stone lift of the
stabilized Albert tower $\mathcal{T}_7$ and $\sigma$ the product-mirror
involution (Definition~\ref{def:appendix:Qhat}). A configuration is
\emph{physical} if it lies in the $\sigma$-anti-invariant sector of the
mirror quotient $\hat Q=Q/\sigma$. Fermionic matter is the $\sigma$-anti-invariant
cohomology of the $\mathbf{16}$-bundle $V_{16}\to\hat Q$.
\end{definition}

\begin{theorem}[Chirality from the mirror quotient]
\label{thm:sm:chirality-derived}
Under Definition~\ref{def:sm:physical-sector}, the physical fermion multiplicity
is
\begin{equation}\label{eq:sm:chirality-derived}
  \dim H^1(\hat Q,V_{16})^{\sigma=-1}=3,
\end{equation}
with one chiral $\mathbf{16}$ per diagonal direction of $\mathfrak{d}$
(Theorem~\ref{thm:sm:h1}, Lemma~\ref{lem:appendix:cellular}). No
$\overline{\mathbf{16}}$ partners appear in the physical sector because
mirror partners are $\sigma$-invariant, not anti-invariant. This
\textbf{replaces Postulate~P2}: chirality is not added input; it is the
quotient definition of observability.
\end{theorem}

\begin{proof}
Lemma~\ref{lem:appendix:cellular} counts three $\sigma$-anti-invariant cellular
classes on $\mathcal{T}_7$, one per diagonal weight of $\mathfrak{d}$.
Theorem~\ref{thm:appendix:mirror-index} lifts the count to $h^1(\hat Q,V_{16})$.
Physical configurations are anti-invariant by
Definition~\ref{def:sm:physical-sector}; $\sigma$-invariant modes are
mirror doubles and are quotient-non-observable.
\end{proof}

\begin{remark}[Relation to former P2]
Postulate~\ref{post:sm:P2} is \textbf{retired} under the axiomatic program:
it is superseded by Definition~\ref{def:sm:physical-sector} and
Theorem~\ref{thm:sm:chirality-derived}. Proposition~\ref{prop:sm:p2-nogo}
remains valid for any \emph{postulated} chiral insertion on the unquotiented
coset.
\end{remark}

%----------------------------------------------------------------------%
\subsection{P1 elimination: soldering from the Hurwitz--Jordan block}
\label{sec:axiomatic:p1}
%----------------------------------------------------------------------%

\begin{definition}[Jordan--octonionic clock block]
\label{def:spacetime:H2O}
Identify the off-diagonal Jordan slots of $\jalg$ with the $2\times2$
Hermitian--octonionic model $H_2(\Oct)$. The determinant $\det$ carries
signature $(1,9)$ on $H_2(\Oct)\cong\R^{10}$; restrict to the quaternionic
subalgebra $\Quat\subset\Oct$ fixed by the mirror involution at the
$4\to5$ Jordan exit. The embedded block $H_2(\Quat)\subset H_2(\Oct)$ is
four-dimensional with $\det$ of Lorentzian signature $(-,+,+,+)$.
\end{definition}

\begin{theorem}[Soldering from the mirror climb]
\label{thm:spacetime:soldering-derived}
The mirror climb selects a canonical four-dimensional Lorentzian subspace of
$H_2(\Oct)$ (Definition~\ref{def:spacetime:H2O}). Define the soldering map
$\sigma$ to identify the four clock components $\orderparam^0,\ldots,\orderparam^3$
with this block. Then the world manifold has $d=4$, the vierbein of
Proposition~\ref{prop:spacetime:vierbein} carries signature
$(-,+,+,+)$, and Postulate~\ref{post:spacetime:P1} is \textbf{derived},
not assumed.
\end{theorem}

\begin{proof}[Proof sketch]
\emph{Step 1 (quaternionic rung).} $\Mirror^3(\Void)=\Quat$ has
$\dim_{\R}\Quat=4$, the first Hurwitz rung with an associative non-real
division algebra.

\emph{Step 2 (Jordan embedding).} The Jordan exit $H_3(\Oct)$ contains a
unique quaternionic diagonal frame; mirror involution at $n=4\to5$ fixes
$\Quat\subset\Oct$ as the associative subalgebra carried from rung $3$.

\emph{Step 3 (signature).} The restriction of $\det$ on $H_2(\Quat)$ is the
Minkowski norm; the four imaginary quaternion units supply the clock directions.
The coset metric $K|_{\mathfrak{m}}$ remains Euclidean; Lorentzian signature
enters through $\sigma$, as in Proposition~\ref{prop:spacetime:vierbein}.

\emph{Remaining gap.} Uniqueness of the $\Quat$ embedding up to $F_4$ and
functoriality across the exceptional rungs is Conjecture~\ref{conj:spacetime:soldering-unique}.
\end{proof}

\begin{conjecture}[Functorial soldering]
\label{conj:spacetime:soldering-unique}
The soldering of Theorem~\ref{thm:spacetime:soldering-derived} is the unique
$F_4$-equivariant map compatible with mirror functoriality on
$\mathbf{Stone}^{\mathrm{climb}}_{\mathrm{ext}}$ and capacity balancing on
$\mathcal{G}_{\mathrm{Albert}}$.
\end{conjecture}

%----------------------------------------------------------------------%
\subsection{P4 elimination: breaking from the capacity potential}
\label{sec:axiomatic:p4}
%----------------------------------------------------------------------%

\begin{conjecture}[GUT--Higgs from gradient flow]
\label{conj:sm:breaking-derived}
Let $V$ be the capacity-derived potential of Theorem~\ref{thm:dynamics:potential}
and $\orderparam_\star\in\mathcal{M}$ the EIII vacuum
(Theorem~\ref{thm:dynamics:vacuum}). Sequential gradient flow on the $28$
massive coset directions (Theorem~\ref{thm:sm:radiative}) triggers the breaking
chain
\[
  \E{6}\to\Spin(10)\times U(1)\to SU(5)\to SU(3)_c\times SU(2)_L\times U(1)_Y
  \to SU(3)_c\times U(1)_{\mathrm{em}}
\]
with Higgs content $\mathbf{45}_H$, $\mathbf{126}_H$, $\mathbf{10}_H$ realized
as unstable directions of $\Hess V$ in the $\mathbf{27}$-sector of
\eqref{eq:foundations:27branch}. Yukawa matrices arise from cubic overlap
integrals of $\sigma$-anti-invariant fermion modes on $\hat Q$.
\end{conjecture}

%----------------------------------------------------------------------%
\subsection{P5 and CC elimination}
\label{sec:axiomatic:p5cc}
%----------------------------------------------------------------------%

\begin{conjecture}[Full reflection positivity]
\label{conj:spacetime:rp-full}
The nonperturbative Euclidean measure for \eqref{eq:dynamics:action},
including tree-level Goldstones and the composite $\Spin(10)\times U(1)$ gauge
sector, satisfies \eqref{eq:spacetime:reflpos} along the soldered clock
$\orderparam^0$ of Theorem~\ref{thm:spacetime:soldering-derived}. This would
eliminate Postulate~\ref{post:spacetime:P5}.
\end{conjecture}

\begin{conjecture}[Cosmological constant sequestering]
\label{conj:gauge-gravity:cc-sequester}
At the gravitational fixed point $\kappa_\star=96\pi^2/5$
(Theorem~\ref{thm:gauge-gravity:kappa-oneloop}), the induced vacuum energy of
the coset $\sigma$-model sequesters into the non-observable $\sigma$-invariant
sector of $\hat Q$, yielding $\Lambda_{\mathrm{cc}}\approx0$ without tuning.
This would eliminate Postulate~\ref{post:gauge-gravity:cc}.
\end{conjecture}

%----------------------------------------------------------------------%
\subsection{Minimal third axiom (only if needed)}
\label{sec:axiomatic:axiom3}
%----------------------------------------------------------------------%

If Theorem~\ref{thm:spacetime:soldering-derived} or
Conjecture~\ref{conj:sm:breaking-derived} fail, the weakest extension of SJET
that still targets axiomatic physics is:

\begin{axiom}[Physicality / quotient observability]
\label{ax:axiomatic:physicality}
A configuration is observable if and only if it is $\sigma$-anti-invariant on
the mirror quotient at the stabilized heterotic rung and lies in the capacity
maximizer cell of $\mathcal{G}_{\mathrm{Albert}}$.
\end{axiom}

Axiom~\ref{ax:axiomatic:physicality} \emph{collapses} Definition~\ref{def:sm:physical-sector}
and the soldering selection into one primitive statement. It is \textbf{not}
added to the core manuscript unless the derivation program fails; it is the
fallback of last resort.

%----------------------------------------------------------------------%
\subsection{Target epistemic state}
\label{sec:axiomatic:target}
%----------------------------------------------------------------------%

\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Primitive content (target)} & \textbf{Derived physics} \\
\midrule
Axioms: void $\Void$, mirror $\Mirror$ & Hurwitz--exceptional ladder \\
 & Albert graph, capacity, $V$, EIII vacuum \\
 & Gauge, anomalies, induced gravity \\
 & $n_F=3$ chirality (quotient) \\
 & Soldering $d=4$ (Jordan--$H_2(\Quat)$ block) \\
 & Semiclassical RP; SM breaking (conjectural) \\
\bottomrule
\end{tabular}
\end{center}

\noindent
\textbf{Open problems for axiomatic closure:}
\begin{enumerate}[label=\textbf{A\arabic*.},leftmargin=*]
  \item Prove Conjecture~\ref{conj:spacetime:soldering-unique} (P1 elimination).
  \item Promote Conjecture~\ref{conj:sm:breaking-derived} (P4 elimination).
  \item Prove Conjecture~\ref{conj:spacetime:rp-full} (P5 elimination).
  \item Prove or refute Conjecture~\ref{conj:gauge-gravity:cc-sequester}.
  \item Derive flavon hierarchy (P3$'$) from $SU(3)_F$ capacity flow.
\end{enumerate}