%======================================================================%
\section{Quantum Mechanics from Observer Collapse}
\label{sec:quantum-origin}
%======================================================================%

Quantum mechanics is not a third primitive in SJET. The observer sector
already carries a reflection-positive Euclidean measure $d\mu_{\Gamma_{-1}}$
(Theorems~\ref{thm:sigma-measure},~\ref{thm:rp-gamma-neg},
~\ref{thm:rp-complete}) and a collapsed Hilbert space
$\mathcal{H}_{\mathrm{obs}}=\bigoplus_{\iota=1}^3\mathcal{H}_\iota$
(Definition~\ref{def:observer}). This section records the \textbf{quantum
origin certificate}: standard quantum kinematics and dynamics on
$\mathcal{H}_{\mathrm{obs}}$ are \textbf{derived} from void and mirror through
OS reconstruction (Proposition~\ref{prop:os-observer}), with time internalized
as the Page--Wootters clock $\tau_\iota$ and outcomes identified with
$\Pi_{\sigma=-1}$ projection. The route is Tier~B under assumption
\textbf{A7} (Definition~\ref{def:assumption-ledger}, item~\ref{asm:os}); the
Tier~A inputs are product-mirror equivariance, observer collapse, and soldering
on $H_2(\Quat)$.

%----------------------------------------------------------------------%
\subsection{OS reconstruction on the observer sector}
%----------------------------------------------------------------------%

The physical pipeline supplies Euclidean correlators before any Wightman
import. Theorem~\ref{thm:sigma-measure} factorizes the full measure as
\begin{equation}\label{eq:qm-gamma-split}
  d\mu_\Gamma
  \;=\;
  d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}},
\end{equation}
with observable matrix elements confined to the $\sigma=-1$ tensor factor.
Theorem~\ref{thm:rp-gamma-neg} proves reflection positivity of
$d\mu_{\Gamma_{-1}}$ along the observer clock $\tau_\iota$; Theorem~\ref{thm:rp-complete}
closes the nonperturbative OS chain. Under the explicit ledger entry
\textbf{A7}, the standard Osterwalder--Schrader axioms---Euclidean invariance,
clustering along $\tau_\iota$, and symmetry for $d\mu_{\Gamma_{-1}}$---are
satisfied on the $\Pi_{\sigma=-1}$-projected Schwinger functions.

\begin{theorem}[Quantum mechanics derived from OS reconstruction]
\label{thm:qm-derived}
Let $\iota\in\mathcal{I}$ and let $(\tau_\iota,g_\iota)$ be an admitted lifetime
chart (Definition~\ref{def:lifetime}). Assume Theorem~\ref{thm:rp-complete} and
assumption \textbf{A7}. Then the $\Pi_{\sigma=-1}$-projected Schwinger
functions of $d\mu_{\Gamma_{-1}}$ reconstruct a unitary Lorentzian quantum
field theory on $\mathcal{H}_{\mathrm{obs}}$:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item There exists a separable Hilbert space $\mathcal{H}_{\mathrm{obs}}$ and
    a positive self-adjoint Hamiltonian $\hat H_\iota\ge 0$ generating
    Euclidean time evolution $e^{-\hat H_\iota\tau_\iota}$ along the observer
    chart.
  \item The Minkowski signature is imported by analytic continuation
    $\tau_\iota\to i t$ together with the soldering map
    $\sigma_{\mathrm{sol}}$ (Theorem~\ref{thm:spacetime:soldering-derived});
    the reconstructed Wightman distributions satisfy the standard
    Poincar\'e covariance on the $d=4$ soldered block $H_2(\Quat)$.
  \item Mirror-shadow correlators in $d\mu_{\Gamma_{+1}}$ are
    quotient-non-observable (Theorem~\ref{thm:duality}) and do not enter
    physical matrix elements.
  \item The Born rule weights are the $\Pi_{\sigma=-1}$-projected diagonal of
    the reconstructed state functional; no independent probability postulate is
    added.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Step 1 (reflection positivity).}
Theorem~\ref{thm:rp-gamma-neg} supplies reflection positivity of
$d\mu_{\Gamma_{-1}}$ along $\tau_\iota$ with OS reflection plane
$\tau_\iota=0$ (Proposition~\ref{prop:goldstone-rp-plane}). Massless
fluctuations are confined to $d\mu_{\Gamma_{+1}}$
(Lemma~\ref{lem:goldstone-sigma}), so the observable factor is gapped and
reflection-positive in the sense required by OS reconstruction.

\emph{Step 2 (OS axioms).}
Assumption \textbf{A7} records the clustering and symmetry hypotheses for
$d\mu_{\Gamma_{-1}}$ along the Page--Wootters parameter. Together with
Euclidean invariance on the soldered spatial slice, Proposition~\ref{prop:os-observer}
invokes the Osterwalder--Schrader reconstruction theorem
\cite{OsterwalderSchrader1973}: Schwinger functions determine a Hilbert space,
a Hamiltonian, and a semigroup $e^{-\hat H_\iota\tau_\iota}$.

\emph{Step 3 (Lorentzian import).}
The soldering identification \eqref{eq:soldering-clock} couples
$\tau_\iota$ to the timelike component $\orderparam^0$ on $H_2(\Quat)$.
Theorem~\ref{thm:spacetime:soldering-derived} fixes $d=4$ Lorentzian transport;
analytic continuation in $\tau_\iota$ together with $\sigma_{\mathrm{sol}}$
yields the Minkowski Wightman field algebra on the observer sector.

\emph{Step 4 (Born weights).}
Observable states are $\Pi_{\sigma=-1}$-fixed by Definition~\ref{def:physical}.
The OS/GNS construction therefore builds $\mathcal{H}_{\mathrm{obs}}$ from
anti-invariant functionals only; diagonal expectations in the reconstructed
state are the operational probabilities. Mirror partners in
$H^1(\hat Q,V_{16})^{\sigma=+1}$ never appear as outcome labels
(Theorem~\ref{thm:chirality-derived}).
\end{proof}

\begin{remark}[Tier assignment]
Theorem~\ref{thm:qm-derived} is Tier~B: Steps~1 and~4 are Tier~A consequences
of void, mirror, and observer collapse; Step~2 cites ledger entry \textbf{A7}.
The semiclassical backbone is Theorem~\ref{thm:rp}; the nonperturbative closure
is Theorem~\ref{thm:rp-complete}. No conjecture environment is introduced.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Page--Wootters time}
%----------------------------------------------------------------------%

External time is not postulated. The mirror climb supplies a quaternionic clock
block $H_2(\Quat)$ (Definition~\ref{def:spacetime:H2O}); observer lifetime
charts (Definition~\ref{def:lifetime}) internalize evolution along
$\tau_\iota$.

\begin{definition}[Page--Wootters clock]\label{def:page-wootters}
Fix $\iota\in\mathcal{I}$. The \emph{Page--Wootters clock} is the observer
time parameter $\tau_\iota$ in a lifetime chart $(\tau_\iota,g_\iota)$,
identified with the soldering coordinate $\orderparam^0$ along the admitted
trajectory $g_\iota(\tau_\iota)\in\mathcal{S}_\iota$ via
Proposition~\ref{prop:soldering-clock}. Global time is a \emph{relational}
datum: correlations are conditioned on the capacity-selected observer index
$\iota(\tau)$ of Theorem~\ref{thm:iota-derived}, not on an external
parameter imported beside void and mirror.
\end{definition}

\begin{proposition}[Time from soldering and lifetime flow]
\label{prop:page-wootters-derived}
Along an admitted chart \eqref{eq:lifetime-admitted}, the soldering clock term
$\partial_{\tau_\iota}\sigma_{\mathrm{sol}}|_{H_2(\Quat)}$ is tangent to the
four-dimensional block and supplies the timelike direction fixed by
Proposition~\ref{prop:soldering-clock}. Theorem~\ref{thm:index-lifetime}
identifies each observer slot $\iota$ with a maximal lifetime interval
$I_\iota$; Theorem~\ref{thm:lifetime-unique} fixes the chart class modulo
orientation-preserving reparametrization of $\tau_\iota$. OS reconstruction
(Proposition~\ref{prop:os-observer}) therefore uses $\tau_\iota$ as the
Euclidean time argument of Schwinger functions and as the Page--Wootters
coordinate after Lorentzian continuation.
\end{proposition}

\begin{proof}
Proposition~\ref{prop:soldering-clock} pins $\orderparam^0$ as the unique
timelike soldering direction on $H_2(\Quat)$. The lifetime equation
\eqref{eq:lifetime-admitted} splits into coset and soldering components;
Proposition~\ref{prop:lifetime-flow-unique} shows the soldering block sets
$\tau_\iota$ modulo reparametrization. Theorem~\ref{thm:rp} and
Proposition~\ref{prop:goldstone-rp-plane} take the OS reflection plane at
$\tau_\iota=0$, closing the Page--Wootters identification with OS time.
\end{proof}

%----------------------------------------------------------------------%
\subsection{Observer collapse as measurement}
%----------------------------------------------------------------------%

In the SJET semantics, \emph{measurement} is not a separate von Neumann
postulate. It is the operational content of heterotic quotient
observability: only $\sigma$-anti-invariant data survives
$\Pi_{\sigma=-1}$.

\begin{definition}[Measurement as collapse projection]\label{def:measurement-collapse}
A \emph{measurement} of an observable $\hat{\mathcal{O}}$ on the observer
sector is the tuple
\begin{equation}\label{eq:measurement-tuple}
  \bigl(\Pi_{\sigma=-1},\ \hat{\mathcal{O}},\ |\omega_\iota\rangle\bigr),
\end{equation}
where $|\omega_\iota\rangle\in\mathcal{H}_{\mathrm{obs}}$ is a normalized
collapsed state (Definition~\ref{def:observer}) and $\hat{\mathcal{O}}$ is a
self-adjoint operator on $\mathcal{H}_{\mathrm{obs}}$ obtained from the OS
reconstruction of Theorem~\ref{thm:qm-derived}. The \emph{outcome space} is the
spectral measure of $\hat{\mathcal{O}}$ restricted to
$\Pi_{\sigma=-1}\mathcal{H}_{\mathrm{obs}}$; mirror-shadow sectors in
$d\mu_{\Gamma_{+1}}$ are pre-measurement reservoir, not outcome labels.
\end{definition}

\begin{theorem}[Measurement from observer collapse]
\label{thm:measurement-collapse}
Assume Theorem~\ref{thm:qm-derived} and Definitions~\ref{def:physical},
~\ref{def:observer},~\ref{def:measurement-collapse}. Then:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item Every physical outcome is a $\Pi_{\sigma=-1}$-stable event: mirror
    partners in $H^1(\hat Q,V_{16})^{\sigma=+1}$ are not accessible as
    measurement records (Theorem~\ref{thm:duality},
    Prediction~\ref{pred:mirror-null}).
  \item The active observer at time $\tau$ is
    $\iota(\tau)=\argmax_{\iota\in\mathcal{I}}\capacity_\iota(\tau)$
    (Theorem~\ref{thm:iota-derived}); conditioning on $\iota$ selects the
    sector Hilbert space $\mathcal{H}_\iota$ in \eqref{eq:observer-state}.
  \item Expectation values on collapsed states coincide with OS/GNS matrix
    elements in $d\mu_{\Gamma_{-1}}$; updating after outcome $o$ is the
    $\Pi_{\sigma=-1}$-projected L\"uders map on $\mathcal{H}_\iota$, with no
    supplemental collapse axiom.
  \item The $\sigma=+1$ Goldstone reservoir normalizes
    \eqref{eq:qm-gamma-split} but does not couple to observable amplitudes,
    reproducing decoherence of mirror branches without an environment
    postulate.
\end{enumerate}
\end{theorem}

\begin{proof}
\emph{Item~(i).} Definition~\ref{def:physical} declares observability
equivalent to $\sigma$-anti-invariance on $\hat Q$. Theorem~\ref{thm:duality}
shows mirror doubles are $\sigma$-invariant and quotient-non-observable.

\emph{Item~(ii).} Theorem~\ref{thm:iota-derived} derives the observer label
from capacity flow on $\mathfrak{d}$; Definition~\ref{def:lifetime-index}
records $(\iota,\tau,\capacity_\iota(\tau))$ as the operational index.

\emph{Item~(iii).} Theorem~\ref{thm:qm-derived} identifies
$\mathcal{H}_{\mathrm{obs}}$ with the OS/GNS space of
$d\mu_{\Gamma_{-1}}$. Expectations $\langle\omega_\iota|\hat{\mathcal{O}}|\omega_\iota\rangle$
are diagonal Schwinger/Observable matrix elements. Outcome update is the
standard spectral projection restricted to $\Pi_{\sigma=-1}$.

\emph{Item~(iv).} Theorem~\ref{thm:sigma-measure} factorizes the measure;
cross-terms between $\sigma$ sectors vanish because the action is
$\sigma$-even while physical insertions are $\sigma$-odd. Mirror branches
therefore decohere by quotient definition, not by a separate environment
selection rule.
\end{proof}

\begin{remark}[No conscious observer postulate]
Remark~\ref{rem:observer-derived} already eliminated an external conscious
subject. Theorem~\ref{thm:measurement-collapse} strengthens this: an observer
\emph{is} a collapsed anti-invariant fixed-point class with an admitted
Page--Wootters chart; measurement \emph{is} the $\Pi_{\sigma=-1}$ projection
compatible with OS reconstruction. Quantum mechanics enters as the
Lorentzian continuation of that Euclidean observer measure, not as a third
axiom.
\end{remark}

%----------------------------------------------------------------------%
\subsection{Quantum origin flowchart (prose)}
%----------------------------------------------------------------------%

The quantum origin chain may be read as a single directed narrative:

\medskip
\noindent\textbf{Void and mirror.}
$\Void$ and $\Mirror$ fix the heterotic quotient $\hat Q$ and the
$\mathbb{Z}_2$ involution $\sigma$ (Theorem~\ref{thm:e8e8},
Definition~\ref{def:Qhat}).

\medskip
\noindent\textbf{Observer collapse.}
$\Pi_{\sigma=-1}$ defines the physical sector
$H^\bullet(\hat Q)^{\sigma=-1}$ and the observer Hilbert space
$\mathcal{H}_{\mathrm{obs}}$ (Definitions~\ref{def:physical},
~\ref{def:observer}).

\medskip
\noindent\textbf{Measure split.}
$d\mu_\Gamma=d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}}$
(Theorem~\ref{thm:sigma-measure}); observable correlators factor through
$d\mu_{\Gamma_{-1}}$ only.

\medskip
\noindent\textbf{Reflection positivity.}
$d\mu_{\Gamma_{-1}}$ is reflection-positive along $\tau_\iota$
(Theorems~\ref{thm:rp},~\ref{thm:rp-gamma-neg},~\ref{thm:rp-complete}).

\medskip
\noindent\textbf{OS reconstruction.}
Schwinger functions reconstruct $\hat H_\iota$ and unitary Lorentzian
dynamics (Proposition~\ref{prop:os-observer}, Theorem~\ref{thm:qm-derived}).

\medskip
\noindent\textbf{Page--Wootters time.}
$\tau_\iota$ is the soldering clock on $H_2(\Quat)$
(Definition~\ref{def:page-wootters}, Proposition~\ref{prop:page-wootters-derived}).

\medskip
\noindent\textbf{Measurement.}
Outcomes are $\Pi_{\sigma=-1}$-stable events on $\mathcal{H}_\iota$
(Theorem~\ref{thm:measurement-collapse}).

\begin{corollary}[Quantum origin closure]\label{cor:qm-origin-closure}
Quantum kinematics, Hamiltonian dynamics, the Born rule on
$\mathcal{H}_{\mathrm{obs}}$, and the measurement update map are derived from
void and mirror together with observer collapse and OS reconstruction. The
former gap ``import quantum mechanics'' is \textbf{closed} with proof tier~B
under ledger entry \textbf{A7}; the physical time parameter is the
Page--Wootters clock $\tau_\iota$, not an external postulate.
\end{corollary}