%======================================================================%
\section{Open-Question Derivation Threads}
\label{sec:open-threads}
%======================================================================%

Section~\ref{sec:physics-map} maps every PDG-headline domain through
\eqref{eq:physics-map-pipeline}; Corollary~\ref{cor:physics-map-closure}
certifies \textbf{zero unmapped domains}. Residual work is not missing
\emph{routes} but missing \emph{evaluators} and \emph{limit theorems} on the
same void--mirror datum. This section traces \textbf{nine derivation threads}
identified from the open-question catalog: common patterns among the
$\sim 65$ items not yet at Tier~A/B closure. Each thread records a definition,
question ledger, manuscript anchors, gaps, target $\mathcal{F}_D$ functors,
dependencies, tier-upgrade path, and a boxed pipeline equation. No thread
introduces a third primitive.

%----------------------------------------------------------------------%
\subsection{Master thread map}
\label{sec:open-threads:map}
%----------------------------------------------------------------------%

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.10}
\begin{tabular}{@{}clp{0.42\linewidth}c@{}}
\toprule
\textbf{ID} & \textbf{Thread} & \textbf{Closes (headline)} & \textbf{Sec.} \\
\midrule
I &
  Emergent without evaluator &
  Chemistry, fluids, stellar, bio (Class~V) &
  \ref{sec:thread-1} \\
II &
  Strong-curvature / QG &
  Horizons, BH thermodynamics, Planck regime &
  \ref{sec:thread-2} \\
III &
  Constructive continuum / rigor &
  OS upgrade, mass gap, confinement proof, NS &
  \ref{sec:thread-3} \\
IV &
  Precision / anomaly contact &
  CP phases, $\alpha_s$, hadron $\sim 1\%$, lab anomalies &
  \ref{sec:thread-4} \\
V &
  Cosmological perturbations &
  $P(k)$, inflation detail, BBN network, tensors &
  \ref{sec:thread-5} \\
VI &
  Hadron--nuclear spectroscopy &
  Glueballs, resonances, binding ladder, EMC &
  \ref{sec:thread-6} \\
VII &
  Condensed-matter mechanisms &
  Bands, SC, FQHE, glass transition &
  \ref{sec:thread-7} \\
VIII &
  Arrow of time / entropy &
  Thermodynamic arrow, irreversibility, ensemble &
  \ref{sec:thread-8} \\
IX &
  Phenomenology boundary &
  Honest out-of-scope vs.\ $\mathcal{D}_{\mathrm{ext}}$ &
  \ref{sec:thread-9} \\
\bottomrule
\end{tabular}
\caption{Master map of nine open-question derivation threads. Threads~I--IX
specialize \eqref{eq:universe-summary}; they do not increase the primitive
axiom count.}
\label{tab:open-threads-master}
\end{table}

%----------------------------------------------------------------------%
\subsection{Dependency graph}
\label{sec:open-threads:dependencies}
%----------------------------------------------------------------------%

Threads are not independent. The recommended closure order follows
constructive rigor before precision, precision before cosmology and spectra,
and emergent evaluators after spectroscopy inputs:

\medskip
\noindent\textbf{Wave~1 (foundations) --- \emph{complete}.}
Thread~III (constructive continuum) upgrades assumption~\textbf{A7} to
Theorem~status and supplies the measure backbone for Threads~IV,~V,~II.
Corollary~\ref{cor:thread3-wave1-closure} (Section~\ref{sec:wave1-thread3})
certifies quantitative continuum stability, all-orders $\sigma$-loop
factorization, and Tier~A OS reconstruction; Corollary~\ref{cor:thread4-wave1-partial}
(Section~\ref{sec:wave1-thread4}) records the first precision-thread upgrade
(Jarlskog/CP phases). Wave~2 may proceed.

\medskip
\noindent\textbf{Wave~2 (precision + emergent start) --- \emph{complete}.}
Thread~IV hadron precision is closed in
Corollary~\ref{cor:thread4-wave2-closure}
(Section~\ref{sec:wave2-thread4}).
Thread~V linear perturbation functor is partially closed in
Corollary~\ref{cor:thread5-wave2-closure}
(Section~\ref{sec:wave2-thread5}).
Thread~I opens emergent descent with the first certified
$\mathcal{F}_{\mathrm{emergent}}$ in
Corollary~\ref{cor:thread-1-wave2-partial}
(Section~\ref{sec:wave2-thread1}).
Wave~3 may proceed.

\medskip
\noindent\textbf{Wave~3 (structure).}
Thread~VI (hadron--nuclear $\mathcal{F}_{\mathrm{spec}}$) and residual
Thread~V non-linear refinement run in parallel once Wave~2 is stable.

\medskip
\noindent\textbf{Wave~4 (emergent closure).}
Thread~I (domain evaluators $\mathcal{F}_{\mathrm{emergent}}$) consumes
Thread~VI outputs for nuclear/atomic EFT; Thread~VII (condensed-matter
mechanisms) specializes Thread~I on $\mathcal{T}_7^{(L)}$.

\medskip
\noindent\textbf{Wave~5 (foundational completion).}
Thread~II (strong-curvature $\mathcal{F}_{\mathrm{grav}}$) requires
Thread~III shadow-sector thermodynamics; Thread~VIII (entropy) closes
Thread~II and Thread~VII in the thermodynamic limit.

\medskip
\noindent\textbf{Boundary.}
Thread~IX (phenomenology tier) applies to all waves: observables in
$\mathcal{D}_{\mathrm{ext}}$ are contacts, not derivations, when no
$\mathcal{F}_D$ is named.

\begin{corollary}[Thread ledger closure target]\label{cor:thread-ledger-target}
When Threads~I--IX reach their stated target theorems
(\texttt{thm:thread-1-descent} through \texttt{thm:thread-2-qg},
\texttt{cor:thread3-wave1-closure},
\texttt{cor:thread4-wave2-closure}, \texttt{cor:thread5-wave2-closure},
\texttt{cor:thread-1-wave2-partial}, \texttt{thm:thread6-hadron},
\texttt{thm:thread-7-bands}, \texttt{thm:thread-8-entropy},
and \texttt{def:phenomenology-tier}), the open-question catalog
($\sim 65$ residual items) is partitioned into: \textbf{derived} (functor
named), \textbf{phenomenology} ($\mathcal{D}_{\mathrm{ext}}$ contact), or
\textbf{out of scope} (Thread~IX table). The primitive axiom count remains
$2$; the named conjecture count remains $0$.
\end{corollary}