%======================================================================%
\section{Development Threads V--VI: Cosmological Perturbations and
Hadron--Nuclear Spectroscopy}
\label{sec:threads-5-6}
%======================================================================%

Threads~V and~VI extend the master physics map
(Section~\ref{sec:physics-map}) from \emph{background} cosmology and
\emph{leading} hadronic contacts to the perturbative and spectroscopic
functors required for CMB anisotropies, large-scale structure, and the
full low-energy mass ladder. Both threads are \textbf{descent layers} on the
same pipeline \eqref{eq:physics-map-pipeline}; neither introduces a primitive
beyond $(\Void,\Mirror)$. Thread~III (SM Lagrangian certificate,
Section~\ref{sec:sm-lagrangian}) and Thread~IV (cosmological background
ledger, Sections~\ref{sec:dark-sector},~\ref{sec:cosmology},
~\ref{sec:baryogenesis}) supply the transport inputs $(v,\eta_B,\alpha_{\mathrm{em}},
\Omega_{\mathrm{DM}},H_0^{\mathrm{CMB}},\mathcal{P}_{\sigma=+1})$ that
Threads~V and~VI consume.

%----------------------------------------------------------------------%
\subsection{Thread~5: Cosmological perturbations}
\label{sec:thread-5}
%----------------------------------------------------------------------%

Cosmological \emph{background} quantities---$\Omega_{\mathrm{DM}}$,
$H_0^{\mathrm{CMB}}$, $w(z)\approx -1$, $\eta_B$---are closed in
Threads~III--IV. Thread~V records the \textbf{perturbation functor}: how
$\sigma$-split stress--energy and capacity weights propagate into density
contrasts, growth, and CMB/LSS observables.

\begin{definition}[Thread~5: capacity-graded cosmological perturbation]
\label{def:thread5-pert}
Fix the homogeneous background of Theorems~\ref{thm:hubble-cmb},
~\ref{thm:dm-abundance}, and Prediction~\ref{pred:cc}. Let
$\delta_{\sigma=\pm1}(\mathbf{x},\tau)$ denote the density contrast in the
$\sigma$-graded stress--energy split \eqref{eq:T-split} about
$\orderparam_\star$. The \emph{Thread~5 perturbation datum} is the pair
\begin{equation}\label{eq:thread5-datum}
  \boldsymbol{\delta}
  \;:=\;
  \bigl(
    \delta_{(-1)},\,\delta_{(+1)},\,D_\pm(z),\,P_\pm(k),\,n_s,\,\sigma_8
  \bigr),
\end{equation}
where $\delta_{(-1)}$ is supported on observable baryon--radiation modes in
$H^1(\hat Q,V_{16})^{\sigma=-1}$, $\delta_{(+1)}$ on the mirror-shadow
residue $\mathcal{R}_{+1}$ (Definition~\ref{def:dm-residue}), $D_\pm$ are
linear growth factors in each sector, $P_\pm$ the corresponding matter power
spectra, and $(n_s,\sigma_8)$ the scalar tilt and late-time fluctuation
amplitude contacted in Prediction~\ref{pred:cmb} and
Proposition~\ref{prop:sigma8}.
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}p{0.30\linewidth}p{0.58\linewidth}@{}}
\toprule
\textbf{Unanswered question} & \textbf{SJET status / residual work} \\
\midrule
What sources primordial scalar perturbations without an inflation postulate? &
  Coleman--Weinberg gap on $28$ coset scalars
  (Theorem~\ref{thm:rp}, Lemma~\ref{lem:breaking-cw}) supplies $V>0$;
  ledger Jacobian tilt gives $n_s\neq 1$
  (\eqref{eq:pred-ns}). \textbf{Open:} full curvature perturbation
  $\mathcal{R}$ from $\orderparam$ fluctuations. \\
\addlinespace
How do $\sigma=+1$ shadow modes cluster without observable interactions? &
  Theorem~\ref{thm:dm-sector} identifies $\rho_{\mathrm{DM}}$;
  Proposition~\ref{prop:sigma8} fixes $\sigma_8$ from capacity ratio
  $\sqrt{(w_1+w_2)/w_3}$. \textbf{Open:} non-linear
  $\delta_{(+1)}$ beyond linear growth. \\
\addlinespace
What is the matter power spectrum $P(k)$ at sub-percent accuracy? &
  Leading $P(k)\propto k^{n_s-1}$ with $n_s$ from
  \eqref{eq:pred-ns}. \textbf{Open:} two-loop acoustic peak locations;
  Silk damping from atomic sector
  (Theorem~\ref{thm:atomic-spectrum}). \\
\addlinespace
How does the Hubble ledger affect perturbation observables? &
  $H_0^{\mathrm{loc}}/H_0^{\mathrm{CMB}}=1+1/b_0$ at $z=0$
  (Proposition~\ref{prop:h0-ledger}); BAO $H(z)$ converges at $z\gtrsim 1$
  (Proposition~\ref{prop:hz-ledger}). \textbf{Closed} at linear order. \\
\addlinespace
Are tensor modes required for CMB $B$-modes? &
  No tensor postulate in SJET. \textbf{Open:} $\sigma$-even graviton
  residue routed to $d\mu_{\Gamma_{+1}}$
  (Theorem~\ref{thm:kappa-persistence}) as hidden tensor ledger. \\
\addlinespace
Does $\eta_B$ fix $\Omega_b h^2$ and BBN abundances jointly? &
  \textbf{Closed} triangle: Prediction~\ref{pred:eta-b},
  Theorem~\ref{thm:bbn}, Prediction~\ref{pred:cmb}
  (\eqref{eq:pred-omega-b}). \\
\bottomrule
\end{tabular}
\caption{Thread~5 unanswered questions and SJET closure status. Rows marked
\textbf{Closed} are Tier~B/C contacts; \textbf{Open} rows are honest gaps
for sub-percent LSS/CMB refinement.}
\label{tab:thread5-questions}
\end{table}

\paragraph{SJET anchors.}
Thread~5 is anchored on the following proved or contacted chain:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{$\sigma$-sector stress split.}
    $T_{\mu\nu}=T_{\mu\nu}^{(-1)}+T_{\mu\nu}^{(+1)}$
    (Theorem~\ref{thm:dm-sector}, \eqref{eq:T-split}).
  \item \textbf{Environmental vacuum ledger.}
    $\mathcal{P}_{\sigma=+1}$ and CMB Friedmann constraint
    (Definition~\ref{def:env-pressure}, \eqref{eq:friedmann-cmb}).
  \item \textbf{Shadow abundance and clustering.}
    $\Omega_{\mathrm{DM}}=4/15$ (Theorem~\ref{thm:dm-abundance});
    $\sigma_8=\sqrt{11/16}$ (Proposition~\ref{prop:sigma8}).
  \item \textbf{Baryon sector.}
    $\eta_B\approx 6\times 10^{-10}$ (Theorem~\ref{thm:baryogenesis});
    $\Omega_b h^2$ (Prediction~\ref{pred:cmb}, \eqref{eq:pred-omega-b}).
  \item \textbf{Scalar tilt.}
    $n_s=1-(w_2/w_3)(b_0-n_F)/\kappa_\star$ (Prediction~\ref{pred:cmb},
    \eqref{eq:pred-ns}).
  \item \textbf{Hubble anchors.}
    Theorems~\ref{thm:hubble-local},~\ref{thm:hubble-cmb};
    DESI $H(z)$ contact (Prediction~\ref{pred:hz}).
\end{enumerate}

\paragraph{Gaps.}
Thread~5 does \textbf{not} yet supply:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Partially closed (Wave~2).}
    The linear two-fluid Boltzmann hierarchy
    \eqref{eq:thread5-growth}--\eqref{eq:thread5-kstar} is derived in
    Section~\ref{sec:wave2-thread5}; full curvature perturbation
    $\mathcal{R}$ from $\orderparam$ fluctuations and multi-loop peak
    locations remain open.
  \item Non-linear matter power spectrum or halo mass function beyond
    linear $\sigma_8$.
  \item CMB lensing amplitude $A_L$ and full acoustic peak spectrum at
    Planck precision.
  \item Tensor-to-scalar ratio $r$ from the $\sigma=+1$ graviton reservoir.
\end{enumerate}
These are Tier~C refinement targets (Section~\ref{sec:tier-c-precision}), not
epistemic primitives.

\paragraph{Wave~2 partial closure (Thread~5).}
The capacity two-fluid growth system, perturbation ledger identities, and
leading matter power spectrum with first acoustic scale $k_\star$ are proved in
Section~\ref{sec:wave2-thread5}
(Theorems~\ref{thm:thread5-target},~\ref{prop:thread5-ledger},
~\ref{thm:thread5-power}; Corollary~\ref{cor:thread5-wave2-closure}).
Residual items are non-linear $P(k)$, CMB lensing $A_L$, and tensor ratio $r$.

\paragraph{Target functor $\mathcal{F}_D$ and theorems.}
The Thread~5 evaluator is
\begin{equation}\label{eq:FD-cosmo-pert}
  \mathcal{F}_{\mathrm{cosmo\text{-}pert}}
  \;:=\;
  \mathrm{eval}_{\sigma\text{-}\mathrm{pert}}
  \;:\;
  \mathbf{Struct}\times\mathbf{Ledger}
  \longrightarrow
  \mathbf{PertObs},
\end{equation}
with $\mathbf{PertObs}$ the contact layer
$(\delta_\pm,P_\pm,n_s,\sigma_8,f\sigma_8,\Omega_b h^2)$.
The target theorem bundle
(\texttt{thm:thread5-target}, \texttt{prop:thread5-ledger},
\texttt{thm:thread5-power}) is proved in Section~\ref{sec:wave2-thread5}
(Theorems~\ref{thm:thread5-target},~\ref{prop:thread5-ledger},
~\ref{thm:thread5-power}; Corollary~\ref{cor:thread5-wave2-closure}).
The programme table below records pre-Wave~2 status; see
Remark~\ref{rmk:thread5-wave2-table} for post-Wave~2 upgrades.

\paragraph{Dependencies (Threads~III--IV).}
\begin{center}
\small
\renewcommand{\arraystretch}{1.10}
\begin{tabular}{@{}llp{0.50\linewidth}@{}}
\toprule
\textbf{Thread} & \textbf{Input} & \textbf{Role in Thread~5} \\
\midrule
III &
  $\mathcal{L}_{\mathrm{SM}}$, $v$, $M_Z$, $\alpha_{\mathrm{em}}$
  (Sections~\ref{sec:sm-lagrangian},~\ref{sec:scales}) &
  BBN weak rates, recombination $T_\star$, Coulomb sector for $P(k)$ damping. \\
III &
  $\eta_B$ (Theorem~\ref{thm:baryogenesis}) &
  Baryon density contrast normalization; $\Omega_b h^2$
  (\eqref{eq:pred-omega-b}). \\
IV &
  $\Omega_{\mathrm{DM}}=4/15$ (Theorem~\ref{thm:dm-abundance}) &
  $\delta_{(+1)}$ background; structure formation driver. \\
IV &
  $H_0^{\mathrm{CMB}}$, $\mathcal{P}_{\sigma=+1}$
  (Theorems~\ref{thm:hubble-cmb},~\ref{thm:cc-sequester}) &
  Expansion rate; effective $\Omega_\Lambda^{\mathrm{eff}}$ in growth. \\
IV &
  $w(z)\approx -1$ (Prediction~\ref{pred:cc}) &
  Scale-invariant vacuum stress; ISW suppression at low $z$. \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Tier path.}
\begin{equation}\label{eq:thread5-tier}
  \boxed{%
  \mathrm{Tier~A}
  \;\xrightarrow{\;\text{partition}\;}
  \mathrm{Tier~B}
  \;\xrightarrow{\;\textbf{A1,A7,A8}\;}
  \mathrm{Tier~C}
  }
  \qquad
  (w_1,w_2,w_3)
  \to
  (\Omega_{\mathrm{DM}},\sigma_8,n_s)
  \to
  \text{DESI/Euclid/Planck contacts}.
\end{equation}
Tier~A: Theorem~\ref{thm:partition} fixes the capacity weights.
Tier~B: Theorems~\ref{thm:dm-sector},~\ref{thm:cc-sequester},
~\ref{thm:baryogenesis} under \textbf{A1}, \textbf{A7}, \textbf{A8}.
Tier~C: Proposition~\ref{prop:sigma8}, Prediction~\ref{pred:cmb},
Prediction~\ref{pred:hz} at stated tolerances.

\begin{equation}\label{eq:thread5-boxed}
  \boxed{%
  \mathcal{F}_{\mathrm{cosmo\text{-}pert}}
  \bigl(
    \Pi_{\sigma=-1}\circ\mathrm{Bal}_{\mathcal{C}}\circ\Mirror^{\leq 8}
  \bigr)(\Void)
  \;=\;
  \Bigl\{
    \sigma_8=\sqrt{\tfrac{w_1+w_2}{w_3}},\;
    n_s=1-\tfrac{w_2}{w_3}\tfrac{b_0-n_F}{\kappa_\star},\;
    \Omega_b h^2=\kappa_B\eta_{10}(1+\tfrac{w_1}{b_0})
  \Bigr\}.
  }
\end{equation}

%----------------------------------------------------------------------%
\subsection{Thread~6: Hadron and nuclear spectroscopy functor}
\label{sec:thread-6}
%----------------------------------------------------------------------%

Thread~VI closes the \textbf{nonperturbative spectroscopy} route from
cellular overlap data on $\mathcal{T}_7$ to hadron masses, nuclear binding
ladders, and atomic/CMB transport contacts. Yukawa overlaps
(Section~\ref{sec:yukawa}) fix perturbative quark masses; QCD confinement
(Section~\ref{sec:qcd}) and nuclear--cosmology mapping
(Section~\ref{sec:nuclear-atomic-cosmo}) supply the leading spectroscopic
contacts.

\begin{definition}[Thread~6: spectroscopy evaluator]
\label{def:thread6-spec}
Let $\Lambda_{\mathrm{QCD}}$ be the confinement scale of
Definition~\ref{def:lambda-qcd} (equivalently Proposition~\ref{prop:alpha-s},
\eqref{eq:Lambda-QCD}). For each colour-singlet hadron $H$ with constituent
slots $(i,j,k)$ on $\mathcal{T}_7$, let $\mathcal{A}_H$ be the hadronic
overlap of Definition~\ref{def:hadron-overlap}. For each nucleus with mass
number $A$, let $\mathcal{N}_A$ denote the $A$-fold nuclear overlap
(Definition~\ref{def:nuclear-overlap}, Theorem~\ref{thm:nuclear-binding}).
The \emph{Thread~6 spectroscopy datum} is
\begin{equation}\label{eq:thread6-datum}
  \boldsymbol{\mathcal{S}}
  \;:=\;
  \Bigl\{
    m_H=\Lambda_{\mathrm{QCD}}\,|\mathcal{A}_H|^{1/n_q}
  \Bigr\}_{H\in\mathcal{H}}
  \;\cup\;
  \Bigl\{
    E_B(A)/A=\Lambda_{\mathrm{QCD}}\,\tfrac{w_2}{w_3 b_0}\,\mathcal{F}(A)
  \Bigr\}_{A\in\mathbb{N}}.
\end{equation}
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}p{0.30\linewidth}p{0.58\linewidth}@{}}
\toprule
\textbf{Unanswered question} & \textbf{SJET status / residual work} \\
\midrule
What fixes the hadron mass spectrum beyond the proton and pion? &
  Definition~\ref{def:hadron-overlap} and
  Lemma~\ref{lem:hadron-cellular} reduce masses to hub triple
  intersections; Prediction~\ref{pred:hadron-masses} contacts
  $m_p$, $m_\pi$, $m_\rho$. \textbf{Open:} full PDG baryon/meson table. \\
\addlinespace
Why do nuclear magic numbers include $28=n_S$? &
  Theorem~\ref{thm:nuclear-binding}: shell closures at
  $A_\star\in\{2,8,20,28\}$ from $28$ coset scalars
  (Theorem~\ref{thm:planck}). \textbf{Closed} at leading order. \\
\addlinespace
What is the binding energy per nucleon at the iron peak? &
  \eqref{eq:binding-peak}: $\max E_B/A\approx 11$\,MeV from
  $\Lambda_{\mathrm{QCD}}w_2/(w_3 b_0)$. \textbf{Open:} two-body and
  three-body force refinements ($\mathcal{O}(20\%)$). \\
\addlinespace
How does $\Lambda_{\mathrm{QCD}}$ enter without a separate confinement axiom? &
  Definition~\ref{def:lambda-qcd} from $n_F=3$ and $\alpha_s(M_Z)$;
  Proposition~\ref{prop:alpha-s} from ledger FRG. \textbf{Closed}. \\
\addlinespace
What links hadronic scales to BBN and CMB? &
  Section~\ref{sec:nuclear-atomic-cosmo}: deuteron gate
  \eqref{eq:deuteron-binding}, $Y_p$, $D/H$, $T_{\mathrm{CMB}}$,
  $\Omega_b h^2$. \textbf{Closed} at Tier~B/C. \\
\addlinespace
Can excited resonances and Regge trajectories be derived? &
  \textbf{Open:} $\iota=2$ excitation ansatz in \eqref{eq:mrho-pred};
  no Regge functor yet. \\
\bottomrule
\end{tabular}
\caption{Thread~6 unanswered questions and SJET closure status. Hadronic
masses are Tier~C contacts at $\mathcal{O}(10\%)$; nuclear magic-number
routing is Tier~B.}
\label{tab:thread6-questions}
\end{table}

\paragraph{SJET anchors.}
Thread~6 is anchored on:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Colour gauge and confinement.}
    Theorem~\ref{thm:qcd-derived}; Theorem~\ref{thm:confinement};
    $\sigma_{\mathrm{str}}=w_3\Lambda_{\mathrm{QCD}}^2$
    (\eqref{eq:string-tension}).
  \item \textbf{Strong coupling and scale.}
    Proposition~\ref{prop:alpha-s} ($\alpha_s(M_Z)$, $\Lambda_{\mathrm{QCD}}$);
    Theorem~\ref{thm:strong-cp} ($\theta_{\mathrm{obs}}=0$).
  \item \textbf{Hadronic overlaps.}
    Definition~\ref{def:hadron-overlap}, Lemma~\ref{lem:hadron-cellular},
    Prediction~\ref{pred:hadron-masses}.
  \item \textbf{Nuclear overlaps.}
    Definition~\ref{def:nuclear-overlap}, Lemma~\ref{lem:nuclear-cellular},
    Theorem~\ref{thm:nuclear-binding}.
  \item \textbf{Atomic and CMB transport.}
    Theorem~\ref{thm:atomic-spectrum}, Theorem~\ref{thm:bbn},
    Prediction~\ref{pred:cmb} (Table~\ref{tab:nuclear-cosmo-map}).
  \item \textbf{Coset multiplicity.}
    $n_S=28$ (Theorem~\ref{thm:planck}) in magic numbers
    \eqref{eq:magic-numbers}.
\end{enumerate}

\paragraph{Gaps.}
Thread~6 does \textbf{not} yet supply:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item A complete excited-state spectrum (meson/baryon towers, Regge slopes).
  \item Sub-percent hadron mass predictions (lattice-quality).
  \item Microscopic nuclear shell model from $\mathcal{T}_7$ dynamics.
  \item Three-body nuclear forces and $A>56$ stability curve.
\end{enumerate}
The transport theorems of Section~\ref{sec:nuclear-atomic-cosmo} are honest
Tier~B/C: SM+QCD+hydrogen Hamiltonian with SJET-fixed parameters.

\paragraph{Target functor $\mathcal{F}_D$ and theorems.}
The Thread~6 evaluator is
\begin{equation}\label{eq:FD-spec}
  \mathcal{F}_{\mathrm{spec}}
  \;:=\;
  \mathrm{eval}_{\mathrm{overlap\text{-}spectroscopy}}
  \;:\;
  \mathbf{Struct}\times\mathbf{Ledger}
  \longrightarrow
  \mathbf{SpecObs},
\end{equation}
with $\mathbf{SpecObs}$ the mass and binding contact layer. Target theorem
bundle:

\begin{theorem}[Hadron mass functor, target]
\label{thm:thread6-hadron}
Assume Definition~\ref{def:thread6-spec},
Lemma~\ref{lem:hadron-cellular}, Theorem~\ref{thm:confinement}, and
Proposition~\ref{prop:alpha-s}. The assignment
\begin{equation}\label{eq:thread6-hadron-functor}
  H
  \;\longmapsto\;
  m_H
  \;=\;
  \Lambda_{\mathrm{QCD}}\,
  \Bigl|\sum_{\{i,j,k\}}
  \epsilon_{ijk}\sqrt{w_iw_jw_k}\,
  \mathcal{P}_{ijk}\,
  \mathrm{pair}(C_i,C_j,C_k;\chi_{\mathrm{flux}})\Bigr|^{1/n_q}
\end{equation}
is functorial under cellular triality (Proposition~\ref{prop:triality}) and
capacity exchange on $\mathfrak{d}$. It specializes to
Prediction~\ref{pred:hadron-masses} for $H\in\{p,\pi,\rho\}$.
\end{theorem}

\begin{theorem}[Nuclear binding functor, target]
\label{thm:thread6-nuclear}
Assume Definition~\ref{def:nuclear-overlap},
Theorem~\ref{thm:nuclear-binding}, and Theorem~\ref{thm:thread6-hadron}.
The binding energy per nucleon satisfies
\begin{equation}\label{eq:thread6-binding-functor}
  \frac{E_B(A)}{A}
  \;=\;
  \Lambda_{\mathrm{QCD}}\,
  \frac{w_2}{w_3 b_0}\,
  \mathcal{F}(A)
  \;+\;
  \sum_{H\in\mathcal{H}_A}\frac{m_H}{A}\,\mathcal{O}(\alpha_s),
\end{equation}
with $\mathcal{F}(A)$ peaked at $A_\star\in\{2,8,20,28\}$ of
\eqref{eq:magic-numbers}. The deuteron point is
$E_B^{(2)}(d)=2\Lambda_{\mathrm{QCD}}(w_1/w_3)\alpha_s/(4\pi)$
(\eqref{eq:deuteron-binding}).
\end{theorem}

\begin{proposition}[Spectroscopy--cosmology bridge, target]
\label{prop:thread6-cosmo-bridge}
Under Theorems~\ref{thm:thread6-hadron},~\ref{thm:thread6-nuclear},
Theorem~\ref{thm:bbn}, and Prediction~\ref{pred:cmb}, the parameter vector
\begin{equation}\label{eq:thread6-bridge}
  (\Lambda_{\mathrm{QCD}},\,m_p,\,E_B^{(2)}(d),\,\alpha_{\mathrm{em}}(0),\,\eta_B)
\end{equation}
fixes $(Y_p,D/H,\Omega_b h^2,T_{\mathrm{CMB}})$ without additional
cosmological input. Thread~6 output feeds Thread~5 through $\Omega_b h^2$
and BBN-initiated $\delta_b$.
\end{proposition}

\paragraph{Dependencies (Threads~III--IV).}
\begin{center}
\small
\renewcommand{\arraystretch}{1.10}
\begin{tabular}{@{}llp{0.50\linewidth}@{}}
\toprule
\textbf{Thread} & \textbf{Input} & \textbf{Role in Thread~6} \\
\midrule
III &
  Yukawa overlaps, quark masses
  (Theorems~\ref{thm:yukawa-mass},~\ref{thm:quark-mass-2loop}) &
  Flavour insertions in $\mathcal{A}_H$, $\mathcal{N}_B$;
  isospin splitting \eqref{eq:isospin-split}. \\
III &
  $\mathrm{SU}(3)_c$ breaking chain
  (Theorem~\ref{thm:qcd-derived}) &
  Colour flux bundle $V_3$; flux tube $\chi_{\mathrm{flux}}$. \\
III &
  $V(\orderparam)$, $n_S=28$
  (Definitions~\ref{def:potential}, Theorem~\ref{thm:planck}) &
  Magic numbers; saturation scale $w_2/(w_3 b_0)$. \\
IV &
  $b_0=12$, $\kappa_\star$ (Theorem~\ref{thm:beta},~\ref{thm:kappa}) &
  Ledger normalization in binding ladder and $\alpha_s$ residue. \\
IV &
  $\eta_B$ (Theorem~\ref{thm:baryogenesis}) &
  BBN network; $\Omega_b h^2$ closure with Thread~5. \\
IV &
  $H_0^{\mathrm{CMB}}$ (Theorem~\ref{thm:hubble-cmb}) &
  $T_{\mathrm{CMB}}$ and photon phase-space density
  (Definition~\ref{def:t-cmb}). \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Tier path.}
\begin{equation}\label{eq:thread6-tier}
  \boxed{%
  \mathrm{Tier~A}
  \;\xrightarrow{\;\text{cellular}\;}
  \mathrm{Tier~B}
  \;\xrightarrow{\;\textbf{A3,A4,A7}\;}
  \mathrm{Tier~C}
  }
  \qquad
  \mathcal{T}_7\ \text{overlaps}
  \to
  \text{confinement, }\Lambda_{\mathrm{QCD}}
  \to
  m_H,\,E_B/A\ \text{PDG contacts}.
\end{equation}
Tier~A: Lemma~\ref{lem:yukawa-cellular}, Lemma~\ref{lem:hadron-cellular}
(cellular cohomology + Stone lift).
Tier~B: Theorems~\ref{thm:qcd-derived},~\ref{thm:confinement},
~\ref{thm:strong-cp} under \textbf{A3}, \textbf{A4}, \textbf{A7}.
Tier~C: Prediction~\ref{pred:hadron-masses},
Theorem~\ref{thm:nuclear-binding}, Table~\ref{tab:qcd-map},
Table~\ref{tab:nuclear-cosmo-map}.

\begin{equation}\label{eq:thread6-boxed}
  \boxed{%
  \mathcal{F}_{\mathrm{spec}}
  \bigl(
    \Pi_{\sigma=-1}\circ\mathrm{Bal}_{\mathcal{C}}\circ\Mirror^{\leq 8}
  \bigr)(\Void)
  \;=\;
  \Bigl\{
    m_H=\Lambda_{\mathrm{QCD}}\,|\mathcal{A}_H|^{1/n_q},\;
    \tfrac{E_B(A)}{A}=\Lambda_{\mathrm{QCD}}\,\tfrac{w_2}{w_3 b_0}\,\mathcal{F}(A)
  \Bigr\}_{H,A}.
  }
\end{equation}

%----------------------------------------------------------------------%
\subsection{Thread coupling: V $\leftrightarrow$ VI}
\label{sec:threads-5-6-coupling}
%----------------------------------------------------------------------%

Threads~V and~VI are not independent: nuclear and atomic transport
(Section~\ref{sec:nuclear-atomic-cosmo}) supplies the matter sector
parameters that Thread~5 integrates into perturbation observables.

\begin{proposition}[Thread~5--6 closure triangle]
\label{prop:threads-56-triangle}
The parameter chain
\begin{equation}\label{eq:threads-56-triangle}
  \mathcal{F}_{\mathrm{spec}}
  \;\Longrightarrow\;
  (\Lambda_{\mathrm{QCD}},\eta_B,\alpha_{\mathrm{em}},m_p)
  \;\Longrightarrow\;
  \mathcal{F}_{\mathrm{cosmo\text{-}pert}}
  \;\Longrightarrow\;
  (\Omega_b h^2,\,Y_p,\,D/H,\,n_s,\,\sigma_8)
\end{equation}
is closed at Tier~B/C with no fourth cosmological or hadronic primitive.
Predictions~\ref{pred:eta-b},~\ref{pred:bbn},~\ref{pred:cmb}, and
Prediction~\ref{pred:dm} are the experimental vertices.
\end{proposition}

\begin{remark}[Placement in the physics map]
Thread~5 specializes Class~IV of Section~\ref{sec:physics-map:grouping}
($\mathcal{F}_D=\mathrm{eval}_{\sigma\mathrm{-split}}$ on perturbations).
Thread~6 specializes the nuclear and QCD rows of
Table~\ref{tab:physics-map-complete} beyond the emergent label, upgrading
hadron and binding entries to overlap-derived functors. Both threads inherit
the master pipeline \eqref{eq:physics-map-pipeline} and remain subordinate to
the two-axiom primitive count of Theorem~\ref{thm:universe-summary}.
\end{remark}