%======================================================================%
\section{Derivation Threads I--II: Emergent Descent and Strong-Curvature Gravity}
\label{sec:threads-1-2}
%======================================================================%

Sections~\ref{sec:emergent} and~\ref{sec:physics-map} record two frontier
routes that are \textbf{mapped} but not yet \textbf{certified} by closed
domain evaluators $\mathcal{F}_D$. \textbf{Thread~1} (emergent without
evaluator) traces chemistry, condensed matter, thermodynamics, and allied
many-body domains through iterated observer collapse
$\mathcal{E}_N=(\Pi_{\sigma=-1})^{\otimes N}$ on $\mathcal{T}_7$
(Section~\ref{sec:emergent}) without postulating a third primitive.
\textbf{Thread~2} (strong-curvature / quantum gravity) traces Planck-scale and
horizon physics through the induced-gravity chain
(Theorems~\ref{thm:planck},~\ref{thm:kappa},~\ref{thm:kappa-persistence})
and the $\sigma$-sector measure split (Theorem~\ref{thm:sigma-measure}).
Neither thread introduces new axioms; both specialize the master pipeline
\eqref{eq:physics-map-pipeline} to named evaluators still to be proved.

%----------------------------------------------------------------------%
\subsection{Thread~1: Emergent physics without domain evaluator}
\label{sec:thread-1}
%----------------------------------------------------------------------%

\paragraph{Thread definition.}
\textbf{Thread~1} is the \emph{descent-without-evaluator} route: once the
fundamental contact layer
$\mathfrak{E}=\mathcal{U}(\Pi_{\sigma=-1}\circ\mathrm{Bal}_{\mathcal{C}}
\circ\Mirror^{\leq 8})(\Void)$
(Theorem~\ref{thm:universe-summary}) fixes SM gauge--Yukawa--Higgs content,
induced $d=4$ gravity, and OS quantum mechanics on $\mathcal{H}_{\mathrm{obs}}$,
all laboratory-scale many-body physics is obtained by \textbf{coarse-graining}
the same $\Pi_{\sigma=-1}$ data---not by importing a new field species.
Section~\ref{sec:emergent} supplies the core descent operator
$\mathcal{E}_N$, the capacity shell ladder, the replica thermodynamic limit,
and the $\sigma$-measure capacity ensemble; Table~\ref{tab:physics-map-complete}
(Class~V) nonetheless lists twenty emergent subfields with route
\emph{Emergent} and functor
$\mathcal{F}_D=\mathrm{eval}_{\mathrm{emergent}}$ \emph{without} a dedicated
closure certificate analogous to Theorem~\ref{thm:qm-derived} or
Theorem~\ref{thm:dm-sector}. Thread~1 closes that \textbf{evaluator gap}:
every Class~V row must factor through a single named
$\mathcal{F}_{\mathrm{emergent}}$ assembled from $\mathcal{E}_N$, flavon
overlap networks, and standard EFT on Class~I--II outputs.

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.10}
\begin{tabular}{@{}clp{0.52\linewidth}@{}}
\toprule
\textbf{ID} & \textbf{Prior catalog question} & \textbf{Thread~1 closure target} \\
\midrule
EM-CHEM &
  Periodic table / valence beyond noble-gas leading order &
  Theorem~\ref{thm:chemistry-ladder} $\to$
  \texttt{thm:thread-1-descent} (spectroscopic refinement) \\
EM-BAND &
  Quantitative electronic band gaps &
  Theorem~\ref{thm:condensed-matter} $\to$
  \texttt{thm:thread-1-bands} (Bloch determinant contact) \\
EM-SC &
  Superconductivity, fractional QHE, strong correlation &
  Remark~\ref{rmk:emergent-honest} open frontier $\to$
  \texttt{prop:thread-1-correlation} (overlap percolation) \\
EM-ATOM &
  Atomic / molecular spectra, reaction rates &
  Physics-map Tier~C rows $\to$
  \texttt{cor:thread-1-qed} (QED on SM $U(1)_{\mathrm{em}}$) \\
EM-THERMO &
  Heat capacities, critical exponents &
  Theorem~\ref{thm:thermodynamics} $\to$
  \texttt{thm:thread-1-critical} (Yukawa--band refinement) \\
EM-FLUID &
  Navier--Stokes, MHD, fusion plasma &
  Class~V hydrodynamic rows $\to$
  \texttt{def:thread-1-continuum} (continuum limit functor) \\
EM-ASTRO &
  Stellar structure, nucleosynthesis transport &
  Section~\ref{sec:nuclear-atomic-cosmo} contact $\to$
  \texttt{prop:thread-1-stellar} (opacity EFT envelope) \\
EM-BIO &
  Molecular folding, neural / cellular scales &
  Biophysics emergent rows $\to$
  \texttt{rmk:thread-1-bio} (statistical envelope, no new $\mathcal{F}_D$) \\
EM-EVAL &
  No named $\mathcal{F}_D$ for Class~V (physics-map gap) &
  \texttt{def:thread-1-evaluator} certifies
  $\mathcal{F}_{\mathrm{emergent}}$ \\
\bottomrule
\end{tabular}
\caption{Unanswered questions from the physics-map and emergent-physics catalogs
that Thread~1 is designed to close. Rows cite
Table~\ref{tab:physics-map-complete} (Class~V), Remark~\ref{rmk:emergent-honest},
and Section~\ref{sec:emergent:map}.}
\label{tab:thread-1-questions}
\end{table}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}llp{0.46\linewidth}@{}}
\toprule
\textbf{Label} & \textbf{Object} & \textbf{Role in Thread~1} \\
\midrule
\ref{def:emergent-descent} &
  $\mathcal{E}_N=(\Pi_{\sigma=-1})^{\otimes N}$ &
  Many-body descent seed; tensor replication on $\mathcal{T}_7$ \\
\ref{prop:emergent-functor} &
  Additivity, locality, quotient &
  Functoriality certificate for $N\mapsto\mathcal{E}_N$ \\
\ref{def:flavon-network} &
  Overlap graph $G_Z$ &
  Chemistry bonding avatar at atomic scale \\
\ref{thm:chemistry-ladder} &
  Capacity shell ladder &
  Periodic-table leading-order closure \\
\ref{def:replica-limit} &
  $L\to\infty$, $N=\rho L^3$ &
  Condensed-matter thermodynamic limit \\
\ref{thm:condensed-matter} &
  Fermi liquid, Bloch bands &
  Replica-limit band theory \\
\ref{def:capacity-ensemble} &
  $d\nu_\beta\propto e^{-\beta\hat H_\iota}d\mu_{\Gamma_{-1}}$ &
  Equilibrium thermodynamics seed \\
\ref{thm:thermodynamics} &
  $\mathcal{Z}$, $F$, $S$ from $\sigma$-measure &
  Statistical mechanics without Gibbs postulate \\
\ref{thm:qm-derived} &
  OS reconstruction on $\mathcal{H}_{\mathrm{obs}}$ &
  Quantum kinematics for emergent sectors \\
\ref{thm:breaking-complete} &
  SM gauge content after $\E{6}$ breaking &
  Input EFT for chemistry and matter \\
\ref{tab:emergent-map} &
  Descent correspondence table &
  Honest tier assignment (B/C throughout) \\
\ref{rmk:emergent-honest} &
  Non-closure disclaimer &
  Gap ledger for Thread~1 target theorems \\
\bottomrule
\end{tabular}
\caption{Existing SJET anchors for Thread~1. Every row is already in the
manuscript; Thread~1 assembles them under
\texttt{def:thread-1-evaluator}.}
\label{tab:thread-1-anchors}
\end{table}

\paragraph{Gap analysis.}
Thread~1 has a \textbf{conceptual} descent map (Section~\ref{sec:emergent:map})
but lacks three certificates required for physics-map parity with
Class~II--IV rows:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Evaluator.} No definition
    $\mathcal{F}_{\mathrm{emergent}}$ appears in
    \eqref{eq:physics-map-pipeline}; Class~V cites
    $\mathrm{eval}_{\mathrm{emergent}}$ only in prose
    (Section~\ref{sec:physics-map:grouping}).
  \item \textbf{Continuum functor.} The replica limit
    \eqref{eq:replica-limit} and Bloch connection
    \eqref{eq:bloch-bands} are Tier~B/C; a proof that
    $\mathcal{E}_N$ converges to a unique continuum effective action
    $S_{\mathrm{eff}}^{\mathrm{cont}}$ on soldered $d=4$ geometry
    (Definition~\ref{def:soldering}) is not yet a theorem.
  \item \textbf{Strong-correlation frontier.}
    Remark~\ref{rmk:emergent-honest} explicitly excludes superconductivity,
    fractional quantum Hall, and other strong-correlation phases; overlap-network
    percolation (Definition~\ref{def:flavon-network}) is not yet tied to
    phase-transition exponents.
  \item \textbf{Quantitative contacts.} Noble-gas closures, Landau parameter
    \eqref{eq:landau-F0}, and free-energy identities are leading-order;
    atomic spectroscopy and quantitative band gaps remain Tier~C imports.
\end{enumerate}
Removing ledger entries \textbf{A5} (flavon truncation) or \textbf{A7} (OS
reconstruction) invalidates subchains but does not affect the void--mirror
climb; Thread~1 upgrades \emph{emergent} rows to explicit
$\mathcal{F}_{\mathrm{emergent}}$ output without adding primitives.

\paragraph{Wave~2 partial closure (Thread~1).}
The first Class~V domain evaluator, descent factorization for chemistry and
atomic rows, and periodic-tower continuum functor are certified in
Section~\ref{sec:wave2-thread1}
(Definition~\ref{def:thread-1-evaluator},
Theorem~\ref{thm:thread-1-descent},
Definition~\ref{def:thread-1-continuum};
Corollary~\ref{cor:thread-1-wave2-partial}).
Residual Thread~1 items---quantitative band gaps, critical exponents,
strong-correlation phases, and full Class~V closure---remain for later waves;
see Remark~\ref{rmk:thread1-wave2-table}.

\paragraph{Target evaluators and theorems.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}llp{0.44\linewidth}@{}}
\toprule
\textbf{Functor / label} & \textbf{Tier target} & \textbf{Proposed content} \\
\midrule
$\mathcal{F}_{\mathrm{emergent}}$ &
  B $\to$ A &
  \texttt{def:thread-1-evaluator}: assemble
  $\mathcal{E}_N$, $G_Z$, $d\nu_\beta$ on $\mathcal{T}_7$ \\
$\mathcal{F}_{\mathrm{descent}}$ &
  B &
  \texttt{thm:thread-1-descent}: factorization
  $\mathcal{F}_{\mathrm{emergent}}=
  \mathrm{coarse}\circ\mathcal{E}_N\circ\mathrm{eval}_{\mathrm{SM}}$ \\
$\mathcal{F}_{\mathrm{band}}$ &
  B/C &
  \texttt{thm:thread-1-bands}: $\det(\mathcal{D}_{\mathbf{k}})$ contact
  for band gaps \\
$\mathcal{F}_{\mathrm{thermo}}$ &
  B &
  \texttt{thm:thread-1-critical}: capacity-weighted critical exponents
  from \eqref{eq:Z-sigma} \\
$\mathcal{F}_{\mathrm{continuum}}$ &
  B &
  \texttt{def:thread-1-continuum}: $L\to\infty$ limit of cellular cosheaf
  $\mathcal{F}_{16}$ \\
--- &
  B/C &
  \texttt{cor:thread-1-closure}: Class~V physics-map rows certified
  under \texttt{def:thread-1-evaluator} \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Dependency edges.}
\begin{itemize}[leftmargin=*]
  \item \textbf{Upstream (required).}
    Observer collapse $\Pi_{\sigma=-1}$
    (Definition~\ref{def:heterotic-collapse});
    OS quantum mechanics (Theorem~\ref{thm:qm-derived});
    SM breaking chain (Theorem~\ref{thm:breaking-complete});
    $\sigma$-measure split (Theorem~\ref{thm:sigma-measure}).
  \item \textbf{Peer threads.}
    Thread~2 (weak): induced gravity supplies the background vierbein
    (Proposition~\ref{prop:vierbein}) for continuum limits;
    environmental pressure $\mathcal{P}_{\sigma=+1}$
    (Definition~\ref{def:env-pressure}) enters thermodynamic
    \eqref{eq:thermo-laws}.
    Nuclear/atomic contact (Section~\ref{sec:nuclear-atomic-cosmo}) is a
    \emph{specialization} of Thread~1 at low $N$.
  \item \textbf{Downstream (feeds).}
    Biophysics and plasma rows in Table~\ref{tab:physics-map-complete};
    precision chemistry and materials Tier~C workbook.
\end{itemize}

\paragraph{Proof-tier upgrade path ($\mathbf{E}\to\mathbf{B}\to\mathbf{A}$).}
\begin{enumerate}[label=\textbf{\arabic*.},leftmargin=*]
  \item \textbf{Tier~E (emergent contact).}
    Current Class~V status: SM\,+\,GR\,+\,QED effective theory with no
    named $\mathcal{F}_D$ (Section~\ref{sec:physics-map:grouping},
    Remark~\ref{rmk:emergent-honest}).
  \item \textbf{Tier~B (ledger-conditional).}
    Close \texttt{def:thread-1-evaluator} and
    \texttt{thm:thread-1-descent} under \textbf{A5} (flavon overlap),
    \textbf{A7} (OS reconstruction for $\mathcal{H}_N^{\mathrm{em}}$),
    and \textbf{A8} (environmental pressure routing); matches
    Section~\ref{sec:emergent} tier assignments.
  \item \textbf{Tier~A (void--mirror).}
    Upgrade additivity and locality of $\mathcal{E}_N$
    (Proposition~\ref{prop:emergent-functor}) to a \emph{unique} descent
    functor from $H^1(\mathcal{T}_7,\mathcal{F}_{16})^{\sigma=-1}$ alone,
    eliminating \textbf{A5} from the chemistry ladder
    (Theorem~\ref{thm:chemistry-ladder}) and identifying the replica limit
    with Stone-lift cellular data (Proposition~\ref{prop:stone-lift}) without
    emergent lattice identification.
\end{enumerate}

\begin{equation}\label{eq:thread-1-pipeline}
  \boxed{%
  \begin{aligned}
    \mathcal{F}_{\mathrm{emergent}}(D)
    \;&=\;
    \mathrm{coarse}_{\beta,N,L}\circ
    \mathcal{E}_N\circ
    \Pi_{\sigma=-1}\circ
    \mathrm{Bal}_{\mathcal{C}}\circ
    \Mirror^{\leq 8}(\Void),\\[4pt]
    \mathcal{E}_N
    \;&=\;
    (\Pi_{\sigma=-1})^{\otimes N},
    \qquad
    \mathcal{H}_N^{\mathrm{em}}=\mathrm{Im}(\mathcal{E}_N)
    \subset
    \mathcal{H}_{\mathrm{obs}}^{\otimes N}.
  \end{aligned}}
\end{equation}

%----------------------------------------------------------------------%
\subsection{Thread~2: Strong-curvature and quantum gravity}
\label{sec:thread-2}
%----------------------------------------------------------------------%

\paragraph{Thread definition.}
\textbf{Thread~2} is the \emph{strong-curvature} route: beyond the
Einstein--Hilbert ledger truncation (\textbf{A1}), where the effective
coupling $\kappa(k)=k^2/\MPl^2(k)$ (Definition~\ref{def:kappa}) reaches the
UV organizing fixed point $\kappa_\star=96\pi^2/5$
(Theorem~\ref{thm:kappa}) and induced $\MPl$ is anchored to the electroweak
scale via Sakharov $a_2$ (Theorem~\ref{thm:planck},
Proposition~\ref{prop:planck-scale}). At curvature scales $R\sim\MPl^2$ and on
black-hole horizons (Table~\ref{tab:physics-map-complete}, astrophysics row),
the one-loop EH truncation is insufficient; Thread~2 traces how
\emph{higher-curvature} and \emph{graviton} modes are routed to the
$\sigma=+1$ shadow sector (Theorem~\ref{thm:kappa-persistence},
assumption~\textbf{A8}), how dark-matter cohomology residue
$\mathcal{R}_{+1}$ (Definition~\ref{def:dm-residue}) gravitates at
$\kappa_\star$, and how the nonperturbative measure split
\eqref{eq:gamma-split} constrains a horizon EFT \emph{without} importing a
separate quantum-gravity axiom. The target is a named evaluator
$\mathcal{F}_{\mathrm{grav}}$ certifying Planck-scale and horizon physics as
outputs of the same void--mirror pipeline.

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.10}
\begin{tabular}{@{}clp{0.52\linewidth}@{}}
\toprule
\textbf{ID} & \textbf{Prior catalog question} & \textbf{Thread~2 closure target} \\
\midrule
QG-EH &
  Einstein--Hilbert sufficiency at $R\sim\MPl^2$ &
  \textbf{A1} truncation $\to$
  \texttt{thm:thread-2-curvature} (EH domain of validity) \\
QG-R2 &
  $R^2$, graviton loops, higher curvature &
  Theorem~\ref{thm:kappa-persistence} $\to$
  \texttt{prop:thread-2-shadow-routing} (full Jacobian certificate) \\
QG-PL &
  Absolute Planck mass identification &
  Theorem~\ref{thm:planck}, \eqref{eq:planck-v} $\to$
  \texttt{cor:thread-2-planck} (D3 closure at $\kappa_\star$) \\
QG-BH &
  Black-hole horizons, entropy &
  Physics-map Tier~B/C row $\to$
  \texttt{thm:thread-2-horizon} (observer-local horizon EFT) \\
QG-NP &
  Nonperturbative quantum gravity &
  Theorem~\ref{thm:sigma-measure} $\to$
  \texttt{thm:thread-2-qg} (shadow-sector gravitational measure) \\
QG-DM &
  Shadow-sector stress at strong curvature &
  Theorem~\ref{thm:dm-sector} $\to$
  \texttt{prop:thread-2-shadow-stress} ($T_{\mu\nu}^{(+1)}$ at horizon) \\
QG-CC &
  Vacuum energy back-reaction under curvature &
  Theorem~\ref{thm:cc-sequester} $\to$
  \texttt{lem:thread-2-a0-horizon} ($a_0$ density on horizons) \\
QG-EVAL &
  No $\mathcal{F}_D$ for black-hole / Planck rows &
  \texttt{def:thread-2-evaluator} certifies
  $\mathcal{F}_{\mathrm{grav}}$ \\
\bottomrule
\end{tabular}
\caption{Unanswered questions from the gravity and astrophysics rows of
Table~\ref{tab:physics-map-complete} and the strong-curvature frontier beyond
\textbf{A1}. Rows do not reopen CC row~\textbf{CC} of
Table~\ref{tab:gap-ledger} (already derived).}
\label{tab:thread-2-questions}
\end{table}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}llp{0.46\linewidth}@{}}
\toprule
\textbf{Label} & \textbf{Object} & \textbf{Role in Thread~2} \\
\midrule
\ref{thm:planck} &
  Sakharov $\MPl^2$ from $28$ coset scalars &
  Induced Planck mass $a_2$ truncation \\
\ref{def:kappa} &
  $\kappa(k)=k^2/\MPl^2(k)$ &
  Dimensionless gravitational coupling \\
\ref{thm:kappa} &
  $\kappa_\star=96\pi^2/5$, $\beta_\kappa$ &
  One-loop UV fixed point on EH truncation \\
\ref{thm:kappa-persistence} &
  $R^2$/graviton decoupling on observable row &
  Strong-curvature modes routed to $d\mu_{\Gamma_{+1}}$ \\
\ref{prop:frg-jacobian} &
  Extended FRG stability matrix &
  Relevant directions $\kappa$, $\Lambda_{\mathrm{cc}}$ \\
\ref{thm:cc-sequester} &
  $\Lambda_{\mathrm{cc}}=\Pi_{\sigma=+1}\Lambda_{\mathrm{cc}}$ &
  Vacuum energy sequestering at $\kappa_\star$ \\
\ref{lem:a0-sigma-plus} &
  $a_0^{(\pm1)}$ heat-kernel split &
  Curvature--vacuum coupling graded by $\sigma$ \\
\ref{thm:sigma-measure} &
  $d\mu_\Gamma=d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}}$ &
  Nonperturbative sector factorization \\
\ref{thm:dm-sector} &
  $\rho_{\mathrm{DM}}=\langle T_{00}^{(+1)}\rangle_{\mathcal{R}_{+1}}$ &
  Shadow stress sources curvature \\
\ref{def:dm-freezeout} &
  $k_{\mathrm{FO}}=\kappa_\star^{1/2}v$ &
  Organizing scale for gravitational freeze-out \\
\ref{prop:vierbein} &
  Composite vierbein on $\mathfrak{m}$ &
  Strong-field metric from coset section \\
\ref{thm:spacetime:soldering-derived} &
  $d=4$ Lorentzian block $H_2(\Quat)$ &
  Horizon geometry transport \\
\ref{rmk:observer-frg} &
  Observer-local FRG along $g_\iota$ &
  Strong-curvature flow chart \\
\bottomrule
\end{tabular}
\caption{Existing SJET anchors for Thread~2. The EH chain and
$\sigma$-routing lemmas supply the backbone; horizon and nonperturbative
certificates are the Thread~2 target layer.}
\label{tab:thread-2-anchors}
\end{table}

\paragraph{Gap analysis.}
Thread~2 has \textbf{Tier~B} control of $\kappa_\star$ on the observable FRG
row but lacks closed strong-curvature theorems:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Evaluator.} Black holes appear as
    \emph{Emergent: induced gravity + Tier~B horizon EFT}
    (Table~\ref{tab:physics-map-complete}) with no
    $\mathcal{F}_{\mathrm{grav}}$ definition parallel to
    $\mathcal{F}_{\sigma\mathrm{-split}}$ for cosmology.
  \item \textbf{Horizon certificate.} No theorem identifies observer horizon
    data with $\Pi_{\sigma=-1}$-projected boundary modes on
    $\hat Q$; the Tier~B horizon EFT is named but not derived.
  \item \textbf{Nonperturbative QG.} Theorem~\ref{thm:kappa} is explicitly
    one-loop with higher curvature neglected
    (Section~\ref{sec:physics:gauge}); a nonperturbative fixed-point
    statement for the full gravitational measure on
    $d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}}$ is not proved.
  \item \textbf{Strong-field $\sigma$ routing.} Theorem~\ref{thm:kappa-persistence}
    treats $R^2$ and graviton loops at the fixed point; explicit strong-curvature
    propagation of $T_{\mu\nu}^{(+1)}$ near horizons is not separated from
    the cosmological shadow residue of Theorem~\ref{thm:dm-sector}.
  \item \textbf{Quantitative contacts.} Planck mass \eqref{eq:planck-v} is
    Tier~B/C (Proposition~\ref{prop:planck-scale}); Bekenstein--Hawking
    entropy and quasi-normal spectra are not in the contact layer.
\end{enumerate}
Thread~2 closes these gaps within the existing ledger
(\textbf{A1},~\textbf{A2},~\textbf{A4},~\textbf{A8}); no new gravitational
primitive is introduced.

\paragraph{Target evaluators and theorems.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}llp{0.44\linewidth}@{}}
\toprule
\textbf{Functor / label} & \textbf{Tier target} & \textbf{Proposed content} \\
\midrule
$\mathcal{F}_{\mathrm{grav}}$ &
  B $\to$ A &
  \texttt{def:thread-2-evaluator}: assemble $\kappa$, $\MPl$,
  $\Gamma_{\mathrm{eff}}$ at $\kappa_\star$ \\
$\mathcal{F}_{\kappa}$ &
  B &
  \texttt{cor:thread-2-kappa}: persistence of $\kappa_\star$ under
  \textbf{A8} extended truncation \\
$\mathcal{F}_{\mathrm{horizon}}$ &
  B/C &
  \texttt{thm:thread-2-horizon}: observer-local horizon EFT from
  $\sigma_{\mathrm{sol}}$ and $d\mu_{\Gamma_{-1}}$ \\
$\mathcal{F}_{\mathrm{shadow}}$ &
  B &
  \texttt{prop:thread-2-shadow-stress}: $T_{\mu\nu}^{(+1)}$ sourcing
  strong-field Einstein equations \\
$\mathcal{F}_{\mathrm{np}}$ &
  B &
  \texttt{thm:thread-2-qg}: nonperturbative gravitational measure on
  \eqref{eq:gamma-split} \\
--- &
  B/C &
  \texttt{lem:thread-2-a0-horizon}: $a_0^{(+1)}$ on horizon shells;
  \texttt{cor:thread-2-closure} for astrophysics rows \\
\bottomrule
\end{tabular}
\end{center}

\paragraph{Dependency edges.}
\begin{itemize}[leftmargin=*]
  \item \textbf{Upstream (required).}
    Induced gravity (\textbf{A1}, Theorem~\ref{thm:kappa});
    Sakharov scale (\textbf{A2}, Theorem~\ref{thm:planck});
    D3 scale identification (Section~\ref{sec:scales},
    Proposition~\ref{prop:planck-scale});
    $\sigma$-measure split (Theorem~\ref{thm:sigma-measure});
    soldering (Theorem~\ref{thm:spacetime:soldering-derived}).
  \item \textbf{Peer threads.}
    Thread~1 (weak): emergent continuum limits use the vierbein
    (Proposition~\ref{prop:vierbein}) and pressure conjugate
    $\mathcal{P}_{\sigma=+1}$.
    Dark-sector thread (Section~\ref{sec:dark-sector}): $\mathcal{R}_{+1}$
    and freeze-out (Definition~\ref{def:dm-freezeout}) supply shadow
    stress; cosmology thread (Section~\ref{sec:cosmology}): CC sequestering
    sets the de~Sitter background for horizon EFT.
    Quantum-origin thread (Section~\ref{sec:quantum-origin}): OS reconstruction
    constrains the observable gravitational measure.
  \item \textbf{Downstream (feeds).}
    Black-hole and strong-field astrophysics rows;
    early-universe curvature corrections beyond
    Coleman--Weinberg gap (\textbf{A3});
    precision $\MPl$ workbook (Appendix~\ref{sec:appendix:frg}).
\end{itemize}

\paragraph{Proof-tier upgrade path ($\mathbf{E}\to\mathbf{B}\to\mathbf{A}$).}
\begin{enumerate}[label=\textbf{\arabic*.},leftmargin=*]
  \item \textbf{Tier~E (emergent contact).}
    Current black-hole row: induced gravity + unspecified horizon EFT
    (Table~\ref{tab:physics-map-complete}); Tier~B/C contact only.
  \item \textbf{Tier~B (ledger-conditional).}
    Close \texttt{def:thread-2-evaluator},
    \texttt{thm:thread-2-horizon}, and
    \texttt{thm:thread-2-qg} under \textbf{A1}--\textbf{A2},
    \textbf{A4}, \textbf{A8}; extend Theorem~\ref{thm:kappa-persistence}
    to strong-field charts $(\tau_\iota,g_\iota)$ along
    Definition~\ref{def:lifetime}.
  \item \textbf{Tier~A (void--mirror).}
    Derive the observer-local EH truncation (\textbf{A1}) from
    $\sigma$-equivariance of \eqref{eq:action} and capacity balance on
    $\mathfrak{m}$ without FRG ledger import; identify
    $\kappa_\star$ as a consequence of the $28|4$ coset split
    (Lemma~\ref{lem:goldstone-sigma}) and anomaly arithmetic
    (Theorem~\ref{thm:beta}) alone; upgrade shadow routing to
    Theorem~\ref{thm:duality} without \textbf{A8} decoupling hypothesis.
\end{enumerate}

\begin{equation}\label{eq:thread-2-pipeline}
  \boxed{%
  \begin{aligned}
    \mathcal{F}_{\mathrm{grav}}(D)
    \;&=\;
    \mathrm{eval}_{\kappa}\circ
    \Pi_{\sigma=-1}\circ
    \mathrm{Bal}_{\mathcal{C}}\circ
    \Mirror^{\leq 8}(\Void),\\[4pt]
    \mathrm{eval}_{\kappa}
    \;&:\;
    (\MPl,\kappa_\star,\Gamma_{\mathrm{eff}})
    \longmapsto
    \mathcal{M}_{\mathrm{strong}}(D),
    \qquad
    \beta_\kappa\big|_{\sigma=-1,\,\kappa_\star}=0,\\[2pt]
    \beta_{\alpha R^2},\,
    \beta_{\mathrm{graviton}}
    \;&\subset\;
    d\mu_{\Gamma_{+1}}
    \quad
    (\textbf{A8},\ \text{Thm.~\ref{thm:kappa-persistence}}).
  \end{aligned}}
\end{equation}

\begin{remark}[Thread coupling]
\label{rmk:threads-1-2-coupling}
Threads~1 and~2 are logically orthogonal: Thread~1 coarse-grains
$\Pi_{\sigma=-1}$ matter on $\mathcal{T}_7$; Thread~2 organizes
curvature couplings at $\kappa_\star$ and routes strong-field back-reaction
to $d\mu_{\Gamma_{+1}}$. Their intersection is the thermodynamic pressure
term $\mathcal{P}_{\sigma=+1}$ in \eqref{eq:thermo-laws} and the vierbein
(Proposition~\ref{prop:vierbein}) shared by condensed-matter continuum
limits and horizon geometry. Neither thread adds a primitive axiom; both
extend Corollary~\ref{cor:physics-map-closure} with named evaluators
$\mathcal{F}_{\mathrm{emergent}}$ and $\mathcal{F}_{\mathrm{grav}}$.
\end{remark}