%======================================================================%
\section{Research Threads III--IV: Continuum Rigor and Precision Contact}
\label{sec:threads-3-4}
%======================================================================%

Sections~\ref{sec:derivation-complete}--\ref{sec:physics-map} close semantic
coverage of the PDG-aligned physics map. Two \emph{research threads} remain
as explicit programme coordinates: \textbf{Thread~3} (constructive continuum
limit and nonperturbative rigor) and \textbf{Thread~4} (precision and anomaly
contact). This section traces both threads through the same master pipeline
\eqref{eq:master-pipeline}, records open questions in tabular form, names
existing anchors and residual gaps, and states target theorem upgrades with
tier labels and dependency chains. Threads~III and~IV are not new primitives;
they are audit trails for the rigor and precision layers that connect cellular
mirror data to OS quantum mechanics (Thread~3) and to sub-percent PDG contacts
(Thread~4).

%======================================================================%
\subsection{Thread~3: Constructive continuum limit and rigor}
\label{sec:thread-3}
%======================================================================%

\begin{definition}[Thread~3: constructive continuum limit]
\label{def:thread-3}
\emph{Thread~3} is the functorial chain that transports discrete mirror data
on the stabilized Albert tower $\mathcal{T}_7$ to a nonperturbatively
well-defined observer-sector Euclidean measure, then to Lorentzian quantum
mechanics by OS reconstruction. Its pipeline stages are:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Cellular cohomology} on $\mathcal{T}_7$ with cosheaf
    $\mathcal{F}_{16}$ (Definition~\ref{def:tower7},
    Definition~\ref{def:F16}, Lemma~\ref{lem:cellular}).
  \item \textbf{Profinite Stone lift} to $Q$ with $\sigma$-type stability
    (Proposition~\ref{prop:stone-lift}, Appendix~\ref{sec:appendix:quotient}).
  \item \textbf{Mirror quotient} $\hat Q=Q/\sigma$ and bundle $V_{16}\to\hat Q$
    (Definition~\ref{def:Qhat}, Theorem~\ref{thm:observer-fp}).
  \item \textbf{Radiative mass gap} on the $28$ observer-sector coset
    directions (Theorem~\ref{thm:rp}, assumption~\textbf{A3}).
  \item \textbf{$\sigma$-loop expansion} of the Euclidean measure
    (Theorem~\ref{thm:sigma-measure}, Lemma~\ref{lem:goldstone-sigma}).
  \item \textbf{OS upgrade} from semiclassical reflection positivity to full
    observer-sector reconstruction (Theorems~\ref{thm:rp-gamma-neg},
    \ref{thm:rp-complete}, Proposition~\ref{prop:os-observer},
    Theorem~\ref{thm:qm-derived}).
\end{enumerate}
Thread~3 closes former gap \textbf{P5} (nonperturbative reflection positivity)
and supplies the constructive backbone for Section~\ref{sec:quantum-origin}.
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.14}
\begin{tabular}{@{}clp{0.46\linewidth}c@{}}
\toprule
\textbf{ID} & \textbf{Question} & \textbf{Resolution status} & \textbf{Tier} \\
\midrule
T3-Q1 &
  Does $\dim H^1(\mathcal{T}_7,\mathcal{F}_{16})^{\sigma=-1}=3$
  survive the Stone lift to $Q$? &
  \textbf{Closed} --- Proposition~\ref{prop:stone-lift},
  Theorem~\ref{thm:mirror-index} &
  A \\
T3-Q2 &
  Is the observable coset sector radiatively gapped? &
  \textbf{Closed} --- Theorem~\ref{thm:rp} ($\mu^2>0$ on $28$ modes,
  Lemma~\ref{lem:breaking-cw}) &
  B \\
T3-Q3 &
  Do massless Goldstones decouple from $d\mu_{\Gamma_{-1}}$? &
  \textbf{Closed} --- Lemma~\ref{lem:goldstone-sigma},
  $4$ modes in $\mathfrak{m}_{+1}\subset d\mu_{\Gamma_{+1}}$ &
  B \\
T3-Q4 &
  Does $d\mu_\Gamma$ factorize as
  $d\mu_{\Gamma_{-1}}\otimes d\mu_{\Gamma_{+1}}$? &
  \textbf{Closed} --- Theorem~\ref{thm:sigma-measure} &
  B \\
T3-Q5 &
  Is $d\mu_{\Gamma_{-1}}$ reflection-positive along $\tau_\iota$? &
  \textbf{Closed} --- Theorem~\ref{thm:rp-gamma-neg} &
  B \\
T3-Q6 &
  Do OS axioms reconstruct unitary QFT on $\mathcal{H}_{\mathrm{obs}}$? &
  \textbf{Closed under \textbf{A7}} ---
  Proposition~\ref{prop:os-observer},
  Theorem~\ref{thm:qm-derived} &
  B \\
T3-Q7 &
  Do $\sigma$-sector loop corrections remain factorized at all orders? &
  \textbf{Partial} --- tree and one-loop split proved;
  all-orders target \ref{thm:thread3-sigma-loop} &
  B$\to$A? \\
T3-Q8 &
  Is there a lattice error bound
  $\|H^1(\mathcal{T}_7)-H^1(Q)\|<\varepsilon$? &
  \textbf{Open} --- profinite stability shown;
  explicit $\varepsilon$ bound target \ref{thm:thread3-continuum} &
  --- \\
T3-Q9 &
  Does the gauge sector inherit a nonperturbative mass gap (YM)? &
  \textbf{Open} --- semiclassical gap on coset;
  confinement contact Tier~C (Theorem~\ref{thm:confinement}) &
  C \\
\bottomrule
\end{tabular}
\caption{Thread~3 question ledger. \textbf{Closed} entries are proved in the
manuscript; \textbf{Partial} and \textbf{Open} entries name target upgrades
below.}
\label{tab:thread-3-questions}
\end{table}

\paragraph{Existing anchors.}
Thread~3 is already threaded through the manuscript at the following nodes:
\begin{itemize}[leftmargin=*]
  \item \textbf{Cellular $\to$ continuum.}
    Appendix~\ref{sec:appendix:quotient}: triality on $\mathcal{T}_7$
    (Proposition~\ref{prop:triality}), cellular count
    (Lemma~\ref{lem:cellular}), Stone lift
    (Proposition~\ref{prop:stone-lift}), Lefschetz index
    (Theorem~\ref{thm:mirror-index}).
  \item \textbf{Quotient geometry.}
    Definition~\ref{def:Qhat}; observer fixed-point theorem
    (Theorem~\ref{thm:observer-fp}); duality
    (Theorem~\ref{thm:duality}).
  \item \textbf{Mass gap.}
    Coleman--Weinberg gap (Lemma~\ref{lem:breaking-cw}, assumption~\textbf{A3});
    semiclassical RP (Theorem~\ref{thm:rp}); Goldstone split
    (Lemma~\ref{lem:goldstone-sigma}).
  \item \textbf{$\sigma$-measure and loops.}
    Nonperturbative factorization (Theorem~\ref{thm:sigma-measure});
    instanton split parallel (Proposition~\ref{prop:theta-measure});
    graviton/$R^2$ routing (assumption~\textbf{A8},
    Theorem~\ref{thm:kappa-persistence}).
  \item \textbf{OS chain.}
    RP on $d\mu_{\Gamma_{-1}}$ (Theorem~\ref{thm:rp-gamma-neg});
    closure (Theorem~\ref{thm:rp-complete});
    quantum origin (Theorem~\ref{thm:qm-derived},
    Corollary~\ref{cor:qm-origin-closure}).
\end{itemize}

\paragraph{Residual gaps.}
\begin{enumerate}[label=\textbf{G3.\arabic*},leftmargin=*]
  \item \label{gap:thread3-continuum}
    \textbf{Quantitative continuum limit.} Proposition~\ref{prop:stone-lift}
    proves dimensional stability of $H^1$ under profinite refinement; an
    explicit operator-norm bound between cellular and continuum Laplacians on
    $\hat Q$ is not yet recorded.
  \item \label{gap:thread3-sigma-loop}
    \textbf{All-orders $\sigma$-loop expansion.} The tree-level factorization
    \eqref{eq:gamma-split} and one-loop Jacobian block
    (Appendix~\ref{sec:appendix:frg}) are proved; a uniform bound on
    cross-sector loop insertions at order $L\ge 2$ remains a programme item.
  \item \label{gap:thread3-gauge-gap}
    \textbf{Nonperturbative gauge mass gap.} Theorem~\ref{thm:confinement}
    supplies a Tier~C area-law contact; a constructive OS proof for
    $\mathrm{SU}(3)_c$ on $\hat Q$ parallel to Theorem~\ref{thm:rp-complete}
    is not closed.
  \item \label{gap:thread3-a7}
    \textbf{Ledger \textbf{A7} minimization.} Clustering and Euclidean
    symmetry for $d\mu_{\Gamma_{-1}}$ are recorded as a derived truncation
    (Definition~\ref{def:assumption-ledger}, item~\ref{asm:os}); deriving
    \textbf{A7} from void and mirror alone would promote Thread~3 to Tier~A.
\end{enumerate}

\paragraph{Target theorems.}
\begin{theorem}[Target: quantitative continuum limit]
\label{thm:thread3-continuum}
\textbf{Target (Thread~3).} Let $\mathcal{T}_7^{(n)}$ be a profinite refinement
of the stabilized Albert tower and $Q^{(n)}$ its Stone lift. There exists
$\varepsilon_n\to 0$ such that the $\sigma$-anti-invariant cellular Laplacian
$\Delta_{\mathcal{T}_7^{(n)}}$ on $H^1(\mathcal{T}_7^{(n)},\mathcal{F}_{16})$
converges in operator norm to the Laplacian on
$H^1(Q,V_{16})^{\sigma=-1}$, and the observer count
$\dim H^1=3$ is stable for all $n$. \textbf{Upgrade:} Lemma~\ref{lem:cellular}
$\to$ Tier~A continuum stability; closes \ref{gap:thread3-continuum}.
\end{theorem}

\begin{theorem}[Target: mass gap certificate on observer coset]
\label{thm:thread3-mass-gap}
\textbf{Target (Thread~3).} Under assumption~\textbf{A3} and
$\iota$-sector convexity~\textbf{A6}, the Euclidean measure on the
$28$-dimensional complement of $\mathfrak{m}_{+1}$ satisfies an OS mass gap
$\Delta_\iota\ge c\,\mu>0$ uniform in $\iota\in\mathcal{I}$, with
$\mu^2$ the Coleman--Weinberg scale of Lemma~\ref{lem:breaking-cw}.
\textbf{Status:} semiclassical content in Theorem~\ref{thm:rp};
\textbf{upgrade:} promote to nonperturbative gap alongside
Theorem~\ref{thm:rp-complete}.
\end{theorem}

\begin{theorem}[Target: $\sigma$-loop expansion]
\label{thm:thread3-sigma-loop}
\textbf{Target (Thread~3).} For the Euclidean measure
$d\mu_\Gamma[\orderparam,A]$ of \eqref{eq:gamma-full}, the loop expansion
factorizes order-by-order:
\begin{equation}\label{eq:sigma-loop-expansion}
  \log Z_\Gamma
  \;=\;
  \log Z_{\Gamma_{-1}}
  \;+\;
  \log Z_{\Gamma_{+1}},
\end{equation}
with no mixed $\sigma=\pm1$ cross-terms at any loop order, provided
higher-curvature and graviton loops are routed to the $\sigma=+1$ sector per
assumption~\textbf{A8}. \textbf{Status:} tree (Theorem~\ref{thm:sigma-measure})
and one-loop FRG block (Proposition~\ref{prop:frg-jacobian});
\textbf{upgrade:} close \ref{gap:thread3-sigma-loop} and promote
\textbf{A8} back-reaction bounds to a lemma.
\end{theorem}

\begin{theorem}[Target: OS upgrade]
\label{thm:thread3-os-upgrade}
\textbf{Target (Thread~3).} Derive assumption~\textbf{A7} (clustering and
Euclidean invariance for $d\mu_{\Gamma_{-1}}$) from product-mirror
equivariance and compactness on EIII, so that
Proposition~\ref{prop:os-observer} and Theorem~\ref{thm:qm-derived} become
Tier~A consequences of void and mirror. \textbf{Status:} Tier~B under
\textbf{A7}; \textbf{upgrade:} close \ref{gap:thread3-a7}; former P5 becomes
Tier~A.
\end{theorem}

\paragraph{Dependencies and tier upgrades.}
Thread~3 depends on Tier~A inputs (void, mirror, cellular count, triality,
Stone lift) and Tier~B ledger entries \textbf{A3} (Coleman--Weinberg gap),
\textbf{A6} ($\iota$-convexity), \textbf{A7} (OS axioms), and \textbf{A8}
($\sigma$-routed gravity loops). The dependency DAG is
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Input} & \textbf{Thread~3 output} \\
\midrule
Lemma~\ref{lem:cellular}, Proposition~\ref{prop:stone-lift} &
  Continuum observer multiplicity \\
Lemma~\ref{lem:breaking-cw}, Theorem~\ref{thm:rp} &
  Coset mass gap \\
Theorem~\ref{thm:sigma-measure}, Lemma~\ref{lem:goldstone-sigma} &
  $\sigma$-loop factorization (tree) \\
Theorem~\ref{thm:rp-gamma-neg}, Proposition~\ref{prop:os-observer} &
  OS reconstruction \\
Theorem~\ref{thm:qm-derived} &
  Quantum mechanics certificate \\
\bottomrule
\end{tabular}
\end{center}
\textbf{Tier upgrades sought:} \textbf{A7}$\to$\textbf{derived}
(Theorem~\ref{thm:thread3-os-upgrade}); cellular stability
$\to$ quantitative bound (Theorem~\ref{thm:thread3-continuum}); P5
(Table~\ref{tab:gap-ledger}) from Tier~B to Tier~A.

\begin{equation}\label{eq:thread3-pipeline}
  \boxed{%
  \mathcal{T}_7
  \;\xrightarrow{\;\text{Stone}\;}\;
  Q
  \;\xrightarrow{\;/\sigma\;}\;
  \hat Q
  \;\xrightarrow{\;\Pi_{\sigma=-1},\,\mu^2>0\;}\;
  d\mu_{\Gamma_{-1}}
  \;\xrightarrow{\;\text{OS}\;}\;
  \mathcal{H}_{\mathrm{obs}}
  }
\end{equation}
Equation~\eqref{eq:thread3-pipeline} is the Thread~3 specialization of
\eqref{eq:master-pipeline} to the rigor layer; Section~\ref{sec:quantum-origin}
records the OS endpoint (Corollary~\ref{cor:qm-origin-closure}).

%======================================================================%
\subsection{Thread~4: Precision and anomaly contact}
\label{sec:thread-4}
%======================================================================%

\begin{definition}[Thread~4: precision and anomaly contact]
\label{def:thread-4}
\emph{Thread~4} is the experimental contact thread: Tier~A anomaly arithmetic
and $\beta$-function identities propagate through the ledger FRG and two-loop
threshold matching to sub-percent PDG observables, CP-odd invariants, and
hadronic residues. Its stages are:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Anomaly anchor.} Cubic and mixed anomaly cancellation
    (Theorem~\ref{thm:anomaly}); $b_0=12$ from $\mathbf{27}$ content
    (Theorem~\ref{thm:beta}).
  \item \textbf{Ledger FRG.} Extended Jacobian
    (Proposition~\ref{prop:frg-jacobian}, Appendix~\ref{sec:appendix:frg});
    capacity residues $\mathcal{R}_\iota(\mu)$ on observer charts.
  \item \textbf{Two-loop thresholds.} Flavon, Yukawa, electroweak, and QCD
    refinements (Theorems~\ref{thm:nu-ratio-2loop},
    \ref{thm:quark-mass-2loop}, Theorem~\ref{thm:g2-2loop}).
  \item \textbf{Precision closure.} Definition~\ref{def:tier-c-closure};
    Corollaries~\ref{cor:tier-c-closure},~\ref{cor:quark-tier-c}.
  \item \textbf{CP phases.} CKM $(\rho,\eta)$ from $\mathcal{P}_{ij}$
    (Proposition~\ref{prop:ckm-precision}); strong CP
    (Theorem~\ref{thm:strong-cp}); baryogenesis
    (Proposition~\ref{prop:flavon-cp}).
\end{enumerate}
Thread~4 closes the D1--D3 precision programme and extends semantic closure
(Corollary~\ref{cor:semantic-closure}) to quark and hadron sectors.
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.14}
\begin{tabular}{@{}clp{0.44\linewidth}c@{}}
\toprule
\textbf{ID} & \textbf{Question} & \textbf{Resolution status} & \textbf{Tier} \\
\midrule
T4-Q1 &
  Is $b_0=12$ consistent with PDG three-family SM? &
  \textbf{Closed} --- Theorem~\ref{thm:beta}, Table~\ref{tab:predictions-T1} &
  A \\
T4-Q2 &
  Is the mixed GS coefficient $-1$ (one family) stable? &
  \textbf{Closed} --- Theorem~\ref{thm:anomaly} &
  A \\
T4-Q3 &
  Does $\Delta m^2_{31}/\Delta m^2_{21}$ match PDG at $<1\%$? &
  \textbf{Closed} --- Theorem~\ref{thm:nu-ratio-2loop},
  Table~\ref{tab:tier-c-precision} &
  C \\
T4-Q4 &
  Does $m_\mu/m_e$ match pole ratio at $<1\%$? &
  \textbf{Closed} --- Propositions~\ref{prop:lepton-ratio-2loop},
  \ref{prop:lepton-pole} &
  C \\
T4-Q5 &
  Does $\Delta a_\mu^{\mathrm{SJET}}$ match $\delta a_\mu$ at $<1\%$? &
  \textbf{Closed} --- Theorem~\ref{thm:g2-2loop},
  Table~\ref{tab:tier-c-precision} &
  C \\
T4-Q6 &
  Do quark ratios $m_s/m_d$, $m_c/m_s$, $m_t/m_b$ close at $<1\%$? &
  \textbf{Closed} --- Theorem~\ref{thm:quark-mass-2loop},
  Table~\ref{tab:quark-masses} &
  C \\
T4-Q7 &
  Do CKM Wolfenstein $(\lambda,A,\rho,\eta)$ close at $<1\%$? &
  \textbf{Closed} --- Proposition~\ref{prop:ckm-precision},
  Prediction~\ref{pred:ckm-pdg} &
  C \\
T4-Q8 &
  Does $\alpha_s(M_Z)$ close at sub-percent? &
  \textbf{Open} --- Prop.~\ref{prop:alpha-s} $\approx 0.14$ vs.\ PDG
  $0.1179$ ($\sim 15\%$); target \ref{thm:thread4-alpha-s} &
  C \\
T4-Q9 &
  Do hadron masses $m_p$, $m_\pi$, $m_\rho$ close at $<5\%$? &
  \textbf{Partial} --- Prediction~\ref{pred:hadron-masses}
  ($m_p$ $\sim 10\%$, $m_\pi$ match, $m_\rho$ $\sim 13\%$) &
  C \\
T4-Q10 &
  Is strong CP $\bar\theta_{\mathrm{obs}}=0$ consistent with EDM bounds? &
  \textbf{Closed} --- Theorem~\ref{thm:strong-cp},
  Table~\ref{tab:qcd-map} &
  B \\
T4-Q11 &
  Are CP phases $(\rho,\eta,\delta_{\mathrm{flavon}})$ derived without
  tuning? &
  \textbf{Partial} --- CKM from $\mathcal{P}_{ij}$;
  Jarlskog target \ref{thm:thread4-cp-phases} &
  C \\
\bottomrule
\end{tabular}
\caption{Thread~4 question ledger. Headline flavour and electroweak precision
items are \textbf{closed} (Corollary~\ref{cor:tier-c-closure}); QCD and
hadronic rows remain the active precision frontier.}
\label{tab:thread-4-questions}
\end{table}

\paragraph{Existing anchors.}
Thread~4 is anchored at:
\begin{itemize}[leftmargin=*]
  \item \textbf{Tier~A anomaly sector.}
    Theorem~\ref{thm:anomaly} (cubic $16-80+64=0$, mixed $-1$);
    Theorem~\ref{thm:beta} ($b_0=12$);
    Prediction~\ref{pred:gut} ($\alpha_{\mathrm{GUT}}\approx 1/24$).
  \item \textbf{Flavour precision.}
    Section~\ref{sec:tier-c-precision}: $\Delta m^2$ ratio, $m_\mu/m_e$,
    $\Delta a_\mu$, $\sin^2\theta_W(M_Z)$
    (Table~\ref{tab:tier-c-precision},
    Table~\ref{tab:predictions-comparison}).
  \item \textbf{Quark sector.}
    Section~\ref{sec:quark-precision}: Theorem~\ref{thm:quark-mass-2loop},
    Proposition~\ref{prop:ckm-precision}, Prediction~\ref{pred:ckm-pdg};
    workbooks \eqref{eq:workbook-quark-masses}, \eqref{eq:workbook-ckm}.
  \item \textbf{QCD contact.}
    Section~\ref{sec:qcd}: Proposition~\ref{prop:alpha-s},
    Theorem~\ref{thm:confinement}, Prediction~\ref{pred:hadron-masses};
    Table~\ref{tab:qcd-map}.
  \item \textbf{CP sector.}
    Theorem~\ref{thm:strong-cp} ($\theta_{\mathrm{obs}}=0$);
    Proposition~\ref{prop:flavon-cp} ($\varepsilon_{\mathrm{CP}}$);
    Proposition~\ref{prop:ckm-precision} ($\rho$, $\eta$).
  \item \textbf{Validation ledger.}
    Table~\ref{tab:experimental-validation};
    Definition~\ref{def:contact-map};
    Corollary~\ref{cor:tier-c-closure}.
\end{itemize}

\paragraph{Residual gaps.}
\begin{enumerate}[label=\textbf{G4.\arabic*},leftmargin=*]
  \item \label{gap:thread4-alpha-s}
    \textbf{Strong coupling.} One-loop residue \eqref{eq:alpha-s-mz} overshoots
    PDG by $\sim 15\%$; two-loop remark in Section~\ref{sec:qcd:alpha-s} is
    not yet a closed theorem.
  \item \label{gap:thread4-hadrons}
    \textbf{Hadron spectrum.} Cellular overlap programme
    (Definition~\ref{def:hadron-overlap}) gives order-of-magnitude contacts;
    sub-percent proton mass from $\Lambda_{\mathrm{QCD}}$ alone is open.
  \item \label{gap:thread4-Vub}
    \textbf{$|V_{ub}|$ tail.} Table~\ref{tab:ckm-pdg}: $|V_{ub}|$ at $\sim 6\%$
    tolerance, the weakest CKM entry.
  \item \label{gap:thread4-jarlskog}
    \textbf{Jarlskog invariant.} $(\rho,\eta)$ are closed individually; a
    single derived $J_{\mathrm{CKM}}$ from imaginary parts of
    $\mathcal{P}_{ij}$ is not yet recorded.
  \item \label{gap:thread4-anomaly-two-loop}
    \textbf{Two-loop anomaly matching.} Tier~A one-loop identities are exact;
    threshold corrections to $b_0$ and GS coefficients at GUT scales are not
    tabulated.
\end{enumerate}

\paragraph{Target theorems.}
\begin{theorem}[Target: two-loop $\alpha_s(M_Z)$ contact]
\label{thm:thread4-alpha-s}
\textbf{Target (Thread~4).} Extend Proposition~\ref{prop:alpha-s} with
two-loop ledger $\beta$-functions parallel to
Theorem~\ref{thm:quark-mass-2loop}, yielding
$\alpha_s(M_Z)=0.118\pm 0.003$ from $(\alpha_{\mathrm{GUT}},M_{\mathrm{GUT}},
w_3,b_0)$ alone. \textbf{Upgrade:} close \ref{gap:thread4-alpha-s}; promote
QCD row in Table~\ref{tab:qcd-map} from $\sim 15\%$ to $<2\%$.
\end{theorem}

\begin{theorem}[Target: CP phases from overlap phases]
\label{thm:thread4-cp-phases}
\textbf{Target (Thread~4).} Derive the Jarlskog invariant
\begin{equation}\label{eq:jarlskog-target}
  J_{\mathrm{CKM}}
  \;=\;
  A\,\lambda^3\,\eta
  \;\approx\;
  3.0\times 10^{-5}
\end{equation}
and the flavon phase $\delta_3-\delta_1$ of \eqref{eq:flavon-phase} from a
single complex overlap matrix $\mathcal{P}_{ij}\in\mathbb{C}$ with imaginary
parts fixed by oriented triality on $\mathcal{T}_7$
(Proposition~\ref{prop:triality}), with no additional CP postulate.
\textbf{Upgrade:} close \ref{gap:thread4-jarlskog}; unify CKM and baryogenesis
CP rows.
\end{theorem}

\begin{theorem}[Target: anomaly contact at two loops]
\label{thm:thread4-anomaly-contact}
\textbf{Target (Thread~4).} The one-loop identities
$b_0=12$ and mixed coefficient $-1$ of Theorem~\ref{thm:anomaly} persist as
\emph{contact invariants} under two-loop FRG flow
\eqref{eq:frg-system-app}: any threshold correction $\delta b_0$ at
$M_{\mathrm{GUT}}$ satisfies $|\delta b_0|<0.1$ when projected to the
$\Pi_{\sigma=-1}$ Jacobian row. \textbf{Upgrade:} close
\ref{gap:thread4-anomaly-two-loop}; tie Thread~4 to Appendix~\ref{sec:appendix:frg}.
\end{theorem}

\begin{theorem}[Target: precision-closed hadron mass]
\label{thm:thread4-hadron-precision}
\textbf{Target (Thread~4).} Refine Prediction~\ref{pred:hadron-masses} with
two-loop $\Lambda_{\mathrm{QCD}}$ and overlap phases from
Theorem~\ref{thm:Hij-derived}, yielding
$m_p=0.938\,\mathrm{GeV}$, $m_\pi=0.140\,\mathrm{GeV}$,
$m_\rho=0.775\,\mathrm{GeV}$ within $3\%$. \textbf{Upgrade:} close
\ref{gap:thread4-hadrons}; merge Thread~4 with Section~\ref{sec:qcd:hadrons}.
\end{theorem}

\paragraph{Dependencies and tier upgrades.}
Thread~4 depends on Tier~A anomaly arithmetic, Tier~B ledger FRG
(\textbf{A4} one-loop FRG), and D1--D3 scale identification
(Section~\ref{sec:scales}). The dependency chain is
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Input} & \textbf{Thread~4 output} \\
\midrule
Theorem~\ref{thm:anomaly}, Theorem~\ref{thm:beta} &
  $b_0=12$, GS coefficient exact contacts \\
Proposition~\ref{prop:frg-jacobian}, \eqref{eq:frg-system} &
  Capacity residues $\mathcal{R}_\iota$, threshold factors $R^{(2)}$ \\
Theorems~\ref{thm:nu-ratio-2loop}, \ref{thm:quark-mass-2loop},
Theorem~\ref{thm:g2-2loop} &
  Sub-percent flavour and $g$-2 contacts \\
Proposition~\ref{prop:ckm-precision}, Theorem~\ref{thm:strong-cp} &
  CP-even/odd sector contacts \\
Proposition~\ref{prop:alpha-s}, Prediction~\ref{pred:hadron-masses} &
  QCD/hadron Tier~C anchors \\
\bottomrule
\end{tabular}
\end{center}
\textbf{Tier upgrades sought:} QCD/hadron rows C$\to$ precision-closed
(Theorems~\ref{thm:thread4-alpha-s},~\ref{thm:thread4-hadron-precision});
CP phases C$\to$ B under derived $\mathcal{P}_{ij}$ complex structure
(Theorem~\ref{thm:thread4-cp-phases}); validation of $b_0$ at two loops
(Theorem~\ref{thm:thread4-anomaly-contact}).

\begin{equation}\label{eq:thread4-pipeline}
  \boxed{%
  (b_0,\text{GS})
  \;\xrightarrow{\;\text{FRG}\;}\;
  \mathcal{R}_\iota,\,R^{(2)}
  \;\xrightarrow{\;\text{D1--D3}\;}\;
  \mathcal{O}_{\mathrm{SJET}}
  \;\xrightarrow{\;\delta\;}\;
  \mathcal{O}_{\mathrm{exp}}
  }
\end{equation}
Equation~\eqref{eq:thread4-pipeline} is the Thread~4 specialization of
\eqref{eq:master-pipeline} to the contact layer;
Definition~\ref{def:contact-map} and Corollary~\ref{cor:tier-c-closure}
record the mid-2026 closure certificate for headline observables.

%======================================================================%
\subsection{Thread coupling and programme status}
\label{sec:threads-3-4-coupling}
%======================================================================%

Threads~3 and~4 are not independent. Thread~3 supplies the measure and OS
foundation on which Thread~4 loop arithmetic is defined: capacity residues
$\mathcal{R}_\iota$ are observer-chart functionals
(Remark~\ref{rmk:observer-frg}); $\sigma$-loop factorization
(Theorem~\ref{thm:sigma-measure}) ensures that precision observables computed
in $d\mu_{\Gamma_{-1}}$ are not contaminated by shadow-sector normalization;
the Coleman--Weinberg gap (Theorem~\ref{thm:rp}) sets the scale
$\mu\equiv v$ (Proposition~\ref{prop:mu-lifetime}) used in every Thread~4
workbook. Conversely, Thread~4 validates Thread~3: the $b_0=12$ anchor enters
the mass-gap counting on coset scalars ($n_S=28$); anomaly cancellation
guarantees that OS-reconstructed gauge dynamics is consistent at the contact
layer.

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Thread} & \textbf{Closed items} & \textbf{Open targets} & \textbf{Tier} \\
\midrule
3 &
  Cellular $\to$ $\hat Q$; coset mass gap; tree $\sigma$-split;
  OS reconstruction under \textbf{A7} &
  Thms.~\ref{thm:thread3-continuum}--\ref{thm:thread3-os-upgrade};
  gauge-sector gap &
  A/B \\
4 &
  $b_0$, GS; $\Delta m^2$, $m_\mu/m_e$, $g$-2, CKM, strong CP &
  Thms.~\ref{thm:thread4-alpha-s}--\ref{thm:thread4-hadron-precision};
  Jarlskog &
  A/C \\
\bottomrule
\end{tabular}
\caption{Thread~3--4 programme status as of mid-2026. \textbf{Closed} rows
cite proved manuscript content; \textbf{Open targets} name the upgrade
theorems of this section.}
\label{tab:threads-3-4-status}
\end{table}

\begin{corollary}[Thread audit certificate]\label{cor:threads-3-4-audit}
Relative to the semantic closure certificate
(Corollary~\ref{cor:semantic-closure}):
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item Thread~3 has \textbf{six} of nine questions closed
    (Table~\ref{tab:thread-3-questions}); residual items are quantitative
    continuum bounds, all-orders $\sigma$-loops, and gauge-sector OS gap.
  \item Thread~4 has \textbf{eight} of eleven questions closed or partial;
    residual items are $\alpha_s(M_Z)$, hadron masses, $|V_{ub}|$, and
    Jarlskog unification.
  \item No thread introduces a new primitive: both are audit trails over
    \eqref{eq:master-pipeline} with tier upgrades explicitly named.
\end{enumerate}
\end{corollary}

\begin{remark}[Relation to physics map]
Table~\ref{tab:physics-map-complete} Class~II (dynamical, Tier~B) and
Class~III (flavour and precision, Tier~C) are the physics-map avatar of
Threads~3 and~4 respectively. Corollary~\ref{cor:physics-map-closure}
therefore subsumes the closed portions of this section; the thread tables
record what remains for full Tier~A OS derivation and sub-percent QCD/hadron
contact.
\end{remark}