%======================================================================%
\subsection{Thread VII: Condensed-Matter Mechanisms}
\label{sec:thread-7}
%======================================================================%

Condensed matter is not a third primitive in SJET. It is the thermodynamic
limit of emergent descent: many replicated $\Pi_{\sigma=-1}$ modes on a
periodic extension of the Albert tower $\mathcal{T}_7$, with band structure
read off the cellular cosheaf $\mathcal{F}_{16}$
(Section~\ref{sec:emergent:condensed},
Theorem~\ref{thm:condensed-matter}). Thread~VII traces the \textbf{mechanism
chain} from observer collapse to Fermi-liquid quasiparticles, Bloch bands, and
metal--insulator splits; quantitative band gaps and strong-correlation phases
remain Tier~C or explicitly out of scope (Remark~\ref{rmk:emergent-honest}).

\begin{definition}[Condensed-matter thread datum]\label{def:thread-7}
The \emph{condensed-matter thread datum} is the triple
\begin{equation}\label{eq:thread-7-datum}
  \mathfrak{C}
  \;:=\;
  \bigl(
    \mathcal{E}_N,\;
    \mathcal{T}_7^{(L)},\;
    \mathcal{D}_{\mathbf{k}}
  \bigr),
\end{equation}
where $\mathcal{E}_N=(\Pi_{\sigma=-1})^{\otimes N}$ is the emergent descent
operator (Definition~\ref{def:emergent-descent}),
$\mathcal{T}_7^{(L)}$ is the $L$-fold periodic tower extension
(Definition~\ref{def:replica-limit}), and
$\mathcal{D}_{\mathbf{k}}=\bigoplus_\iota w_\iota D_\iota(\mathbf{k})$ is the
capacity-weighted cellular connection supplying Bloch eigenvalues
\eqref{eq:bloch-bands}. Laboratory condensed matter is
$\mathcal{F}_{\mathrm{CM}}(\mathfrak{C})$: the replica limit of
$\mathcal{H}_N^{\mathrm{em}}$ with Pauli exclusion inherited from tensor
antisymmetry (Proposition~\ref{prop:emergent-functor}).
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}clp{0.52\linewidth}@{}}
\toprule
\textbf{Q\#} & \textbf{Question} & \textbf{SJET status} \\
\midrule
Q7.1 &
  How do electronic bands arise without a postulated crystal Hamiltonian? &
  Bloch bands from $\mathcal{F}_{16}$ restriction maps on
  $\mathcal{T}_7^{(L)}$; eigenvalues \eqref{eq:bloch-bands}
  (Theorem~\ref{thm:condensed-matter}, item~(ii)). \\
\addlinespace
Q7.2 &
  What fixes low-$T$ quasiparticle interactions? &
  Capacity-weighted forward scattering;
  $F_0^s=\sum_\iota w_\iota^2=357/729$ \eqref{eq:landau-F0}
  (Theorem~\ref{thm:condensed-matter}, item~(i)). \\
\addlinespace
Q7.3 &
  When is the system metallic versus insulating? &
  Partial versus hub-saturated filling of the capacity shell ladder
  \eqref{eq:shell-ladder}; Mott threshold as overlap-network percolation
  (Theorem~\ref{thm:condensed-matter}, item~(iii)). \\
\addlinespace
Q7.4 &
  Are superconductivity, FQHE, or other strong-correlation phases derived? &
  \textbf{No.} Not closed in Section~\ref{sec:emergent:condensed};
  honest Tier~C/out-of-scope per Thread~IX. \\
\addlinespace
Q7.5 &
  What experimental anchors exist? &
  Leading-order Fermi-liquid and band-gap contacts;
  Table~\ref{tab:emergent-map} row ``Condensed matter''. \\
\bottomrule
\end{tabular}
\caption{Thread~VII question ledger: condensed-matter mechanisms.}
\label{tab:thread-7-questions}
\end{table}

\paragraph{Anchors.}
The thread is anchored at:
Definition~\ref{def:emergent-descent} (descent operator),
Definition~\ref{def:replica-limit} (thermodynamic limit),
Theorem~\ref{thm:condensed-matter} (Fermi liquid, bands, filling),
\eqref{eq:landau-F0}--\eqref{eq:bloch-bands},
Table~\ref{tab:emergent-map} (emergent descent map),
and the physics-map rows on electronic band structure and phonons
(Table~\ref{tab:physics-map-complete}, Class~V).

\paragraph{Gaps.}
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Lattice identification.} The periodic extension
    $\mathcal{T}_7^{(L)}$ is an emergent crystal identification, not a Tier~A
    output of void and mirror alone.
  \item \textbf{Landau EFT import.} Fermi-liquid identification cites ledger
    entry \textbf{A7} (clustering at long wavelength).
  \item \textbf{Quantitative closure.} Band gaps, effective masses, and
    critical exponents require radiative Yukawa and band-determinant
    refinements (Tier~C).
  \item \textbf{Strong correlations.} Superconductivity, fractional quantum
    Hall, and other non-Fermi-liquid phases are \emph{not} claimed derived.
\end{enumerate}

\paragraph{Targets.}
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item Structural: replica limit \eqref{eq:replica-limit} with density-fixed
    $N=\rho L^3$.
  \item Mechanism: nonempty Fermi surface $\mathcal{F}$ from partial capacity
    occupancy; insulator from hub saturation.
  \item Contact: leading-order match of $F_0^s$ and band-theory free energy
    $\Omega(\mu,T)$ in the $N\to\infty$ limit
    (Theorem~\ref{thm:thermodynamics}, item~(iv)).
  \item Falsifier: a derived band structure would be excluded if
    capacity-weighted connectivity $\mathcal{D}_{\mathbf{k}}$ could not
    reproduce the metal--insulator split of a standard tight-binding limit
    without importing an independent crystal potential.
\end{enumerate}

\paragraph{Dependencies.}
Thread~VII depends on:
observer collapse $\Pi_{\sigma=-1}$ (Section~\ref{sec:observer});
the cellular cosheaf $\mathcal{F}_{16}$ on $\mathcal{T}_7$
(Definition~\ref{def:F16});
capacity partition $(w_1,w_2,w_3)=(1/27,10/27,16/27)$
(Theorem~\ref{thm:partition});
emergent chemistry shell ladder (Theorem~\ref{thm:chemistry-ladder});
OS reconstruction for fermionic statistics (Theorem~\ref{thm:qm-derived}).

\paragraph{Tier path.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}llp{0.46\linewidth}@{}}
\toprule
\textbf{Tier} & \textbf{Content} & \textbf{Ledger / note} \\
\midrule
A &
  Pauli exclusion from antisymmetry of $\mathcal{H}_N^{\mathrm{em}}$;
  hub cocycle $\phi_1+\phi_2+\phi_3=0$ &
  Proposition~\ref{prop:emergent-functor} \\
B &
  Replica limit; Fermi-liquid and band-theory identification &
  \textbf{A7}; emergent $\mathcal{T}_7^{(L)}$ \\
C &
  Quantitative band gaps, $F_0^s$ contact, critical exponents &
  Radiative Yukawa + band determinant \\
\bottomrule
\end{tabular}
\end{center}

\begin{equation}\label{eq:thread-7-box}
  \boxed{%
  \varepsilon_n(\mathbf{k})
  \;=\;
  \lambda_n\!\bigl(\mathcal{D}_{\mathbf{k}}\bigr),
  \qquad
  \mathcal{D}_{\mathbf{k}}
  \;:=\;
  \bigoplus_{\iota=1}^3 w_\iota\,D_\iota(\mathbf{k}),
  \qquad
  L\to\infty,\;
  N=\rho L^3.}
\end{equation}

%======================================================================%
\subsection{Thread VIII: Arrow of Time and Entropy}
\label{sec:thread-8}
%======================================================================%

The thermodynamic arrow of time is not postulated as a separate law. It is the
coarse-grained asymmetry of observer-sector evolution along the Page--Wootters
clock $\tau_\iota$ (Definition~\ref{def:page-wootters}), weighted by the
$\sigma=-1$ Euclidean measure $d\mu_{\Gamma_{-1}}$
(Theorem~\ref{thm:sigma-measure}) and the capacity ensemble of
Definition~\ref{def:capacity-ensemble}. Mirror-shadow entropy stored in
$d\mu_{\Gamma_{+1}}$ is quotient-non-observable but sets the direction of
freeze-out and environmental pressure
(Definition~\ref{def:dm-freezeout}, Definition~\ref{def:env-pressure}).
Thread~VIII unifies quantum time, statistical entropy, and cosmological
sector decoupling into one directed narrative.

\begin{definition}[Arrow-of-time thread datum]\label{def:thread-8}
The \emph{arrow-of-time thread datum} is the quadruple
\begin{equation}\label{eq:thread-8-datum}
  \mathfrak{T}
  \;:=\;
  \bigl(
    \tau_\iota,\;
    d\mu_{\Gamma_{-1}},\;
    d\nu_\beta,\;
    k_{\mathrm{FO}}
  \bigr),
\end{equation}
where $\tau_\iota$ is the Page--Wootters clock,
$d\mu_{\Gamma_{-1}}$ is the observable factor of \eqref{eq:gamma-split},
$d\nu_\beta$ is the capacity ensemble \eqref{eq:capacity-ensemble}, and
$k_{\mathrm{FO}}=\kappa_\star^{1/2}v$ is the shadow freeze-out scale
(Definition~\ref{def:dm-freezeout}). The \emph{thermodynamic arrow} is the
monotone increase of capacity-weighted microstate entropy $S$ in
\eqref{eq:helmholtz} along increasing $\tau_\iota$ on admitted lifetime charts,
modulo hub-cocycle gauge relabelings on $\mathcal{T}_7$.
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}clp{0.52\linewidth}@{}}
\toprule
\textbf{Q\#} & \textbf{Question} & \textbf{SJET status} \\
\midrule
Q8.1 &
  Is time external or relational? &
  Relational: $\tau_\iota$ is the soldering clock on $H_2(\Quat)$
  (Definition~\ref{def:page-wootters},
  Proposition~\ref{prop:page-wootters-derived}). \\
\addlinespace
Q8.2 &
  Where does the partition function come from? &
  $\mathcal{Z}(\beta)=\mathrm{Tr}\,e^{-\beta\hat H_\iota}$ equals the
  $\Pi_{\sigma=-1}$-projected functional integral on
  $\mathcal{M}_{-1}$ \eqref{eq:Z-sigma}
  (Theorem~\ref{thm:thermodynamics}). \\
\addlinespace
Q8.3 &
  What defines entropy? &
  Capacity-weighted microstate count on $\mathcal{T}_7$ modulo hub cocycle
  \eqref{eq:helmholtz}; not a postulated Gibbs axiom. \\
\addlinespace
Q8.4 &
  Why does entropy increase? &
  Below $k_{\mathrm{FO}}$, $\sigma=+1$ reservoir ceases entropy sharing with
  $d\mu_{\Gamma_{-1}}$ \eqref{eq:dm-freezeout}; observable sector
  equilibration is directed along $\tau_\iota$ under \textbf{A7} clustering. \\
\addlinespace
Q8.5 &
  How does the shadow sector enter? &
  $d\mu_{\Gamma_{+1}}$ normalizes the split but does not contribute to
  $\mathcal{Z}(\beta)$ in the observable sector
  (Theorem~\ref{thm:duality}, Remark on emergent thermodynamics). \\
\addlinespace
Q8.6 &
  Is quantitative heat capacity derived? &
  Euler structure \eqref{eq:thermo-laws} is Tier~B; numeric heat capacities
  and critical points are Tier~C contacts. \\
\bottomrule
\end{tabular}
\caption{Thread~VIII question ledger: arrow of time and entropy.}
\label{tab:thread-8-questions}
\end{table}

\paragraph{Anchors.}
The thread is anchored at:
Theorem~\ref{thm:sigma-measure} (measure factorization),
Definition~\ref{def:page-wootters} and Proposition~\ref{prop:page-wootters-derived}
(clock),
Theorem~\ref{thm:qm-derived} (OS reconstruction),
Definition~\ref{def:capacity-ensemble} and Theorem~\ref{thm:thermodynamics}
(statistical mechanics),
Definition~\ref{def:dm-freezeout} and Lemma~\ref{lem:dm-capacity-fraction}
(entropy routing at freeze-out),
Definition~\ref{def:env-pressure} (environmental pressure conjugate).

\paragraph{Gaps.}
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Coarse-graining proof.} The identification of $S$ with a
    microstate count on $\mathcal{T}_7$ is structural; a full Kolmogorov--Sinai
    or entanglement-entropy certificate is not supplied.
  \item \textbf{Quantum arrow.} Measurement update is Tier~B via
    Theorem~\ref{thm:measurement-collapse}; a complete alignment of
    decoherence timescales with laboratory records is Tier~C.
  \item \textbf{Cosmological entropy.} Shadow freeze-out fixes $f_{+1}=4/15$
    but does not derive the full cosmological entropy budget of the CMB.
  \item \textbf{Quantitative thermodynamics.} Heat capacities, latent heats,
    and critical exponents require emergent refinements beyond
    \eqref{eq:thermo-laws}.
\end{enumerate}

\paragraph{Targets.}
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item Derive $\mathcal{Z}(\beta)$, $F(\beta)$, and $S$ from $d\mu_{\Gamma_{-1}}$
    without a supplemental statistical postulate.
  \item Identify the thermodynamic arrow with monotone $\tau_\iota$ flow and
    sector freeze-out at $k_{\mathrm{FO}}$.
  \item Contact: free-energy limit $F/N\to\Omega(\mu,T)$ in the replica limit
    (Theorem~\ref{thm:thermodynamics}, item~(iv)).
  \item Falsifier: an observable-sector theory that requires time-symmetric
    equilibrium on $d\mu_{\Gamma_{-1}}$ while maintaining
    $\Pi_{\sigma=-1}$ projection would contradict the directed capacity
    ensemble.
\end{enumerate}

\paragraph{Dependencies.}
Thread~VIII depends on:
Thread~VII replica limit (for $N\to\infty$ free-energy contact);
Section~\ref{sec:quantum-origin} (Page--Wootters, OS reconstruction);
Theorem~\ref{thm:sigma-measure} (measure split);
Section~\ref{sec:dark-sector:abundance} (shadow freeze-out);
Definition~\ref{def:env-pressure} and Theorem~\ref{thm:cc-sequester}
(environmental conjugate variables).

\paragraph{Tier path.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}llp{0.46\linewidth}@{}}
\toprule
\textbf{Tier} & \textbf{Content} & \textbf{Ledger / note} \\
\midrule
A &
  $\sigma$-grading; quotient non-observability of $d\mu_{\Gamma_{+1}}$ &
  Theorem~\ref{thm:duality} \\
B &
  $\mathcal{Z}(\beta)$ from OS + capacity ensemble;
  Euler relation \eqref{eq:thermo-laws} &
  \textbf{A7}, \textbf{A8} \\
B/C &
  Shadow freeze-out scale $k_{\mathrm{FO}}$; fraction $f_{+1}=4/15$ &
  \textbf{A1}, FRG at $\kappa_\star$ \\
C &
  Heat capacities, critical points, decoherence timescales &
  Emergent refinements \\
\bottomrule
\end{tabular}
\end{center}

\begin{equation}\label{eq:thread-8-box}
  \boxed{%
  d\nu_\beta
  \;=\;
  \frac{1}{\mathcal{Z}(\beta)}\,
  e^{-\beta\hat H_\iota}\,
  d\mu_{\Gamma_{-1}},
  \qquad
  F(\beta)=-\frac{1}{\beta}\log\mathcal{Z}(\beta)
  \;=\;
  \langle S\rangle_{\Gamma_{-1}}-TS.}
\end{equation}

%======================================================================%
\subsection{Thread IX: Out-of-Scope Phenomenology Boundary}
\label{sec:thread-9}
%======================================================================%

Semantic closure of the \emph{fundamental} chain
(Corollary~\ref{cor:semantic-closure}) does not claim Tier~A/B closure of every
laboratory observable. Thread~IX records the \textbf{honest phenomenology
boundary}: which domains are \emph{emergent contacts} on fixed SM+$d{=}4$
gravity outputs, which data are \emph{external datums} imported from standard
effective theory, and which rows of Table~\ref{tab:physics-map-complete} are
explicitly out of scope for new SJET theorems. This thread prevents
over-claiming while certifying that \textbf{no additional primitive} is required
beyond void and mirror (Remark~\ref{rmk:emergent-honest},
Corollary~\ref{cor:physics-map-closure}).

\begin{definition}[Phenomenology tier]\label{def:phenomenology-tier}
A result carries the \emph{phenomenology tier} when it satisfies all of:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{No new primitive.} The claim uses only outputs of
    \eqref{eq:master-pipeline} through Tier~A or Tier~B functors.
  \item \textbf{Emergent truncation.} The laboratory description is obtained by
    $\mathcal{F}_D=\mathrm{eval}_{\mathrm{emergent}}$ on SM+$d{=}4$ gravity+QED
    (Class~V, Section~\ref{sec:physics-map:grouping}), not by a new
    $\sigma$-sector insertion.
  \item \textbf{External datum class.} Numerical comparison uses measured or
    tabulated constants from the \emph{external datum class}
    $\mathcal{D}_{\mathrm{ext}}$ (Definition~\ref{def:external-datum}).
  \item \textbf{Non-closure certificate.} The manuscript records that the
    result is a \emph{contact}, not a closure theorem, with tolerance
    $\delta$ from Definition~\ref{def:contact-map} when applicable.
\end{enumerate}
Phenomenology tier is the honest label for Class~V rows in
Table~\ref{tab:physics-map-complete}; it is stricter than Tier~C alone because
it explicitly names the imported EFT layer.
\end{definition}

\begin{definition}[External datum class]\label{def:external-datum}
The \emph{external datum class} $\mathcal{D}_{\mathrm{ext}}$ is the set of
laboratory and astrophysical inputs \textbf{not} fixed by void and mirror at
Tier~A/B, imported only at the phenomenology contact layer:
\begin{equation}\label{eq:external-datum}
  \mathcal{D}_{\mathrm{ext}}
  \;:=\;
  \bigl\{
    \text{measured masses and lifetimes below $\Lambda_{\mathrm{QCD}}$},
    \;
    \text{nuclear binding tables},
    \;
    \text{atomic/QED tabulations},
    \;
    \text{crystal potentials and disorder},
    \;
    \text{opacity and EOS tables},
    \;
    \text{plasma transport coefficients},
    \;
    \text{biological complexity scales}
  \bigr\}.
\end{equation}
An observable $O$ is an \emph{external-datum contact} when
$O=\mathcal{C}_{\mathrm{ext}}(\mathfrak{E},\delta)$ for
$\mathfrak{E}$ the universe datum \eqref{eq:universe-summary} and
$\mathcal{C}_{\mathrm{ext}}$ a standard EFT evaluator drawing on
$\mathcal{D}_{\mathrm{ext}}$ but introducing \textbf{no} new entry in the
assumption ledger \textbf{A1--A8}.
\end{definition}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.12}
\begin{tabular}{@{}clp{0.52\linewidth}@{}}
\toprule
\textbf{Q\#} & \textbf{Question} & \textbf{SJET status} \\
\midrule
Q9.1 &
  Does SJET derive every PDG-row observable at Tier~A/B? &
  \textbf{No.} $20$ Tier~C/emergent rows in
  Table~\ref{tab:physics-map-complete}; fundamental closure is
  Corollary~\ref{cor:semantic-closure}. \\
\addlinespace
Q9.2 &
  What is the honest label for many-body physics? &
  Phenomenology tier (Definition~\ref{def:phenomenology-tier});
  functor $\mathrm{eval}_{\mathrm{emergent}}$. \\
\addlinespace
Q9.3 &
  Which inputs are external? &
  Class $\mathcal{D}_{\mathrm{ext}}$
  (Definition~\ref{def:external-datum}): tabulated low-energy and
  continuum data not output by \eqref{eq:master-pipeline}. \\
\addlinespace
Q9.4 &
  Are superconductivity, turbulence, or protein folding derived? &
  \textbf{Out of scope.} Emergent EFT contacts only; no new SJET theorem
  claimed (Thread~VII Q7.4). \\
\addlinespace
Q9.5 &
  Is hierarchical closure honest? &
  \textbf{Yes.} Corollary~\ref{cor:physics-map-closure} item~(vi):
  emergent rows certify \emph{no additional primitive}. \\
\addlinespace
Q9.6 &
  Where do tolerances enter? &
  Definition~\ref{def:contact-map} for Tier~C predictions;
  phenomenology tier adds explicit $\mathcal{D}_{\mathrm{ext}}$ tagging. \\
\bottomrule
\end{tabular}
\caption{Thread~IX question ledger: phenomenology boundary.}
\label{tab:thread-9-questions}
\end{table}

\paragraph{Anchors.}
The thread is anchored at:
Definition~\ref{def:proof-tiers} (Tier~A/B/C),
Corollary~\ref{cor:semantic-closure} and Corollary~\ref{cor:physics-map-closure},
Table~\ref{tab:physics-map-complete} (especially Class~V emergent rows),
Remark~\ref{rmk:emergent-honest} (Section~\ref{sec:emergent}),
Remark on emergent rows (Section~\ref{sec:physics-map}),
Definition~\ref{def:contact-map} (tolerances),
Table~\ref{tab:emergent-map} (descent versus contact rows).

\paragraph{Gaps.}
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Per-observable certificates.} The map assigns routes, not
    individual closure proofs for each many-body observable.
  \item \textbf{EFT selection.} Which standard EFT (BCS, Navier--Stokes, MHD,
    etc.) applies is laboratory context, not forced by $\mathcal{T}_7$ alone.
  \item \textbf{Systematic $\mathcal{D}_{\mathrm{ext}}$ catalog.} The external
    datum class is named, not exhaustively tabulated observable-by-observable.
  \item \textbf{Precision frontier.} Sub-percent atomic and nuclear contacts
    remain external-datum imports even when fundamental couplings are Tier~B.
\end{enumerate}

\paragraph{Targets.}
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item Maintain primitive count $2$ while mapping all PDG-headline domains.
  \item Tag every Class~V row with phenomenology tier and, where numeric,
    $\mathcal{D}_{\mathrm{ext}}$ membership.
  \item Distinguish \emph{derived descent} (Thread~VII--VIII) from
    \emph{imported contact} (Thread~IX).
  \item Falsifier: claiming a new SJET primitive or ledger entry
    \textbf{A9+} solely to fit a many-body observable would violate
    Corollary~\ref{cor:axiomatic-closure}.
\end{enumerate}

\paragraph{Dependencies.}
Thread~IX depends on:
Theorem~\ref{thm:master-derivation} and \eqref{eq:master-pipeline};
Corollary~\ref{cor:physics-map-closure};
Threads~VII and~VIII (what \emph{is} derived at Tier~B in the emergent layer);
Definition~\ref{def:proof-tiers} and Definition~\ref{def:contact-map}.

\paragraph{Tier path.}
\begin{center}
\small
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}llp{0.46\linewidth}@{}}
\toprule
\textbf{Layer} & \textbf{Functor} & \textbf{Claim type} \\
\midrule
Fundamental &
  $\mathcal{F}_D\circ\Pi_{\sigma=-1}\circ\mathrm{Bal}_{\mathcal{C}}\circ\Mirror^{\leq 8}$ &
  Tier~A/B theorems \\
Descent &
  $\mathcal{E}_N$, $d\nu_\beta$ (Threads~VII--VIII) &
  Tier~B/C structural \\
Phenomenology &
  $\mathrm{eval}_{\mathrm{emergent}}(\mathfrak{E};\mathcal{D}_{\mathrm{ext}})$ &
  Contact only; no new primitive \\
Out of scope &
  Strong correlations, biophysics detail, turbulence &
  External datum or future work \\
\bottomrule
\end{tabular}
\end{center}

\begin{equation}\label{eq:thread-9-box}
  \boxed{%
  \mathcal{M}_{\mathrm{ph}}(D)
  \;=\;
  \mathrm{eval}_{\mathrm{emergent}}\!\bigl(
    \mathcal{F}_D(\mathfrak{E})\,;\,
    \mathcal{D}_{\mathrm{ext}}
  \bigr),
  \qquad
  \mathfrak{E}
  \;=\;
  \mathcal{U}\!\bigl(
    \Pi_{\sigma=-1}\circ\mathrm{Bal}_{\mathcal{C}}\circ\Mirror^{\leq 8}
  \bigr)(\Void).}
\end{equation}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{@{}llcc@{}}
\toprule
\textbf{Domain block} & \textbf{Example observables} &
\textbf{Tier} & \textbf{Scope} \\
\midrule
Nuclear / atomic &
  Binding energies, fine structure &
  Phenomenology &
  $\mathcal{D}_{\mathrm{ext}}$ \\
Condensed matter (strong) &
  SC, FQHE, critical exponents &
  Out of scope &
  Standard many-body EFT \\
Fluids / plasma &
  Navier--Stokes, MHD, fusion &
  Phenomenology &
  $\mathcal{D}_{\mathrm{ext}}$ \\
Astrophysics (stellar) &
  Opacity, $M$--$L$ relation &
  Phenomenology &
  SM+GR+tables \\
Biophysics &
  Folding, neural scales &
  Out of scope &
  Statistical mechanics import \\
\bottomrule
\end{tabular}
\caption{Thread~IX scope table: honest phenomenology and out-of-scope blocks.
Rows are contacts on \eqref{eq:universe-summary}, not new primitives.}
\label{tab:thread-9-scope}
\end{table}

\begin{remark}[Thread closure certificate]\label{rmk:thread-7-9-closure}
Threads~VII--IX complete the emergent frontier trace through SJET.
Thread~VII supplies condensed-matter \emph{mechanisms} at Tier~B/C;
Thread~VIII unifies the \emph{arrow of time} with the $\sigma$-measure and
capacity ensemble; Thread~IX draws the \emph{phenomenology boundary} so that
Class~V physics is hierarchical closure, not hidden postulation. Together with
Section~\ref{sec:emergent}, Section~\ref{sec:quantum-origin}, and
Section~\ref{sec:physics-map}, the manuscript records a complete honest map from
$(\Void,\Mirror)$ to laboratory many-body phenomena without increasing the
primitive axiom count beyond two.
\end{remark}