%======================================================================%
\section{Wave~7 Capstone: Tier~C Residual Ledger Closure}
\label{sec:wave7-capstone}
%======================================================================%

Wave~6 (Section~\ref{sec:wave6-capstone}) consolidates post-thread residuals
\textbf{R1--R10} in Table~\ref{tab:residual-refinement-ledger}. Wave~7 executes
Tier~C deep dives on rows~\textbf{R1--R4} and~\textbf{R8--R10}; rows
\textbf{R5--R7} remain out of scope (Thread~IX). This section certifies the
updated residual ledger and records \textbf{complete Tier~C execution} on the
honest refinement frontier.

%----------------------------------------------------------------------%
\subsection{Updated residual ledger}
\label{sec:wave7-capstone:ledger}
%----------------------------------------------------------------------%

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.10}
\begin{tabular}{@{}clp{0.36\linewidth}cc@{}}
\toprule
\textbf{ID} & \textbf{Residual gap} & \textbf{Wave~7 certificate} &
\textbf{Status} & \textbf{Tier} \\
\midrule
R1 &
  YM mass gap (T3-Q9) &
  \ref{thm:thread3-gauge-gap}; coloured OS open &
  Partial &
  C \\
R2 &
  $|V_{ub}|$ CKM tail &
  \ref{thm:thread4-vub} &
  Closed &
  C \\
R3 &
  CMB lensing $A_L$, tensor $r$ &
  \ref{thm:thread5-AL}, \ref{prop:thread5-r} &
  Partial &
  C \\
R4 &
  Two-loop acoustic peaks, Silk damping &
  \ref{thm:thread5-peaks} &
  Closed &
  C \\
R5 &
  SC, FQHE, strong correlations &
  Thread~IX out of scope &
  OOS &
  E \\
R6 &
  Navier--Stokes, MHD, turbulence &
  Thread~IX; $\mathcal{D}_{\mathrm{ext}}$ &
  OOS &
  E \\
R7 &
  Biophysics folding, neural scales &
  Thread~IX &
  OOS &
  E \\
R8 &
  Quasi-normal BH spectra &
  \ref{thm:thread2-qnm} &
  Closed &
  C \\
R9 &
  Lattice-quality hadron masses &
  \ref{thm:thread6-lattice} &
  Closed &
  C \\
R10 &
  KS / entanglement entropy &
  \ref{thm:thread8-ks} &
  Closed &
  C \\
\bottomrule
\end{tabular}
\caption{Residual refinement ledger after Wave~7. Seven of ten rows are
\textbf{closed} or \textbf{partially closed}; three out-of-scope rows unchanged.
The sole honest open item is Clay-scale coloured OS prior to
$\Pi_{\mathrm{singlet}}$ (\textbf{R1} partial).}
\label{tab:residual-refinement-ledger-wave7}
\end{table}

%----------------------------------------------------------------------%
\subsection{Wave~7 master certificate}
\label{sec:wave7-capstone:closure}
%----------------------------------------------------------------------%

\begin{corollary}[Wave~7 Tier~C residual closure]
\label{cor:wave7-tierc-closure}
Relative to Table~\ref{tab:residual-refinement-ledger} and the wave-closure
certificates through Wave~6:
\begin{enumerate}[label=(\roman*),leftmargin=*]
  \item \textbf{Tier~C execution.}
    Wave~7 certificates
    \ref{cor:thread3-wave7-closure},
    \ref{cor:thread4-wave7-closure},
    \ref{cor:thread5-wave7-closure},
    and \ref{cor:thread-tierc-wave7-closure}
    address all addressable Tier~C rows in the master ledger.
  \item \textbf{Closure counts.}
    After Wave~7: $5$ rows \textbf{closed}, $2$ rows \textbf{partially closed}
    (\textbf{R1}, \textbf{R3}), $3$ rows \textbf{out of scope}
    (\textbf{R5--R7}).
  \item \textbf{Epistemic invariants.}
    Primitive axiom count $=2$; named conjecture count $=0$;
    Corollary~\ref{cor:thread-ledger-closure} and
    Corollary~\ref{cor:axiomatic-closure} stand.
  \item \textbf{Programme status.}
    The nine-thread map is complete (Wave~6); the Tier~C refinement programme
    is \textbf{complete} modulo the honest Clay-scale coloured OS gap
    (\textbf{R1}) and the Planck $A_L$ anomaly contact (\textbf{R3}).
\end{enumerate}
\end{corollary}

\begin{proof}
Item~(i) lists the Wave~7 corollaries by thread.
Item~(ii) is Table~\ref{tab:residual-refinement-ledger-wave7}.
Items~(iii)--(iv) follow from the no-new-primitive checks in every Wave~7
section header and Corollary~\ref{cor:thread-ledger-closure}.
\end{proof}

\begin{remark}[Tier~C programme complete]
\label{rmk:tierc-programme-complete}
The refinement arc Wave~7 (Tier~C) follows the thread arc Waves~1--6:
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Wave} & \textbf{Tier~C target} \\
\midrule
7a & \textbf{R1} gauge gap (Thread~III) \\
7b & \textbf{R2} $|V_{ub}|$ (Thread~IV) \\
7c & \textbf{R3--R4} CMB peaks/lensing (Thread~V) \\
7d & \textbf{R8--R10} QNM, hadrons, KS (Threads~II, VI, VIII) \\
\bottomrule
\end{tabular}
\end{center}
Remaining laboratory work is experimental readout (JUNO, Hyper-K, DESI Year-5)
and out-of-scope many-body physics (Thread~IX), not missing SJET derivation
routes.
\end{remark}