%======================================================================%
\section*{References}
\addcontentsline{toc}{section}{References}
%======================================================================%

\begin{thebibliography}{99}

\bibitem{Albert1934}
P.~Albert, ``On a certain algebra of cubic forms,''
\emph{Ann.\ of Math.} (1934).

\bibitem{Freudenthal1954}
H.~Freudenthal, ``Beziehungen der $\mathfrak{E}_7$ und $\mathfrak{E}_8$
zur Oktavenebene,'' \emph{Indag.\ Math.} (1954).

\bibitem{Hurwitz1898}
A.~Hurwitz, ``\"Uber die Komposition der quadratischen Formen,''
\emph{Math.\ Ann.} (1898).

\bibitem{Stone1936}
M.~H.~Stone, ``The theory of representations for Boolean algebras,''
\emph{Trans.\ Amer.\ Math.\ Soc.} (1936).

\bibitem{Sakharov1967}
A.~D.~Sakharov, ``Vacuum quantum fluctuations in curved space and the
theory of gravitation,'' \emph{Dokl.\ Akad.\ Nauk SSSR} (1967).

\bibitem{GreenSchwarz1984}
M.~B.~Green and J.~H.~Schwarz, ``Anomaly cancellation in supersymmetric
$D=10$ gauge theory,'' \emph{Phys.\ Lett.\ B} (1984).

\bibitem{GeorgiGlashow1974}
H.~Georgi and S.~L.~Glashow, ``Unity of all elementary-particle forces,''
\emph{Phys.\ Rev.\ Lett.} (1974).

\bibitem{PageWootters1983}
D.~N.~Page and W.~K.~Wootters, ``Evolution without evolution,''
\emph{Phys.\ Rev.\ D} (1983).

\bibitem{Reuter1998}
M.~Reuter, ``Nonperturbative evolution equation for quantum gravity,''
\emph{Phys.\ Rev.\ D} (1998).

\bibitem{ColemanWeinberg1973}
S.~Coleman and E.~Weinberg, ``Radiative corrections as the origin of
spontaneous symmetry breaking,'' \emph{Phys.\ Rev.\ D} (1973).

\end{thebibliography}