\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{slashed}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{prediction}[theorem]{Prediction}

\numberwithin{equation}{section}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Quat}{\mathbb{H}}
\newcommand{\Oct}{\mathbb{O}}
\newcommand{\jalg}{J_3(\mathbb{O})}
\newcommand{\E}[1]{\mathrm{E}_{#1}}
\newcommand{\Spin}{\mathrm{Spin}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\Void}{\mathcal{V}}
\newcommand{\Mirror}{\mathsf{M}}
\newcommand{\Climb}{\mathsf{C}}
\newcommand{\capacity}{\mathcal{C}}
\newcommand{\orderparam}{\Phi}
\newcommand{\MPl}{M_{\mathrm{Pl}}}
\newcommand{\Hess}{\operatorname{Hess}}
\DeclareMathOperator{\argmax}{arg\,max}

\title{Stone--Jordan Exceptional Theory\\[0.35em]
\large Building the Universe from the Mirror}
\author{Brandon Belna}
\date{June 6, 2026}

\begin{document}
\maketitle

\begin{abstract}
We construct a mathematical model of the universe from two primitives: the
\textbf{void} (no observable distinction) and an involutive \textbf{mirror
operator} $\Mirror$ on profinite observable spectra. Iterating $\Mirror$ climbs
the Hurwitz division ladder and the exceptional Lie cascade; capacity
balancing $\mathrm{Bal}_{\mathcal{C}}$ is the dual mirror selecting unique
partitions at each rung. The universe is the profinite fixed point
$\mathfrak{U}^\star=\Climb^\infty(\Void)$, stabilizing on the Albert algebra
$J_3(\mathbb{O})$ and the compact exceptional group $E_6$. Physical observables
are $\sigma$-anti-invariant modes on the mirror quotient at the heterotic
rung, selected by observer collapse $\Pi_{\sigma=-1}$. The \emph{as above, so
below} correspondence identifies the universe fixed point with collapsed
observer states; duality is forced by $E_8\times E_8$ product mirror
collapse. A Lefschetz fixed-point theorem yields three observer slots; an
index $\iota$ maps to a lifetime chart $g_\iota:\mathbb{R}\to\mathcal{S}_\iota$.
\textbf{Semantic closure achieved:} the master derivation chain
(Theorem~\ref{thm:master-derivation}) classifies every physical datum by proof
tier (A rigorous; B under derived assumption ledger \textbf{A1--A8}; C
leading-order contact). Former postulates P1--P5, CC, P3$'$, and D1--D3 are
derived with explicit tier labels; no unnamed assumptions or conjectures remain.
Strong CP, baryogenesis, dark matter, Hubble tension, quark precision, proton
decay, quantum origin, and the complete physics domain map (60 domains,
Corollaries~\ref{cor:universe-closure},~\ref{cor:physics-map-closure}) are
derived from void and mirror. Tiered predictions contact JUNO (normal ordering;
$\Delta m^2_{31}/\Delta m^2_{21}\approx 33$), Muon $g$-2 ($n_F=3$, no fourth
generation; loops at $\mu\equiv v$), and DESI ($w(z)\approx -1$). GUT contacts
include $\sin^2\theta_W(M_{\mathrm{GUT}})=3/8$,
$\sin^2\theta_W(M_Z)\approx 0.231$ by RG, and
$\tau(p\to e^+\pi^0)\gtrsim 10^{34}$\,yr under the $\E{6}$ breaking chain. A
falsification timeline (2026--2030) orders the decisive experiments.
\end{abstract}

\noindent\textbf{Keywords:} void; mirror operator; Stone duality; exceptional
Jordan algebra; profinite limit; $E_6$ coset.

\noindent\textbf{MSC 2020:} 03G05, 17C27, 22E46, 81T13.

\tableofcontents
\clearpage