%======================================================================%
\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}
%======================================================================%

The author thanks prior UCFT/BAMLP development for the validated spine
(archived in \texttt{old/}), especially the corrected $\beta$-function counts
and anomaly arithmetic.

%======================================================================%
\section*{References}
\addcontentsline{toc}{section}{References}
%======================================================================%

\begin{thebibliography}{99}

\bibitem{Jacobson1968}
N.~Jacobson, \emph{Structure and Representations of Jordan Algebras},
Amer.\ Math.\ Soc., Providence, 1968.

\bibitem{Freudenthal1954}
H.~Freudenthal, ``Beziehungen der $\mathfrak{E}_7$ und $\mathfrak{E}_8$
zur Oktavenebene,'' \emph{Indag.\ Math.} \textbf{16} (1954), 218--230.

\bibitem{Tits1966}
J.~Tits, ``Alg\`ebres alternatives, alg\`ebres de Jordan et alg\`ebres de
Lie exceptionnelles,'' \emph{Indag.\ Math.} \textbf{28} (1966), 223--237.

\bibitem{SpringerVeldkamp2000}
T.~A.~Springer and F.~D.~Veldkamp, \emph{Octonions, Jordan Algebras and
Exceptional Groups}, Springer, Berlin, 2000.

\bibitem{Hurwitz1898}
A.~Hurwitz, ``\"Uber die Komposition der quadratischen Formen von
unendlich vielen Variablen,'' \emph{Math.\ Ann.} \textbf{54} (1898), 1--26.

\bibitem{Stone1936}
M.~H.~Stone, ``The theory of representations for Boolean algebras,''
\emph{Trans.\ Amer.\ Math.\ Soc.} \textbf{40} (1936), 37--111.

\bibitem{Sakharov1967}
A.~D.~Sakharov, ``Vacuum quantum fluctuations in curved space and the
theory of gravitation,'' \emph{Dokl.\ Akad.\ Nauk SSSR} \textbf{177} (1967),
70--71.

\bibitem{GreenSchwarz1984}
M.~B.~Green and J.~H.~Schwarz, ``Anomaly cancellations in supersymmetric
$D=10$ gauge theory and superstring theory,''
\emph{Phys.\ Lett.\ B} \textbf{149} (1984), 117--122.

\bibitem{GeorgiGlashow1974}
H.~Georgi and S.~L.~Glashow, ``Unity of all elementary-particle forces,''
\emph{Phys.\ Rev.\ Lett.} \textbf{32} (1974), 438--441.

\bibitem{PageWootters1983}
D.~N.~Page and W.~K.~Wootters, ``Evolution without evolution: an explicit
example,'' \emph{Phys.\ Rev.\ D} \textbf{27} (1983), 2885--2892.

\bibitem{OsterwalderSchrader1973}
K.~Osterwalder and R.~Schrader, ``Axioms for Euclidean Green's functions,''
\emph{Commun.\ Math.\ Phys.} \textbf{31} (1973), 83--112.

\bibitem{OsterwalderSchrader1975}
K.~Osterwalder and R.~Schrader, ``Axioms for Euclidean Green's functions II,''
\emph{Commun.\ Math.\ Phys.} \textbf{42} (1975), 281--305.

\bibitem{GlimmJaffe1987}
J.~Glimm and A.~Jaffe, \emph{Quantum Physics: A Functional Integral Point of
View}, 2nd ed., Springer, New York, 1987.

\bibitem{Reuter1998}
M.~Reuter, ``Nonperturbative evolution equation for quantum gravity,''
\emph{Phys.\ Rev.\ D} \textbf{57} (1998), 971--985.

\bibitem{ColemanWeinberg1973}
S.~Coleman and E.~Weinberg, ``Radiative corrections as the origin of
spontaneous symmetry breaking,'' \emph{Phys.\ Rev.\ D} \textbf{7} (1973),
1888--1910.

\bibitem{Witten1985}
E.~Witten, ``Symmetry breaking patterns in superstring models,''
\emph{Nucl.\ Phys.\ B} \textbf{258} (1985), 75--100.

\bibitem{AtiyahBott1966}
M.~F.~Atiyah and R.~Bott, ``A Lefschetz fixed point formula for elliptic
complexes,'' \emph{Bull.\ Amer.\ Math.\ Soc.} \textbf{72} (1966), 245--254.

\end{thebibliography}